### 2013-01-24 03-summary/summary.tex
setup the latex

\documentclass[11pt,letterpaper,oneside]{article}
\usepackage[top=1in,left=1in,right=1in,bottom=1in]{geometry}
\usepackage{fancyvrb}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{url}

%\usepackage{setspace}
%\doublespacing

\title{summary}
\author{Dejun Qian\\electronseu@gmail.com}

\date{}

\begin{document}
\maketitle

% the problem solved, the approach used, and the results
This paper

\cite{bib:Pandita}.

\bibliographystyle{acm}
\bibliography{reference}

\end{document}

### 2013-01-24 03-summary/summary.tex
draft

@@
 \documentclass[11pt,letterpaper,oneside]{article}
-\usepackage[top=1in,left=1in,right=1in,bottom=1in]{geometry}
+\usepackage[top=0.5in,left=1in,right=1in,bottom=1in]{geometry}
 \usepackage{fancyvrb}
@@
 % the problem solved, the approach used, and the results
-This paper
+Software reuse gives software developers to build larger software products with higher quality in shorter time.
+The reused software is usually provided to the developers in the forms of source code or binary executable,
+along with the document explaining to the users how to use itself.
+Reading and understanding the document is important, 
+or even the only way when no source code is provided,
+to correctly use the provided functionalities.
+However, the developers are easily overlook something in the document,
+and misuse some of the functions,
+which will leads to potential bugs in the product.
+Many verification tools are developed to detect the inconsistence between the document and the software,
+however these tools only accept formal specifictions as their input.
+They can't understand documents writen in natual language.
+This paper \cite{bib:Pandita} presents an approach to fill the gap between what is needed by the existing verification tools and what the document can provide.
 
-\cite{bib:Pandita}.
+The author of the paper claimed that they are the first to address this problem.
+This paper developed a technique to get the code contract from the library document.
+The technique includes five steps: parse, pre-process, text analysis, post-process and code contract generation.
+In the parsing step, the parsor process the API documents and extracts intermediate contents of the method description, 
+such as, summary description, argument description, return description, exception dexcription and remark dexcription. 
+In the pre-processing step, the pre-processor takes the intermediate content, 
+and perform three categories of processing: meta-data augmentation, noun boosting and programming constructs and jargon handling.
+These first two steps are critical, as they can improve the results of the third step a lot.
+The third step is text analysis.
+In this step, this paper developed a text analysis engine framework, 
+and adopting an existing POS tagger to annote POS tags for the input sentences.
+After that, they use an NLP technique, called shallow parsor to classify the sentences into semantic templates,
+based on the lexical tokens generated in the previous step.
+The shallow parsor also generates FOL expressions after it has done the classifiction.
+In the post-processing step, the paper does three types of semantic analysis: removing irrelevant modifiers in predicates, classifying predicates into a semantic class based on domain dictionaries, and augmenting expressions.
+In the final step, by using prefined mapping from predicates to code contracts,
+the paper translates the FOL into code contracts.
+
+The author did three experiments to demonstrate the effection of the approach. 
+Their experimens show that the approach presented gives 92\% precision and 92\% recall towards the contract sentence detection.
+And they achieved 82\% of accuracy of code contract generation.
 

### 2013-01-24 03-summary/summary.tex
draft

--- 2013-01-24 03-summary/summary.tex
@@
 % the problem solved, the approach used, and the results
-This paper
+This paper \cite{bib:Pandita} addresses the problem of automating the verification process of software product based on the Application Programmint Interface (API) documents written in natual language.
+Software reuse gives software developers the ability to build larger software products with higher quality in shorter time.
+The reused software library is usually provided to the developers in the forms of source code or binary executable,
+along with the document explaining to how to use itself.
+Reading and understanding the document is important, 
+or even the only way when no source code is provided,
+to correctly use the provided functionalities.
+However, the developers are easily overlook some documents,
+and misuse some of the functions,
+which will leads to potential inconsistency between the software product and the documents.
+Many verification tools are developed to detect the inconsistence,
+however these tools only accept formal specifictions as their input.
+They can't understand documents writen in natual language.
+This paper presents an approach to fill the gap between what is needed by the existing verification tools and what the document can provide.
 
-\cite{bib:Pandita}.
+This paper developed a technique to get the code contract from the library document.
+The technique developed in this paper can read the API document,
+and output the formal specification in the form of code contract which can be accepted by several verification tools.
+Roughly, the technique is composed of two parts: contract sentence selection and code contract generation.
+These two parts can be further divided into five steps: parsing, pre-processing, text analysis, post-processing and code contract generation.
+In the parsing step, the parsor process the API documents and extracts intermediate contents of the method description, 
+such as, summary description, argument description, return description, exception dexcription and remark dexcription. 
+In the pre-processing step, the pre-processor takes the intermediate content, 
+and perform three categories of processing: meta-data augmentation, noun boosting and programming constructs and jargon handling.
+These first two steps are critical, as they can improve the results of the third step a lot.
+The third step is text analysis.
+In this step, this paper developed a text analysis engine framework, 
+and adopting an existing POS tagger to annotate POS tags for the input sentences.
+After that, they use an NLP technique, called shallow parsor to classify the sentences into semantic templates,
+based on the lexical tokens generated by the POS tagger.
+The shallow parsor also generates FOL expressions after it has done the classifiction.
+In the post-processing step, the paper does three types of semantic analysis: removing irrelevant modifiers in predicates, classifying predicates into a semantic class based on domain dictionaries, and augmenting expressions.
+In the final step, by using predefined mapping from predicates to code contracts,
+the code contract generator translates the FOL into code contracts.
+
+The author wrote a prototype to demonstrate the technique developed,
+and did three experiments to evaluate the effectiveness of the approach. 
+The experiment results show that this approach gives 92\% precision and 92\% recall towards the contract sentence detection,
+and achieves 82\% of accuracy of code contract generation.
 

### 2013-01-24 03-summary/summary.tex
first version

@@
 % the problem solved, the approach used, and the results
-This paper \cite{bib:Pandita} addresses the problem of automating the verification process of software product based on the Application Programmint Interface (API) documents written in natual language.
+This paper \cite{bib:Pandita} addresses the problem of automating the verification process of software product based on the Application Programming Interface (API) documents written in natural language.
 Software reuse gives software developers the ability to build larger software products with higher quality in shorter time.
@@
 Many verification tools are developed to detect the inconsistence,
-however these tools only accept formal specifictions as their input.
-They can't understand documents writen in natual language.
+however these tools only accept formal specifications as their input.
+They can't understand documents written in natural language.
 This paper presents an approach to fill the gap between what is needed by the existing verification tools and what the document can provide.
@@
 These two parts can be further divided into five steps: parsing, pre-processing, text analysis, post-processing and code contract generation.
-In the parsing step, the parsor process the API documents and extracts intermediate contents of the method description, 
-such as, summary description, argument description, return description, exception dexcription and remark dexcription. 
+In the parsing step, the parser process the API documents and extracts intermediate contents of the method description, 
+such as, summary description, argument description, return description, exception description and remark description. 
 In the pre-processing step, the pre-processor takes the intermediate content, 
@@
 and adopting an existing POS tagger to annotate POS tags for the input sentences.
-After that, they use an NLP technique, called shallow parsor to classify the sentences into semantic templates,
+After that, they use an NLP technique, called shallow parser to classify the sentences into semantic templates,
 based on the lexical tokens generated by the POS tagger.
-The shallow parsor also generates FOL expressions after it has done the classifiction.
+The shallow parser also generates FOL expressions after it has done the classification.
 In the post-processing step, the paper does three types of semantic analysis: removing irrelevant modifiers in predicates, classifying predicates into a semantic class based on domain dictionaries, and augmenting expressions.

### 2013-01-29 P1-bibliography/annotated_bibliography.tex
project 1: write an annotated bibliography

\documentclass{acmtrans2m}

\title{Software Verification Based on Natural Language Documents: An Annotated Bibliography}
\author{Dejun Qian}

% get rid of footnote on the first page
\def\firstfoot{}

\newenvironment{annotation}{%
  ~\vskip 0.05in                    %space before annotation
  \par\begingroup                   %begin to format the environment
  \leftskip 0.1in\rightskip 0.1in   %set margin
  \def\baselinestretch{2}           %double spacing
  \normalsize                       %font size
  \hskip 2em                        %indent
}{%
  \par\endgroup                     %end of environment
  ~\vskip 0.05in                    %space after annotation
}

\begin{document}
\maketitle
\pagestyle{plain}

This annotated bibliography discusses the techniques used to verify the consistencies
between the software and the documents written in natual language. The software could
use a variety of programming languages, like C/C++, Java, PHP and etc.. The documents
could be in the form of programming language comments, Java annotation or seperate
files.
% Definitions that are required by several of the annotations could go here too.

\nocite{*}

\bibliographystyle{acmtrans}
\bibliography{ar4gste}
\end{document}

### 2013-02-05 P2-revised-summary/summary.tex
initial version from the exercise

--- 2013-01-24 03-summary/summary.tex
@@
 \documentclass[11pt,letterpaper,oneside]{article}
-\usepackage[top=0.5in,left=1in,right=1in,bottom=1in]{geometry}
+%\usepackage[top=0.5in,left=1in,right=1in,bottom=1in]{geometry}
+\usepackage[top=0.5in,left=1.8in,right=1.8in,bottom=1in]{geometry}
 \usepackage{fancyvrb}
@@
 
-%\usepackage{setspace}
-%\doublespacing
+\usepackage{setspace}
+\doublespacing
 
-\title{summary}
+\title{Summary of "Inferring Method Specifications from Natural Language API Descriptions''}
 \author{Dejun Qian\\electronseu@gmail.com}
@@
 % the problem solved, the approach used, and the results
-This paper \cite{bib:Pandita} addresses the problem of automating the verification process of software product based on the Application Programming Interface (API) documents written in natural language.
+Pandita et al.
+\cite{bib:Pandita} address the problem of automating the verification process of software product based on the Application Programming Interface (API) documents written in natural language.
 Software reuse gives software developers the ability to build larger software products with higher quality in shorter time.

### 2013-02-05 P2-revised-summary/summary.tex
revised the summary

@@
 % the problem solved, the approach used, and the results
-Pandita et al.
-\cite{bib:Pandita} address the problem of automating the verification process of software product based on the Application Programming Interface (API) documents written in natural language.
+Pandita et al. \cite{bib:Pandita} address the problem of automating the verification process for software product, 
+using the Application Programming Interface (API) documents written in natural language as the baseline.
 Software reuse gives software developers the ability to build larger software products with higher quality in shorter time.
-The reused software library is usually provided to the developers in the forms of source code or binary executable,
-along with the document explaining to how to use itself.
-Reading and understanding the document is important, 
-or even the only way when no source code is provided,
-to correctly use the provided functionalities.
-However, the developers are easily overlook some documents,
+The reused software library is usually provided to the developers in the form of source code or binary executable,
+along with some documents explaining how to use the library.
+Reading and understanding the documents is important to correctly use the provided functionalities.
+It is even the only way when no source code is available.
+However, the developers easily overlook some documents,
 and misuse some of the functions,
-which will leads to potential inconsistency between the software product and the documents.
-Many verification tools are developed to detect the inconsistence,
+which may lead to potential inconsistency between the software product and the documents.
+Many verification tools are developed to detect the inconsistency,
 however these tools only accept formal specifications as their input.
-They can't understand documents written in natural language.
-This paper presents an approach to fill the gap between what is needed by the existing verification tools and what the document can provide.
+They cannot understand the documents written in natural language.
+Pandita et al. \cite{bib:Pandita} present an approach to fill the gap between what the existing verification tools need and what the document can provide.
 
-This paper developed a technique to get the code contract from the library document.
-The technique developed in this paper can read the API document,
+The authors develop a technique to get the code contract from the library documents.
+The technique can read the API documents,
 and output the formal specification in the form of code contract which can be accepted by several verification tools.
-Roughly, the technique is composed of two parts: contract sentence selection and code contract generation.
+The technique is composed of two parts: contract sentence selection and code contract generation.
 These two parts can be further divided into five steps: parsing, pre-processing, text analysis, post-processing and code contract generation.
-In the parsing step, the parser process the API documents and extracts intermediate contents of the method description, 
-such as, summary description, argument description, return description, exception description and remark description. 
+In the parsing step, the parser processes the API documents and extracts intermediate contents of the method description, 
+such as summary description, argument description, return description, exception description and remark description. 
 In the pre-processing step, the pre-processor takes the intermediate content, 
-and perform three categories of processing: meta-data augmentation, noun boosting and programming constructs and jargon handling.
-These first two steps are critical, as they can improve the results of the third step a lot.
-The third step is text analysis.
-In this step, this paper developed a text analysis engine framework, 
-and adopting an existing POS tagger to annotate POS tags for the input sentences.
-After that, they use an NLP technique, called shallow parser to classify the sentences into semantic templates,
+and performs three categories of processing: meta-data augmentation, noun boosting and programming constructs and jargon handling.
+These first two steps are critical as they can improve the results of the text-analysis step.
+In the text-analysis step, the authors develop a text analysis engine framework, 
+and adopt an existing Parts-Of-Speech (POS) tagger to annotate POS tags for the input sentences.
+Then, they use an Natural Language Processing (NLP) technique known shallow parser to classify the sentences into semantic templates,
 based on the lexical tokens generated by the POS tagger.
-The shallow parser also generates FOL expressions after it has done the classification.
+The shallow parser also generates First-Order Logic (FOL) expressions after it has done the classification.
 In the post-processing step, the paper does three types of semantic analysis: removing irrelevant modifiers in predicates, classifying predicates into a semantic class based on domain dictionaries, and augmenting expressions.
@@
 
-The author wrote a prototype to demonstrate the technique developed,
-and did three experiments to evaluate the effectiveness of the approach. 
-The experiment results show that this approach gives 92\% precision and 92\% recall towards the contract sentence detection,
+The author designed a prototype to demonstrate the technique developed,
+and conducted three experiments to evaluate the effectiveness of the technique. 
+The experiment results show that this technique gives 92\% precision and 92\% recall toward the contract sentence detection,
 and achieves 82\% of accuracy of code contract generation.

### 2013-02-06 04-revise-math/X5-ReviseMath.tex
initial version

\documentclass[12pt]{article}
\textwidth=35pc
\textheight=54pc
\topmargin=-3pc
\linespread{1.3}  % gives about one-and-one-half line spacing
%\linespread{1.6}	% gives about double line spacing

\begin{document}
\begin{center}
\large
\bf
Scholarship Skills 2013\\[1ex]  % an ex is the height of a letter x, and thus depends on the current font size

\Large
Revise Mathematics
\normalsize

\vspace{1ex}
Assigned Thursday 31$^{st}$ January; due Thursday, 7$^{th}$ February 2013.
\\[2pc]  % pc is the abbreviation for a pica, 1/6 inch
\end{center}

\noindent
Apply what you've learned about writing mathematics to rewrite this proof.  
Don't be afraid to \emph{rewrite} it, rather than tinker about with it in small ways.
The \LaTeX{} source for this proof is on the web site, so you can edit it to create your own version.

Please submit the PDF and the \LaTeX{} versions of your re-write to the \textit{cs669-hw @ cs.pdx.edu} mailbox.  \textbf{Please also bring a paper copy to class}; this is the version that I will grade, unless one of us is sick!

\vspace{15pt}    % pt is the abbreviation for a point, 12 pt = 1 pc

\begin{center}
\large
\textbf{The Largest Prime}
\end{center}
\normalsize
\noindent
Suppose that there were a largest prime number $p_i$. 
Then consider the product $\prod_{j=0}^{p_i-1} \; p_i-j$. 
Then $\left( \prod_{j=0}^{p_i-1} \; p_i - j \right) \,+\,1$ 
cannot be divided evenly by any of the numbers
up to $p_i$, $2,3,4,\ldots,p_i$ because each of these divides the left
factor evenly, but not the right factor, hence not their sum.
(Recall that if $a_1$ divides $a_2$ and $a_2=a_3+a_4$ then if $a_1$
divides $a_3$, it will also divide $a_4$.)  
Since we are assuming
$p_i$ is the largest prime, $\left(\prod_{j=0}^{p_i-1}
\;p_i-j\right)\,+\,1$ can have no prime factors greater than $p_i$,
hence $\left(\prod_{j=0}^{p_i-1} \;p_i-j\right)\,+\,1$ is a prime, and
it is greater than $p_i$, since $\prod_{j=0}^{p_i-1}\;p_i-j \ge p_i$.
This contradicts the maximality of $p_i$.  
Hence the assumption that
$p_i$ is the largest prime must be false, and so there is no largest
prime.

\end{document}

### 2013-02-07 04-revise-math/X5-ReviseMath.tex
revise

@@
 \noindent
-Suppose that there were a largest prime number $p_i$. 
-Then consider the product $\prod_{j=0}^{p_i-1} \; p_i-j$. 
-Then $\left( \prod_{j=0}^{p_i-1} \; p_i - j \right) \,+\,1$ 
+Suppose that there were a largest prime number $p$. 
+Then consider the product $P = \prod_{i=1}^{p} \; i$. 
+Then $P\,+\,1$ 
 cannot be divided evenly by any of the numbers
-up to $p_i$, $2,3,4,\ldots,p_i$ because each of these divides the left
+up to $p$, $2,3,4,\ldots,p$ because each of these divides the left
 factor evenly, but not the right factor, hence not their sum.
@@
 Since we are assuming
-$p_i$ is the largest prime, $\left(\prod_{j=0}^{p_i-1}
-\;p_i-j\right)\,+\,1$ can have no prime factors greater than $p_i$,
-hence $\left(\prod_{j=0}^{p_i-1} \;p_i-j\right)\,+\,1$ is a prime, and
-it is greater than $p_i$, since $\prod_{j=0}^{p_i-1}\;p_i-j \ge p_i$.
-This contradicts the maximality of $p_i$.  
+$p$ is the largest prime,
+$P\,+\,1$ can have no prime factors greater than $p$,
+hence $P\,+\,1$ is a prime, and
+it is greater than $p$, since $P \ge p$.
+This contradicts the maximality of $p$.  
 Hence the assumption that
-$p_i$ is the largest prime must be false, and so there is no largest
+$p$ is the largest prime must be false, and so there is no largest
 prime.

### 2013-02-09 P4-5-page-paper/paper.tex
begin project 3 and project 4

\documentclass[11pt,letterpaper,oneside]{article}
\usepackage[top=1in,left=1in,right=1in,bottom=1in]{geometry}
\usepackage{fancyvrb}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{url}

\title{Checking Inconsistency between Driver code and Document}
\author{Dejun Qian\\Department of Computer Science\\Portland State University\\Portland, OR 97201\\dejun@pdx.edu}

\begin{document}
\maketitle

\begin{abstract}
This report presents how we implement coDoc. 
Experiment result shows that, with our effert in this project, coDoc can provide forthfold, 
1) provide the ability to display code and document. 
2) select code based on syntax parsing.
3) make relationship between code and document.
4) analyze relationship.
\end{abstract}

% Include the motivation for your work, your approach, your goals, and a short summary of what you found/achieved/tested.
\section{Introduction}
\label{sec:introduction}
Verification for software is very important. \cite{xiao_automated_2012}.

The initial version\footnote{\texttt{\url{http://web.cecs.pdx.edu/~cs533acc/arum.git}}} has been released.

The rest of the paper is orgnized as follows. 
Section \ref{sec:methodology} introduce our implementation.
Section \ref{sec:results} gives the experiment result of our implementation. 
Section \ref{sec:conclusion} conclude our work and give some thinking towards the future.

% Explain your design / languages, libraries, and tools used, experimental design.
\section{Methodology}
\label{sec:methodology}
This section presents what we have done and how we did it.

\subsection{Build and Make existing code}
On the first stage of our work, we tried to make the software user-friendly. Basically, the following work is done,
\begin{enumerate}
\item Added Makefile and instructions.
\item Added accurate "usage" message to output.
\end{enumerate}

\begin{figure}
\begin{center}
\includegraphics[width=0.6\textwidth]{codoc.eps}
\caption{Structure of Dyninst}
\label{fig:codoc}
\end{center}
\end{figure}

How coDoc works is illustrated in Figure \ref{fig:codoc}\footnote{\texttt{from Bryan's paper \cite{xiao_automated_2012}}}. 
A \emph{point} is a location in a program.

\noindent \newline\textbf{Instrument Using Dyninst}\newline
\indent Figure \ref{fig:codoc} gives a general idea about how coDoc works.

The code used to achieve this goal is shown bellow,
\begin{Verbatim}[frame=single]
printf(``Hello world!'');
\end{Verbatim}

After downloading Elipse\footnote{\texttt{\url{http://www.eclipse.org}}}, we need install JDK.

To test this feature, we designed a test program. 
The functions implemented in the test program is listed in Table \ref{table:functions}.

\begin{table}[th]
\caption{Functions implemented in hello}
\centering
\begin{tabular}{rl}
\hline
Function & Description \\
\hline
fake & functioin never called \\
foo  & basic function \\
recursive & function call itself recursively \\
main & main function \\
\hline
\end{tabular}
\label{table:functions}
\end{table}

% This should NOT be raw data or code listings.  Instead you should present the key results from your work.  Be guided by the papers you have read this quarter - in cases where it is necessary for understanding, a small section of code might be listed, separate from the text, but more commonly an algorithm might be shown.  Results are not long tables of data, rather, one or two graphs, or tables with key rows or columns highlighted or italicized.
\section{Results}
\label{sec:results}
The result for the experiment is shown in fig.

% Based on what you have so far, what can you conclude?  What cool ideas did you think up but not have time to implement so far?
\section{Conclusions and Future Work}
\label{sec:conclusion}
There is still a great deal of opportunity to improve coDoc.

% Follow a standard ACM format for your references.  You have examples in the papers you have read.
\bibliographystyle{acm}
\bibliography{reference}

%\begin{thebibliography}{9}
%\bibitem{bib:coDoc}
%\emph{http://www.coDoc.org}
%\end{thebibliography}

\end{document}

### 2013-02-12 P4-5-page-paper/paper.tex
backup

@@
 
-\title{Checking Inconsistency between Driver code and Document}
+\title{coDoc: A Tool for Managing Relationships between Driver code and Documents}
 \author{Dejun Qian\\Department of Computer Science\\Portland State University\\Portland, OR 97201\\dejun@pdx.edu}
@@
 \begin{abstract}
-This report presents how we implement coDoc. 
+When writing software, 
+we need the documents in hand, 
+especially when we are developing driver software.
+This paper presents how we implement coDoc. 
 Experiment result shows that, with our effert in this project, coDoc can provide forthfold, 

### 2013-02-13 P4-5-page-paper/paper.tex
backup

--- 2013-02-09 P4-5-page-paper/paper.tex
@@
 \usepackage[top=1in,left=1in,right=1in,bottom=1in]{geometry}
+\usepackage{textcomp}
 \usepackage{fancyvrb}
@@
 
-\title{Checking Inconsistency between Driver code and Document}
-\author{Dejun Qian\\Department of Computer Science\\Portland State University\\Portland, OR 97201\\dejun@pdx.edu}
+\title{coDoc: A Tool for Managing Relationships between Codes and Documents}
+\author{Dejun Qian}
 
@@
 \begin{abstract}
-This report presents how we implement coDoc. 
+When writing and testing software, 
+we need the documents in hand.
+This is extremely true for software that is document intensive, 
+such as hardware driver and virtual device.
+This paper presents coDoc, 
+an integrated development environment for managing relationships between codes and documents. 
+We first describe the architecture and features of coDoc.
+We then discuss several design decisions that we faced in developing coDoc and the trade-offs in making these decisions.
+To provide perspective,
+we report our experiences in mapping two virtual network interface card (NIC) to the real NIC documents.
+\end{abstract}
+
+% Include the motivation for your work, your approach, your goals, and a short summary of what you found/achieved/tested.
+\section{Introduction}
+\label{sec:introduction}
+Documents play an important role in software engineering process,
+from requirement analysis to architecture design,
+from code written to software testing,
+from software maitentence to software updating.
+Software that relates closely to hardware devices is extremely document intensive.
+Examples of these software could be bootloader, 
+Operating System (OS) Hardware Abstraction Layer (HAL),
+virtual devices of virtual machines.
+These software should conform to hardware documents.
+A typical embedded CPU usually have documents with thousands of pages.
+A computer system usually is consisted of over ten hardware modules.
+To effectively maintain the relationships between the codes and the documents is really important for developing and verification of these software.
+
+Many work has been done to deal with the relationships between Application Programming Interface (API) documents and its client codes \cite{Pandita_inferring_2012}.
+API documents are usually well indexed by the functions or the class.
+When we are interested in a piece of code in the client software,
+we can easily find the related API document by the invoded function.
+The relationships between the client codes and the API documents are easily constructed by using the function name as the keyword.
+However, the code related to hardware and its documents are usually related in a different way.
+The main reason is that the hardware document usually talks about how to use the hardware,
+more specifically how to program the registers inside the hardware module.
+Different from the API document,
+we can not locate the document for a piece of hardware related code, and vice versa,
+because there exists no similar keywork like the function name or the class name.
+
+The hardware documents differ from the API documents in the following ways,
+\begin{itemize}
+\item the hardware documents are usually published as pdf files, while the API documents are usually html files
+\item the hardware documents are composed of texts, tables and diagrams, while the API documents are usually texts only
+\item hard for the computer to relate the document piece to the code piece automatically
+\end{itemize}
+
+These differences make the construction of the relationships between the hardware related codes and their documents really challenging.
+This paper presents coDoc, a tool to easily create, maintain, and display the relationships.
+
+One way to construct the relationship for hardware related code and its documents is to use machine learning method.
+This method need the seed data to train the model.
+
 Experiment result shows that, with our effert in this project, coDoc can provide forthfold, 
@@
 4) analyze relationship.
-\end{abstract}
-
-% Include the motivation for your work, your approach, your goals, and a short summary of what you found/achieved/tested.
-\section{Introduction}
-\label{sec:introduction}
-Verification for software is very important. \cite{xiao_automated_2012}.
 

### 2013-02-13 P4-5-page-paper/paper.tex
backup

@@
 These differences make the construction of the relationships between the hardware related codes and their documents really challenging.
+To our knowlege, there is no tool exists to address this problem.
+People usually write down the position of the related document piece in the document as a comment of the code.
+This is a simple workaround as no easier tools are available.
+However, this method can only handle simple situations.
+If there are thousands of these comments, 
+and there are cluttered over in the code,
+then it will be very hard to manage.
 This paper presents coDoc, a tool to easily create, maintain, and display the relationships.
+% The initial version\footnote{\texttt{\url{git@github.com:derekqian/coDoc.git}}} has been released.
+The key features of coDoc are as follows,
+\begin{itemize}
+\item provide the ability to display code and document. 
+\item select code based on syntax parsing.
+\item stable to the change of unrelated code.
+\item make relationship between code and document.
+\item display the relationship.
+\end{itemize}
 
-One way to construct the relationship for hardware related code and its documents is to use machine learning method.
-This method need the seed data to train the model.
-
-Experiment result shows that, with our effert in this project, coDoc can provide forthfold, 
-1) provide the ability to display code and document. 
-2) select code based on syntax parsing.
-3) make relationship between code and document.
-4) analyze relationship.
-
-The initial version\footnote{\texttt{\url{http://web.cecs.pdx.edu/~cs533acc/arum.git}}} has been released.
+Using coDoc, we have created relationships for to virtual NIC devices fo qemu.
+These two devices are DIO and E100.
 
 The rest of the paper is orgnized as follows. 
-Section \ref{sec:methodology} introduce our implementation.
-Section \ref{sec:results} gives the experiment result of our implementation. 
+Section \ref{sec:background} introduce the background of poppler and CDT.
+Section \ref{sec:arch} provides the overall architecture and key features of coDoc.
+Section \ref{sec:decision} gives the design decisions of coDoc and the trade-offs of these decisions.
+Section \ref{sec:evaluation} summarizes our experiences of creating and maitaining the relationships for two virtual devices.
+Section \ref{sec:related} presents the related work.
 Section \ref{sec:conclusion} conclude our work and give some thinking towards the future.
@@
 % Explain your design / languages, libraries, and tools used, experimental design.
-\section{Methodology}
-\label{sec:methodology}
-This section presents what we have done and how we did it.
+\section{Background}
+\label{sec:background}
+\subsection{poppler}
+We adopt poppler, a open-source pdf render, to render pdf content in coDoc.
+This PDF render is written in C++, 
+and is widely used in Linux systems.
+It uses Cairo and GTK to draw the rendered content.
+
+\subsection{C Development Tool}
+CDT is an Eclipse plugin which supports C/C++ syntax parsing.
+It is written in Java and provide Eclipse with the ability of syntax highlighting and code completion when developing C/C++ code.
+
+% This should NOT be raw data or code listings.
+Instead you should present the key arch from your work.
+Be guided by the papers you have read this quarter - in cases where it is necessary for understanding, a small section of code might be listed, separate from the text, but more commonly an algorithm might be shown.
+Result are not long tables of data, rather, one or two graphs, or tables with key rows or columns highlighted or italicized.
+\section{Architecture and Features of coDoc}
+\label{sec:arch}
+The result for the experiment is shown in fig.
 
@@
 
-% This should NOT be raw data or code listings.
-Instead you should present the key results from your work.
-Be guided by the papers you have read this quarter - in cases where it is necessary for understanding, a small section of code might be listed, separate from the text, but more commonly an algorithm might be shown.
-Results are not long tables of data, rather, one or two graphs, or tables with key rows or columns highlighted or italicized.
-\section{Results}
-\label{sec:results}
+\section{Methodology and Design Decisions}
+\label{sec:decision}
+The result for the experiment is shown in fig.
+
+\section{Evaluation}
+\label{sec:evaluation}
+The result for the experiment is shown in fig.
+
+\section{Related Work}
+\label{sec:related}
 The result for the experiment is shown in fig.
@@
 There is still a great deal of opportunity to improve coDoc.
+
+One way to construct the relationship for hardware related code and its documents is to use machine learning method.
+This method need the seed data to train the model.
 

### 2013-02-14 P4-5-page-paper/paper.tex
backup

@@
 \label{sec:arch}
-The result for the experiment is shown in fig.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.55\textwidth]{architecture.eps}
+\caption{coDoc Architecture and Features}
+\label{fig:architecture}
+\end{center}
+\end{figure}
+
+The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
+It contains CDT editor, poppler, PDF editor and multi-editor.
+There are three kinds of data here, 1) the codes, 2) the documents, 3) the relationships.
+We only handle C/C++ code at this time, 
+as most system code are written in this language.
+CDT editor reads and parses the codes, 
+highlights syntax elements.
+We use poppler to read the pdf file and render the pdf pages to images.
+As poppler is developed in C++, and Eclipse RCP is in Java language,
+we need a adaptor to bridge the C++ code and the Java code.
+We use JNI to implement this adaptor.
+PDF editor implements an adaptor, 
+and use it to get the PDF page from poppler and display it.
+The multi-editor is responsible to read the relationship data,
+and highlight certain code piece and document piece respectively.
+
+To represent a relationship, 
+we first need to define the strategy to identify the code piece and document piece.
+As
+
+% convert platformview.png platformview.eps
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{platformview.eps}
+\caption{coDoc Platform View}
+\label{fig:platformview}
+\end{center}
+\end{figure}
 

### 2013-02-14 P4-5-page-paper/paper.tex
backup

@@
 
+The main contributions of this paper are list as follows,
+\begin{itemize}
+\item address the diffeculty of remain the integrity of the relationships when codes change
+\item present a standard format for the code piece identifier
+\item a standard format for the document piece identifier
+\item a standard format for the relationship between the code and document
+\item implement coDoc which adopts these standard formats
+\end{itemize}
+
 The rest of the paper is orgnized as follows. 
@@
 and highlight certain code piece and document piece respectively.
-
 To represent a relationship, 
 we first need to define the strategy to identify the code piece and document piece.
-As
+
+\subsection{Identifying the Code Piece}
+The codes are always evolving during its lifetime.
+We don't want our relationships created for one version stopped working for other version.
+This goal call for a robust identifying strategy for the code piece.
+Our first method used to identify the code piece is to record the offset of the select code from the beginning of the code file and the selected length.
+This method is straight forward and is easy to understand and implement.
+However, this method definitely will violate the robust requirement.
+To achieve the goal, we need to find some properties of the code that are relatively stable when code evolves.
+These properties should also can serve as the key to uniquely identify the code piece.
+The intuitive thought is to use the semantic information,
+as it describes the intrinsical meaning of the code.
+However, there is no formal method to describe this information.
+We use syntax information in our approach to form the main element of our identifier.
+The code can be parsed and represented by a syntax tree.
+The change of the code in one branch will usually not affect the code branch in the other.
+If we can identify the code piece based on the position in the syntax tree,
+we can design a robust method to identify the code piece.
+To make the method more robust,
+we can introduce the information in the first method as the second key.
+When the syntax identifier fails to locate the code piece,
+we can use the offset information to assited the decision.
+We also include in the identifier the content for the integrity check.
+The structure used to achieve this goal is shown bellow,
+\begin{Verbatim}[frame=single]
+class CodeSelection {
+  private String syntaxcodepath;
+  private String selcodepath;
+  private String syntaxcodetext;
+  private String selcodetext;
+}
+\end{Verbatim}
+
+\section{Methodology and Design Decisions}
+\label{sec:decision}
+\subsection{Embedded vs Seperate for PDF Reader}
+The tool should display both codes and documents at the same time.
+We can implement the code viewer and the PDF viewer in seperate process,
+and use inner process communication (IPC) techniques to synchronize.
+The advantage of this method is that each windows is in their own window,
+can ocuppy the whole screen,
+and display more content which eliminate the need to scroll the window horizontally.
+When the user uses a computer with dual monitor,
+the tool implementing this method is extremely a good choice,
+as the user can choose to display the code and the document in seperate moniter.
+However, this implementation is heavy,
+and get performance issues.
+When using the tool, 
+the user may need to launch the PDF reader,
+which is slow.
+Our earlier implementation use this method,
+and encountered a lot of synchronization problems oriatated from the IPC communication.
+In coDoc, we choose to implement the code viewer and the code viewer in the same process.
+This way, all the commucations are done in the same process.
+%The Eclipse framework even makes the whole system single thread.
+No IPC communication is needed,
+which is more efficient and makes the tool more user-friendly.
+With the new method, we can smoothly operate the tool without any uncomfortable feeling.
+The advantage of the first method come the disadvantage of the new method,
+as the code viwer and the document viwer should share the whole screen now.
+However, with a efficient and user-friendly screen split strategy and screen area assignment method,
+we can make the user feel less uncomfortable when viewing the content.
+Also, most programmer now not only are using dual moniters, 
+but also the moniters they are using are larger and larger.
+Using a larger moniter with high definition will make this disadvantage point nothing.
+And even better, in this situation, this method will overcome the first method,
+as moving the eyes between two big moniter is energy consuming.
+
+\subsection{Relationship Store Model}
+In coDoc, we store the relationship data in XML file, 
+instead of the SQL database.
+The reason that we didn't use a SQL database is that the relationships is semi-structured,
+as we decide to store the content along with the identifier.
+The content is used to further check the integrity.
+XML database is very suitable for our semi-structured data here.
+
+\section{Evaluation}
+\label{sec:evaluation}
+\textbf{Effectiveness.} We have evaluated coDoc by mapping two virtual devices and their related document.
+The number of relationships created and the time used to created these relationships is listed in Table \ref{table:evaluate}.
+
+\begin{table}[th]
+\caption{Evaluate Result}
+\centering
+\begin{tabular}{rcc}
+\hline
+Code & \# of Relationships & time(hr) \\
+\hline
+dio & 108 & 2 \\
+e100  & 213 & 4\\
+\hline
+\end{tabular}
+\label{table:evaluate}
+\end{table}
+
+The fine granularity of the identifying method makes the relationship results very accurate, 
+80\% of the code piece are marked inside the statement.
+This result is hard for comment based method to achieve.
+The same result happens for the document.
+In the whole relationships, 
+90\% of the document pieces are marked as on cell in a table.
+The comments in the PDF file will be too crowd to be useful,
+as it will affect the normal reading of the document.
+Our approach can also make the development efficient,
+as we don't need the developer to change both the code and the document when only relationship is created.
+This makes the code and document neat and easily to read and understand,
+and will them be understand effeciently.
+
+\noindent \textbf{Usability.} We implement coDoc as an Elipse\footnote{\texttt{\url{http://www.eclipse.org}}} Rich Client Program (RCP), 
+which can make our tool share the user style with Elipse that is acustomed by many programmer.
+Figure \ref{fig:platformview} is the screenshot of the tool.
+Three persons with no exprience with coDoc before have successfully use this tool to created the relationships for their codes and documents.
+They didn't find any difficulties when using this tool.
+All the feedbacks are positive regarding to the use of the tool.
+Now they can easily create their relationships by selecting the code and document piece using mouse, input the comment using keyboard.
+They can also manage the relationships by sorting by attributes, search certain relationships by keywords.
+They also find the feature that allow to categorize the relationships helpful,
+as it makes the relationships more neat when the number of relationships is large.
+
+In our own experience, we found that the ability to see the codes, 
+the documents and the relationships in the same screen really saves a lot of time,
+as we don't need to switch between different softwares.
+The visualized interface also saved us time to learn the detailed syntax about the identifier formats,
+and to write the identifier manually.
+We believe this tool will lead to increased productivity.
 
@@
 
-\subsection{Build and Make existing code}
-On the first stage of our work, we tried to make the software user-friendly. Basically, the following work is done,
-\begin{enumerate}
-\item Added Makefile and instructions.
-\item Added accurate "usage" message to output.
-\end{enumerate}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.6\textwidth]{codoc.eps}
-\caption{Structure of Dyninst}
-\label{fig:codoc}
-\end{center}
-\end{figure}
-
-How coDoc works is illustrated in Figure \ref{fig:codoc}\footnote{\texttt{from Bryan's paper \cite{xiao_automated_2012}}}. 
-A \emph{point} is a location in a program.
-
-\noindent \newline\textbf{Instrument Using Dyninst}\newline
-\indent Figure \ref{fig:codoc} gives a general idea about how coDoc works.
-
-The code used to achieve this goal is shown bellow,
-\begin{Verbatim}[frame=single]
-printf(``Hello world!'');
-\end{Verbatim}
-
-After downloading Elipse\footnote{\texttt{\url{http://www.eclipse.org}}}, we need install JDK.
-
-To test this feature, we designed a test program. 
-The functions implemented in the test program is listed in Table \ref{table:functions}.
-
-\begin{table}[th]
-\caption{Functions implemented in hello}
-\centering
-\begin{tabular}{rl}
-\hline
-Function & Description \\
-\hline
-fake & functioin never called \\
-foo  & basic function \\
-recursive & function call itself recursively \\
-main & main function \\
-\hline
-\end{tabular}
-\label{table:functions}
-\end{table}
-
-\section{Methodology and Design Decisions}
-\label{sec:decision}
-The result for the experiment is shown in fig.
-
-\section{Evaluation}
-\label{sec:evaluation}
-The result for the experiment is shown in fig.
-
 \section{Related Work}
 \label{sec:related}
-The result for the experiment is shown in fig.
+Current tools can manage codes. 
+These kinds of tools include revision control software like git, svn. 
+Revision tools can give the evolving history of the software.
+These tools usually adopt text comparation tools to figure out the differences between the versions of the software.
+The comparation tools can easily give the result about the match points and mismatch points in the codes,
+which means they can manage the relationships between different versions of codes.
+However, these tools are not designed to manage documents.
+Though some people also use them to manage documents,
+they only use it as a persistent data warehouse.
+They can not take the advantages of the comparation tools, 
+as these tool usually can only cope with text file.
+People are using code comments to record the related document piece.
+However, no consistent format exists,
+which makes these information not managable,
+especially when these comments are made by many different developers.
+
+Full text indexing system is developed to processing documents.
+However, they can only relate the keyword to certain documents.
+They do not deal with both codes and documents. 
+Like full text indexing system,
+search engines also work with documents in similar way.
+Most of the documents that are dealed by search engines are web pages.
+Many PDF readers can support highlighting and commenting.
+With these features, we can relate a document piece to a code piece.
+However, these links created are not stable,
+and the PDF readers can not check the integrity of these information.
+
+Generally speaking, these are tools can either handle code management or document management.
+However, they are not designed to do both,
+and managing the mixture of codes and documents is definitely a mission impossible task for them.
 
@@
 \label{sec:conclusion}
-There is still a great deal of opportunity to improve coDoc.
+We implement coDoc, 
+a tool to managing the relationships between the hardware related codes and their documents.
+The main contributions in this paper are the method to identify the code piece.
+Our experiences of using coDoc to manage two virtual device codes and their documents show the tool is robust and efficent,
+and is helpful when developing the virtual devices.
+It can remain stable respect to the evolution of the codes.
 
-One way to construct the relationship for hardware related code and its documents is to use machine learning method.
+There is still a great deal of opportunity to improve coDoc, 
+\begin{enumerate}
+\item combine it with revision control tools to provide a more user-friendly tool suit for developing and maitaining the codes while managing the documents at the same time.
+\item more robust method to identify the document piece in the PDF document to make the tool invariant to the change of the document.
+\item one way to construct the relationship for hardware related code and its documents is to use machine learning method.
 This method need the seed data to train the model.
+\end{enumerate}
 

### 2013-02-19 P4-5-page-paper/paper.tex
backup
double space

@@
 \documentclass[11pt,letterpaper,oneside]{article}
-\usepackage[top=1in,left=1in,right=1in,bottom=1in]{geometry}
+%\usepackage[top=1in,left=1in,right=1in,bottom=1in]{geometry}
+\usepackage[top=0.5in,left=1.8in,right=1.8in,bottom=0.7in]{geometry}
 \usepackage{textcomp}
@@
 
+\usepackage{setspace}
+\doublespacing
+
 \title{coDoc: A Tool for Managing Relationships between Codes and Documents}
-\author{Dejun Qian}
+\author{Dejun Qian\\electronseu@gmail.com}
+
+\date{}
 
@@
 This paper presents coDoc, 
-an integrated development environment for managing relationships between codes and documents. 
+an integrated development environment for managing relationships between codes and documents, as well as developing the codes. 
 We first describe the architecture and features of coDoc.

### 2013-02-19 P4-5-page-paper/paper.tex
backup

@@
 This is extremely true for software that is document intensive, 
-such as hardware driver and virtual device.
+such as hardware driver and virtual device modules.
 This paper presents coDoc, 
 an integrated development environment for managing relationships between codes and documents, as well as developing the codes. 
-We first describe the architecture and features of coDoc.
+We first describe the architecture and the features of coDoc.
 We then discuss several design decisions that we faced in developing coDoc and the trade-offs in making these decisions.
 To provide perspective,
-we report our experiences in mapping two virtual network interface card (NIC) to the real NIC documents.
+we report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents.
 \end{abstract}
@@
 from requirement analysis to architecture design,
-from code written to software testing,
-from software maitentence to software updating.
+from code writting to software testing,
+from software maintainence to software upgrading.
 Software that relates closely to hardware devices is extremely document intensive.
@@
 virtual devices of virtual machines.
-These software should conform to hardware documents.
+These software should conform to hardware documents to operate correctly.
 A typical embedded CPU usually have documents with thousands of pages.
-A computer system usually is consisted of over ten hardware modules.
+A computer system usually consistes of over ten hardware modules.
 To effectively maintain the relationships between the codes and the documents is really important for developing and verification of these software.
 
-Many work has been done to deal with the relationships between Application Programming Interface (API) documents and its client codes \cite{Pandita_inferring_2012}.
+Much work has been done to deal with the relationships between Application Programming Interface (API) documents and their client codes \cite{Pandita_inferring_2012}.
 API documents are usually well indexed by the functions or the class.

### 2013-02-19 P4-5-page-paper/paper.tex
backup

@@
 Much work has been done to deal with the relationships between Application Programming Interface (API) documents and their client codes \cite{Pandita_inferring_2012}.
-API documents are usually well indexed by the functions or the class.
+API documents are usually well indexed by the functions or the classes.
 When we are interested in a piece of code in the client software,
-we can easily find the related API document by the invoded function.
-The relationships between the client codes and the API documents are easily constructed by using the function name as the keyword.
-However, the code related to hardware and its documents are usually related in a different way.
-The main reason is that the hardware document usually talks about how to use the hardware,
-more specifically how to program the registers inside the hardware module.
-Different from the API document,
-we can not locate the document for a piece of hardware related code, and vice versa,
-because there exists no similar keywork like the function name or the class name.
-
+we can easily find the related API documents by the name of the functions that the piece of code calls.
+The relationships between the client codes and the API documents can be easily constructed by using the function names as the keywords.
+However, the codes related to hardware and their documents are usually related in different ways.
+The hardware documents usually talk about how to use the hardware,
+more specifically how to program the registers inside the hardware modules.
 The hardware documents differ from the API documents in the following ways,
 \begin{itemize}
-\item the hardware documents are usually published as pdf files, while the API documents are usually html files
-\item the hardware documents are composed of texts, tables and diagrams, while the API documents are usually texts only
-\item hard for the computer to relate the document piece to the code piece automatically
+\item the hardware documents are usually published as pdf files, while the API documents are usually html files.
+\item the hardware documents are composed of texts, tables and diagrams, while the API documents are usually texts only.
+\item the hardware docuemnts are not orgnized by functions or classes, which are basic elements of codes.
+\item hard for the computer to relate the hardware document pieces to the code pieces automatically.
 \end{itemize}
 
-These differences make the construction of the relationships between the hardware related codes and their documents really challenging.
-To our knowlege, there is no tool exists to address this problem.
-People usually write down the position of the related document piece in the document as a comment of the code.
-This is a simple workaround as no easier tools are available.
+These differences make the constructing of the relationships between the hardware related codes and their documents really challenging.
+To our knowlege, there is no tools exist to address this problem.
+A simple workaround used is to include the positions of the related document pieces in the documents as comments the codes.
 However, this method can only handle simple situations.
-If there are thousands of these comments, 
-and there are cluttered over in the code,
-then it will be very hard to manage.
+If there are thousands of these comments cluttered in the codes,
+it will be very hard to manage them.
 This paper presents coDoc, a tool to easily create, maintain, and display the relationships.
@@
 \begin{itemize}
-\item provide the ability to display code and document. 
-\item select code based on syntax parsing.
-\item stable to the change of unrelated code.
-\item make relationship between code and document.
-\item display the relationship.
+\item provide the ability to display codes and documents.
+\item provide the ability to develop codes.
+\item select code pieces based on syntax tree of the code.
+\item code selections are stable to the changes of unrelated codes.
+\item create relationships between codes and documents.
+\item manage and display the relationships.
 \end{itemize}
 
-Using coDoc, we have created relationships for to virtual NIC devices fo qemu.
+Using coDoc, we have created relationships for two virtual NIC devices in QEMU.
 These two devices are DIO and E100.
 
-The main contributions of this paper are list as follows,
+The main contributions of this paper are listed as follows,
 \begin{itemize}
-\item address the diffeculty of remain the integrity of the relationships when codes change
-\item present a standard format for the code piece identifier
-\item a standard format for the document piece identifier
-\item a standard format for the relationship between the code and document
-\item implement coDoc which adopts these standard formats
+\item design a framework to display and manage codes, documents and relationships.
+\item remain integrity of the relationships when the codes evolve.
+\item present a standard format for the code piece identifier.
+\item a standard format for the document piece identifier.
+\item a standard format for the relationship between the code and document.
+\item implement coDoc which adopts these standard formats.
 \end{itemize}
@@
 The rest of the paper is orgnized as follows. 
-Section \ref{sec:background} introduce the background of poppler and CDT.
+Section \ref{sec:background} introduces the background of poppler and CDT.
 Section \ref{sec:arch} provides the overall architecture and key features of coDoc.
@@
 Section \ref{sec:related} presents the related work.
-Section \ref{sec:conclusion} conclude our work and give some thinking towards the future.
+Section \ref{sec:conclusion} concludes our work and gives some thinking towards the future.
 
-% Explain your design / languages, libraries, and tools used, experimental design.
 \section{Background}
@@
 \subsection{poppler}
-We adopt poppler, a open-source pdf render, to render pdf content in coDoc.
+We adopt poppler, a open-source PDF render, to render PDF content in coDoc.
 This PDF render is written in C++, 
@@
 
-\subsection{C Development Tool}
-CDT is an Eclipse plugin which supports C/C++ syntax parsing.
-It is written in Java and provide Eclipse with the ability of syntax highlighting and code completion when developing C/C++ code.
+\subsection{C/C++ Development Tool}
+C/C++ Development Tool (CDT) is an Eclipse plugin which supports C/C++ syntax parsing.
+It is written in Java and provides Eclipse with the ability of syntax highlighting and code completing when developing C/C++ codes.
 
-% This should NOT be raw data or code listings.
-Instead you should present the key arch from your work.
-Be guided by the papers you have read this quarter - in cases where it is necessary for understanding, a small section of code might be listed, separate from the text, but more commonly an algorithm might be shown.
-Result are not long tables of data, rather, one or two graphs, or tables with key rows or columns highlighted or italicized.
 \section{Architecture and Features of coDoc}
@@
 highlights syntax elements.
-We use poppler to read the pdf file and render the pdf pages to images.
+We use poppler to read the PDF file and render the PDF pages to images.
 As poppler is developed in C++, and Eclipse RCP is in Java language,
-we need a adaptor to bridge the C++ code and the Java code.
+we need an adaptor to bridge the C++ code and the Java code.
 We use JNI to implement this adaptor.
 PDF editor implements an adaptor, 
-and use it to get the PDF page from poppler and display it.
+and uses it to get the PDF page from poppler and displays the page.
 The multi-editor is responsible to read the relationship data,
@@
 The codes are always evolving during its lifetime.
-We don't want our relationships created for one version stopped working for other version.
-This goal call for a robust identifying strategy for the code piece.
-Our first method used to identify the code piece is to record the offset of the select code from the beginning of the code file and the selected length.
+We don't want our relationships created for one version stop working for other versions.
+This goal calls for a robust identifying strategy for the code piece.
+Our first method identifies the code piece as the offset of the selected code from the beginning of the code file and the selected length.
 This method is straight forward and is easy to understand and implement.
@@
 To achieve the goal, we need to find some properties of the code that are relatively stable when code evolves.
-These properties should also can serve as the key to uniquely identify the code piece.
+These properties should also can serve as a key to uniquely identify the code piece.
 The intuitive thought is to use the semantic information,
@@
 However, there is no formal method to describe this information.
-We use syntax information in our approach to form the main element of our identifier.
+We use syntax information to form the main element of our identifier.
 The code can be parsed and represented by a syntax tree.
-The change of the code in one branch will usually not affect the code branch in the other.
+The change of the code in one branch will usually not affect the code in the other branches.
 If we can identify the code piece based on the position in the syntax tree,
@@
 To make the method more robust,
-we can introduce the information in the first method as the second key.
+we can introduce the information in the first method as the secondary key.
 When the syntax identifier fails to locate the code piece,
-we can use the offset information to assited the decision.
-We also include in the identifier the content for the integrity check.
+we can use the offset information to assist the decision.
+We also include in the identifier the content of the code piece for the integrity check.
 The structure used to achieve this goal is shown bellow,
@@
 and use inner process communication (IPC) techniques to synchronize.
-The advantage of this method is that each windows is in their own window,
+The advantage of this method is that each process has its own window,
 can ocuppy the whole screen,
-and display more content which eliminate the need to scroll the window horizontally.
-When the user uses a computer with dual monitor,
+and display more content which reduces the need to scroll the window horizontally.
+When the user uses a computer with two monitors,
 the tool implementing this method is extremely a good choice,
@@
 With the new method, we can smoothly operate the tool without any uncomfortable feeling.
-The advantage of the first method come the disadvantage of the new method,
+The advantage of the first method become the disadvantage of the new method,
 as the code viwer and the document viwer should share the whole screen now.
@@
 we can make the user feel less uncomfortable when viewing the content.
-Also, most programmer now not only are using dual moniters, 
+Also, most programmer now not only are using two moniters, 
 but also the moniters they are using are larger and larger.
-Using a larger moniter with high definition will make this disadvantage point nothing.
+Using a larger moniter with high definition will make this disadvantage nothing.
 And even better, in this situation, this method will overcome the first method,
@@
 \label{sec:evaluation}
-\textbf{Effectiveness.} We have evaluated coDoc by mapping two virtual devices and their related document.
-The number of relationships created and the time used to created these relationships is listed in Table \ref{table:evaluate}.
+\textbf{Effectiveness.} We have evaluated coDoc by mapping two virtual devices and their related documents.
+The number of relationships created and the time used to created these relationships are listed in Table \ref{table:evaluate}.
 
@@
 The fine granularity of the identifying method makes the relationship results very accurate, 
-80\% of the code piece are marked inside the statement.
-This result is hard for comment based method to achieve.
+80\% of the code pieces are marked inside the statement.
+This result is hard for comment-based method to achieve.
 The same result happens for the document.
 In the whole relationships, 
-90\% of the document pieces are marked as on cell in a table.
+90\% of the document pieces are marked on cells in the tables.
 The comments in the PDF file will be too crowd to be useful,
@@
 Our approach can also make the development efficient,
-as we don't need the developer to change both the code and the document when only relationship is created.
-This makes the code and document neat and easily to read and understand,
-and will them be understand effeciently.
+as we don't need the developer to change either the code or the document while only relationship is created.
+This makes the code and document neat and easily to read and understand.
 
 \noindent \textbf{Usability.} We implement coDoc as an Elipse\footnote{\texttt{\url{http://www.eclipse.org}}} Rich Client Program (RCP), 
-which can make our tool share the user style with Elipse that is acustomed by many programmer.
+which can make our tool share the use style with Elipse that is acustomed by many programmer.
 Figure \ref{fig:platformview} is the screenshot of the tool.
-Three persons with no exprience with coDoc before have successfully use this tool to created the relationships for their codes and documents.
+Three persons with no exprience with coDoc before have successfully use this tool to create the relationships for their codes and documents.
 They didn't find any difficulties when using this tool.
@@
 They can also manage the relationships by sorting by attributes, search certain relationships by keywords.
-They also find the feature that allow to categorize the relationships helpful,
-as it makes the relationships more neat when the number of relationships is large.
+They also find the feature that allow them to categorize the relationships helpful.
+This feature makes the relationships more neat when the number of relationships is large.
 
@@
 the documents and the relationships in the same screen really saves a lot of time,
-as we don't need to switch between different softwares.
+as we don't need to switch between different tools.
 The visualized interface also saved us time to learn the detailed syntax about the identifier formats,
@@
 These kinds of tools include revision control software like git, svn. 
-Revision tools can give the evolving history of the software.
-These tools usually adopt text comparation tools to figure out the differences between the versions of the software.
-The comparation tools can easily give the result about the match points and mismatch points in the codes,
+Revision control tools can give the evolving history of the software.
+These tools usually adopt text comparison tools to figure out the differences between different versions of the software.
+The comparation tools can easily give the result about the matching points and mismatching points in the codes,
 which means they can manage the relationships between different versions of codes.
@@
 they only use it as a persistent data warehouse.
-They can not take the advantages of the comparation tools, 
-as these tool usually can only cope with text file.
+They can not take the advantages of the comparison tools, 
+as these tool usually can only deal with text file.
 People are using code comments to record the related document piece.
@@
 Full text indexing system is developed to processing documents.
-However, they can only relate the keyword to certain documents.
+However, they can only relate keywords to certain documents.
 They do not deal with both codes and documents. 
@@
 search engines also work with documents in similar way.
-Most of the documents that are dealed by search engines are web pages.
+Most of the documents that are handled by search engines are web pages.
 Many PDF readers can support highlighting and commenting.
@@
 However, these links created are not stable,
-and the PDF readers can not check the integrity of these information.
+and PDF readers can not check the integrity of these information.
 
-Generally speaking, these are tools can either handle code management or document management.
+Generally speaking, these are tools can either do code management or do document management.
 However, they are not designed to do both,
-and managing the mixture of codes and documents is definitely a mission impossible task for them.
+and managing the relationships between codes and documents is definitely a mission impossible task for them.
 
@@
 Our experiences of using coDoc to manage two virtual device codes and their documents show the tool is robust and efficent,
-and is helpful when developing the virtual devices.
-It can remain stable respect to the evolution of the codes.
+and is helpful when developing and maitaining the virtual devices.
+The relationships remain stable respect to the evolution of the codes.
 
-There is still a great deal of opportunity to improve coDoc, 
+There are still opportunities to improve coDoc, 
 \begin{enumerate}
 \item combine it with revision control tools to provide a more user-friendly tool suit for developing and maitaining the codes while managing the documents at the same time.
-\item more robust method to identify the document piece in the PDF document to make the tool invariant to the change of the document.
-\item one way to construct the relationship for hardware related code and its documents is to use machine learning method.
-This method need the seed data to train the model.
+\item more robust method to identify the document pieces in the PDF documents to make the tool invariant to the change of the documents.
+\item use machine learning method (use the data created as seed to train the model) to construct and check the relationships between hardware related codes and their documents.
 \end{enumerate}

### 2013-02-21 05-graphics/graphics.tex
exercise 5

\documentclass[11pt,letterpaper,oneside]{article}
\usepackage[top=0.5in,left=1in,right=1in,bottom=1in]{geometry}
\usepackage{fancyvrb}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{url}

\title{Good and Bad Graphics}
\author{Dejun Qian\\electronseu@gmail.com}

\date{}

\begin{document}
\maketitle

% Explain the source of the graphic and the idea you think the author was trying to represent.
% Create a digital version of the graphic (for example a pdf or png (portable network graphics) file)
% Explain why you think the graphic is a good or bad representation of the idea.

I got the two graphics by searching in Google Image using keyword ``teach''. Google Image gives a bunch of images. I choose one that I think is good and one that I think is bad. Both of these two graphics are trying to illustrate the meaning of ``teach''.

Figure \ref{fig:good} \cite{bib:good} is the good one. The graphic directly shows one teacher is teaching two students. The meaning is very straightforward. The graphic is composed of simple elements, like cricles and rectangles, which makes the meaning of the graphic stand out.

\begin{figure}
\begin{center}
\includegraphics[width=0.55\textwidth]{teaching.eps}
\caption{A Good Graphic Explaining Teaching}
\label{fig:good}
\end{center}
\end{figure}

Figure \ref{fig:bad} \cite{bib:bad} is the bad one. From this graphic, I cannot see the meaning of ``teach''. The apple tells nothing about teaching. The blackboard and the chalk are related to teaching. However, it is not straightforward for me to get the meaning of ``teach''.

\begin{figure}
\begin{center}
\includegraphics[width=0.55\textwidth]{teach-for-america.eps}
\caption{A Bad Graphic Explaining Teaching}
\label{fig:bad}
\end{center}
\end{figure}

\bibliographystyle{acm}
\bibliography{reference}

\end{document}

### 2013-02-22 P4-5-page-paper/paper.tex
backup

@@
 
-\title{coDoc: A Tool for Managing Relationships between Codes and Documents}
+\title{coDoc: A Tool for Managing Relationships between Code and Documentation}
 \author{Dejun Qian\\electronseu@gmail.com}
@@
 When writing and testing software, 
-we need the documents in hand.
-This is extremely true for software that is document intensive, 
-such as hardware driver and virtual device modules.
+lacking of the ability to efficiently refer to the related documentation hinders the productivity largely.
+This is particularly true for software that is documentation-intensive, 
+such as hardware drivers and virtual device modules.
 This paper presents coDoc, 
-an integrated development environment for managing relationships between codes and documents, as well as developing the codes. 
-We first describe the architecture and the features of coDoc.
-We then discuss several design decisions that we faced in developing coDoc and the trade-offs in making these decisions.
-To provide perspective,
-we report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents.
+an integrated development environment for managing relationships between code and documentation, while developing the code. 
+We describe the architecture and features of coDoc,
+and discuss several design decisions that we faced in developing coDoc and the trade-offs involved in making these decisions.
+We report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents by coDoc.
 \end{abstract}
 
-% Include the motivation for your work, your approach, your goals, and a short summary of what you found/achieved/tested.
 \section{Introduction}
 \label{sec:introduction}
-Documents play an important role in software engineering process,
-from requirement analysis to architecture design,
-from code writting to software testing,
-from software maintainence to software upgrading.
-Software that relates closely to hardware devices is extremely document intensive.
-Examples of these software could be bootloader, 
-Operating System (OS) Hardware Abstraction Layer (HAL),
-virtual devices of virtual machines.
-These software should conform to hardware documents to operate correctly.
-A typical embedded CPU usually have documents with thousands of pages.
-A computer system usually consistes of over ten hardware modules.
-To effectively maintain the relationships between the codes and the documents is really important for developing and verification of these software.
+Documents play an important role in the software engineering process,
+from requirements analysis to architecture design,
+from coding to software testing,
+from software debugging to software maintenance.
+Software that relates closely to hardware devices is extremely document intensive. % explain why
+Examples of such software include bootloaders, 
+Operating System (OS) Hardware Abstraction Layers (HAL),
+and virtual devices for virtual machines.
+Such software must follow the hardware documentation to operate correctly.
+A typical embedded CPU might have documentation consisting of thousands of pages.
+A computer system usually consists of more than ten hardware modules.
+Effectively maintaining the relationships between the code and the documentation is important for developing and verifying such software. % which software
 
-Much work has been done to deal with the relationships between Application Programming Interface (API) documents and their client codes \cite{Pandita_inferring_2012}.
-API documents are usually well indexed by the functions or the classes.
+Much work has been done to handle the relationships between Application Programming Interface (API) documents and their client code \cite{Pandita_inferring_2012} \cite{wei_inferring_2011}.
+API documents are usually well indexed by the functions or the classes that they define.
 When we are interested in a piece of code in the client software,
-we can easily find the related API documents by the name of the functions that the piece of code calls.
-The relationships between the client codes and the API documents can be easily constructed by using the function names as the keywords.
-However, the codes related to hardware and their documents are usually related in different ways.
+we can easily find the related API documents by the names of the functions that the piece of code calls.
+% The relationships between the client codes and the API documents can be easily constructed by using the function names as the keywords.
+However, the code relating to hardware and its documentation usually relate in different ways. % how?
 The hardware documents usually talk about how to use the hardware,
 more specifically how to program the registers inside the hardware modules.
-The hardware documents differ from the API documents in the following ways,
+The hardware documents differ from the API documents in the following ways.
 \begin{itemize}
-\item the hardware documents are usually published as pdf files, while the API documents are usually html files.
-\item the hardware documents are composed of texts, tables and diagrams, while the API documents are usually texts only.
-\item the hardware docuemnts are not orgnized by functions or classes, which are basic elements of codes.
-\item hard for the computer to relate the hardware document pieces to the code pieces automatically.
+\item the hardware documents are usually published as pdf files, while the API documents are usually html files. % matters?
+\item the hardware documents are composed of text, tables and diagrams, while the API documents are usually text only.
+\item the hardware docuemnts are not orgnized by functions or classes, which are the basic elements of code, but instead by hardware modules.
+\item as a consequence of these differences, it is hard for the computer to relate the hardware document pieces to the code pieces automatically.
 \end{itemize}
 
-These differences make the constructing of the relationships between the hardware related codes and their documents really challenging.
-To our knowlege, there is no tools exist to address this problem.
-A simple workaround used is to include the positions of the related document pieces in the documents as comments the codes.
-However, this method can only handle simple situations.
-If there are thousands of these comments cluttered in the codes,
+% These differences make the constructing of the relationships between the hardware related codes and their documents really challenging.
+To our knowlege, there are no tools to address this problem.
+A simple workaround is to include references to positions of the related documentation as comments in the codes.
+However, this can only handle simple situations.
+If there are thousands of such comments cluttered in the code,
 it will be very hard to manage them.
-This paper presents coDoc, a tool to easily create, maintain, and display the relationships.
+This paper presents coDoc, a tool to create, maintain, and display the relationships between code and documentation.
 % The initial version\footnote{\texttt{\url{git@github.com:derekqian/coDoc.git}}} has been released.
-The key features of coDoc are as follows,
+The key features of coDoc are as follows:
 \begin{itemize}
-\item provide the ability to display codes and documents.
-\item provide the ability to develop codes.
-\item select code pieces based on syntax tree of the code.
-\item code selections are stable to the changes of unrelated codes.
-\item create relationships between codes and documents.
-\item manage and display the relationships.
+\item the ability to display both code and documents;
+\item the ability to write and edit code;
+\item code pieces selection based on syntax tree of the code;
+\item stable code selections regarding to the changes of unrelated codes;
+\item creation of relationships between codes and documents;
+\item relationships management and display.
 \end{itemize}
 
-Using coDoc, we have created relationships for two virtual NIC devices in QEMU.
-These two devices are DIO and E100.
+Using coDoc, we have created relationships between two virtual NIC devices in QEMU and the related documents.
+These two devices are DIO \cite{dio} and E100.
 

### 2013-02-22 P4-5-page-paper/paper.tex
backup

@@
 
-The main contributions of this paper are listed as follows,
+The main contributions of this paper are as follows.
 \begin{itemize}
 \item design a framework to display and manage codes, documents and relationships.
-\item remain integrity of the relationships when the codes evolve.
+\item maintain integrity of the relationships when the codes evolve.
 \item present a standard format for the code piece identifier.
@@
 \subsection{C/C++ Development Tool}
-C/C++ Development Tool (CDT) is an Eclipse plugin which supports C/C++ syntax parsing.
-It is written in Java and provides Eclipse with the ability of syntax highlighting and code completing when developing C/C++ codes.
+C/C++ Development Tool (CDT) is an Eclipse plugin that supports C/C++ syntax parsing.
+It is written in Java and provides Eclipse with syntax highlighting and code completion when developing in C or C++.
 
@@
 The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
-It contains CDT editor, poppler, PDF editor and multi-editor.
-There are three kinds of data here, 1) the codes, 2) the documents, 3) the relationships.
-We only handle C/C++ code at this time, 
-as most system code are written in this language.
-CDT editor reads and parses the codes, 
-highlights syntax elements.
-We use poppler to read the PDF file and render the PDF pages to images.
-As poppler is developed in C++, and Eclipse RCP is in Java language,
-we need an adaptor to bridge the C++ code and the Java code.
-We use JNI to implement this adaptor.
-PDF editor implements an adaptor, 
-and uses it to get the PDF page from poppler and displays the page.
-The multi-editor is responsible to read the relationship data,
-and highlight certain code piece and document piece respectively.
+It contains a CDT editor, poppler, a PDF editor and a multi-editor.
+There are three kinds of data here, 1) the code, 2) the documentation, and 3) the relationships.
+We handle only C/C++ code at this time, 
+as most system code is written in C/C++.
+The CDT editor reads and parses the code, 
+and highlights syntax elements.
+We use poppler to read the PDF file and render the PDF pages as images.
+As poppler is developed in C++, and Eclipse Rich Client Program (RCP) is in Java,
+we need an adaptor to bridge between C++ and Java,
+for which we use Java Native Interface (JNI).
+We implement this adaptor in PDF Editor, 
+and uses it to get the PDF page from poppler and display the page.
+The multi-editor is responsible for reading the relationship data,
+and highlighting the code and document pieces that are related.
 To represent a relationship, 
@@
 
-\subsection{Identifying the Code Piece}
-The codes are always evolving during its lifetime.
-We don't want our relationships created for one version stop working for other versions.
-This goal calls for a robust identifying strategy for the code piece.
-Our first method identifies the code piece as the offset of the selected code from the beginning of the code file and the selected length.
+\subsection{Representing Code Segments}
+Code is always evolving during its lifetime.
+We don't want the relationships created for one version to stop working for other versions.
+This goal calls for a robust strategy identifying for the code piece.
+Our first method identifies the code piece as the offset of the selected code from the beginning of the code file and its length.
 This method is straight forward and is easy to understand and implement.
-However, this method definitely will violate the robust requirement.
-To achieve the goal, we need to find some properties of the code that are relatively stable when code evolves.
-These properties should also can serve as a key to uniquely identify the code piece.
+However, this method definitely does not satisfy the robustness requirement.
+To achieve robustness, we need to find some properties of the code that are relatively stable when code evolves.
+That can serve as a key to identify the code piece.
 The intuitive thought is to use the semantic information,
-as it describes the intrinsical meaning of the code.
-However, there is no formal method to describe this information.
-We use syntax information to form the main element of our identifier.
+that is the intrinsic meaning of the code.
+However, we can't find a formal way of defining this information.
+We use syntax information to form the main element of our code references.
 The code can be parsed and represented by a syntax tree.
-The change of the code in one branch will usually not affect the code in the other branches.
-If we can identify the code piece based on the position in the syntax tree,
-we can design a robust method to identify the code piece.
-To make the method more robust,
+A change of the code in one branch will usually not affect the code in other branches.
+Representing code segments based on the position in the syntax tree should be robust.
+To make the method more robust, % prof lost here
 we can introduce the information in the first method as the secondary key.
@@
 we can use the offset information to assist the decision.
-We also include in the identifier the content of the code piece for the integrity check.
-The structure used to achieve this goal is shown bellow,
+We also include in the identifier the content of the code piece as an integrity check.
+The structure used to achieve this goal is shown bellow.
 \begin{Verbatim}[frame=single]

### 2013-02-22 P4-5-page-paper/paper.tex
backup

@@
 We can implement the code viewer and the PDF viewer in seperate process,
-and use inner process communication (IPC) techniques to synchronize.
+and use inter process communication (IPC) techniques to communicate.
 The advantage of this method is that each process has its own window,
-can ocuppy the whole screen,
+can occupy the whole screen,
 and display more content which reduces the need to scroll the window horizontally.
 When the user uses a computer with two monitors,
-the tool implementing this method is extremely a good choice,
-as the user can choose to display the code and the document in seperate moniter.
-However, this implementation is heavy,
-and get performance issues.
+the tool implementing this method is an extremely good choice,
+as the user can choose to display the code and the document on seperate moniters.
+However, this implementation is heavy, % ?
+and has performance issues.
 When using the tool, 
@@
 which is slow.
-Our earlier implementation use this method,
-and encountered a lot of synchronization problems oriatated from the IPC communication.
-In coDoc, we choose to implement the code viewer and the code viewer in the same process.
-This way, all the commucations are done in the same process.
+Our earlest implementation uses this method,
+and encountered synchronization problems from the IPC communication.
+In coDoc, we choose to implement the code viewer and the PDF viewer in the same process.
 %The Eclipse framework even makes the whole system single thread.
-No IPC communication is needed,
-which is more efficient and makes the tool more user-friendly.
-With the new method, we can smoothly operate the tool without any uncomfortable feeling.
-The advantage of the first method become the disadvantage of the new method,
-as the code viwer and the document viwer should share the whole screen now.
-However, with a efficient and user-friendly screen split strategy and screen area assignment method,
+This way, all the commucation is internal to the same process,
+%No IPC communication is needed,
+which is more efficient and makes the tool more responsive.
+%With the new method, we can smoothly operate the tool without any uncomfortable feeling.
+The advantages of the first method become the disadvantage of the new method,
+as the code viwer and the document viwer must share the whole screen now.
+However, with a efficient and user-friendly method of assigning screen area,
 we can make the user feel less uncomfortable when viewing the content.
-Also, most programmer now not only are using two moniters, 
+Also, most programmer now not only are using two moniters, % prove
 but also the moniters they are using are larger and larger.
-Using a larger moniter with high definition will make this disadvantage nothing.
+Using a larger moniter with high definition will make this disadvantage nothing. % need revisement
 And even better, in this situation, this method will overcome the first method,
@@
 \subsection{Relationship Store Model}
-In coDoc, we store the relationship data in XML file, 
-instead of the SQL database.
-The reason that we didn't use a SQL database is that the relationships is semi-structured,
+In coDoc, we store the relationship data in an XML file, 
+rather than a SQL database.
+The reason that we didn't use an SQL database is that the relationships are semi-structured,
 as we decide to store the content along with the identifier.
 The content is used to further check the integrity.
-XML database is very suitable for our semi-structured data here.
+XML database is very suitable for our semi-structured data. % why
 
@@
 \label{sec:evaluation}
-\textbf{Effectiveness.} We have evaluated coDoc by mapping two virtual devices and their related documents.
+\textbf{Effectiveness.} We evaluated coDoc by setting up relationships between the code for two virtual devices and their related documents.
 The number of relationships created and the time used to created these relationships are listed in Table \ref{table:evaluate}.

### 2013-03-14 P5-5-page-paper/paper.tex
project 5, revised version for project 4

% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

\usepackage{textcomp}
\usepackage{fancyvrb}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{url}

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
%\acmVolume{9}
%\acmNumber{4}
%\acmArticle{39}
%\acmYear{2013}
%\acmMonth{3}

\renewcommand{\baselinestretch}{2}

% Document starts
\begin{document}

% Page heads
%\markboth{D. Qian et al.}{coDoc: A Tool for Managing Relationships between Code and Documentation}

% Title portion
\title{coDoc: A Tool for Managing Relationships between Code and Documentation}
\author{DEJUN QIAN
\affil{Portland State University}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
The reusing of either software or hardware components is an important way to build large systems.
Documentation plays a critical role in the process of reusing,
as it describes how the components can be reused.
When writing and testing software, 
we need the documentation in hand.
This is particularly true for software that is documentation-intensive, 
such as device drivers and virtual device modules.
This paper presents coDoc, 
an integrated development environment for managing relationships between code and documentation.
We describe the architecture and features of coDoc,
and discuss several design decisions that we faced in developing coDoc and the trade-offs involved in making these decisions.
We report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents by coDoc.
\end{abstract}

%\category{C.2.2}{Software Engineering}{Tools}

%\terms{Design, Algorithms, Performance}

%\keywords{Wireless sensor networks, media access control, multi-channel, radio interference, time synchronization}

%\acmformat{Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic,
%and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially
%designed for  wireless sensor network applications.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

%\begin{bottomstuff}
%This work is supported by the National Science Foundation, under
%grant CNS-0435060, grant CCR-0325197 and grant EN-CS-0329609.
%
%Author's addresses: G. Zhou, Computer Science Department,
%College of William and Mary; Y. Wu  {and} J. A. Stankovic,
%Computer Science Department, University of Virginia; T. Yan,
%Eaton Innovation Center; T. He, Computer Science Department,
%University of Minnesota; C. Huang, Google; T. F. Abdelzaher,
%(Current address) NASA Ames Research Center, Moffett Field, California 94035.
%\end{bottomstuff}

\maketitle

\section{Introduction}
\label{sec:introduction}
Documentation plays an important role in software engineering.
%from requirement analysis to architecture design,
%from coding to software testing,
%from software debugging to software maintenance.
Software that relates closely to hardware is extremely documentation intensive. % explain why
Examples of such software include bootloaders, 
Hardware Abstraction Layers (HAL) in Operating Systems (OS),
and virtual device modules for virtual machines.
Such software must follow the hardware documentation to operate correctly.
A typical embedded CPU might have documentation consisting of thousands of pages.
A computer system usually consists of more than ten hardware modules.
Effectively maintaining the relationships between the code and the documentation is important for developing and verifying hardware-related software.

To our knowledge, there are no tools to address this problem.
Researchers have done a lot of work to handle the relationships between Application Programming Interface (API) documents and their client code \cite{Pandita_inferring_2012} \cite{wei_inferring_2011}.
However, the approaches developed in the work do not consider the relationships between hardware-related code and its documentation.
API documents are usually well indexed by the functions or the classes that they define.
When we are interested in a piece of code in the client software
we can easily find the related API documents by the names of the functions that the piece of code calls.
% The relationships between the client codes and the API documents can be easily constructed by using the function names as the keywords.
However, the code relating to hardware and its documentation usually relate in different ways.
% the hardware docuemnts are not orgnized by functions or classes, which are the basic elements of code, but instead by hardware modules.
People usually organize hardware documentation by hardware modules and the registers inside the hardware modules.
These modules and registers do not relate to the code in an explicit way.
Hardware documents include text, tables and diagrams, while API documents usually include text only.

% These differences make the constructing of the relationships between the hardware related codes and their documents really challenging.
A simple workaround is to include references to the positions of the related documentation as comments in the code.
However, this can only handle simple situations.
If there are thousands of such comments cluttered in the code,
it will be very hard to manage them.

This paper presents coDoc, a tool to create, maintain, and display relationships between code and documentation.
% The initial version\footnote{\texttt{\url{git@github.com:derekqian/coDoc.git}}} has been released.
The key features of coDoc include 
the ability to display both code and documents, 
the ability to write and edit code, 
code-piece selection based on syntax tree of the code,
%stable code selections regarding to the changes of unrelated codes;
creation of relationships between codes and documents,
and relationships management and display.
Using coDoc, we have created relationships between two virtual NIC devices in QEMU and the related documents.
These two devices are DIO \cite{dio} and E100 \cite{e100}.

The main contributions of this paper are as follows.
\begin{itemize}
\item Design a framework to display and manage codes, documents and relationships.
\item Design coDoc which implement the framework.
\item Maintain integrity of the relationships when the code evolves.
\item Design a standard format to represent the code piece.
\item Design a standard format to represent the document piece.
\item Design a data model for relationships between code and documentation.
\end{itemize}

The rest of the paper is organized as follows. 
Section \ref{sec:arch} provides the overall architecture and key features of coDoc.
%Section \ref{sec:decision} gives the design decisions of coDoc and the trade-offs of these decisions.
Section \ref{sec:evaluation} summarizes our experiences of creating and maitaining the relationships for two virtual devices.
Section \ref{sec:related} presents the related work.
Section \ref{sec:conclusion} concludes our work and gives our future research plan.

\section{Architecture and Features of coDoc}
\label{sec:arch}

\begin{figure}
\begin{center}
\includegraphics[width=0.55\textwidth]{architecture}
\caption{coDoc Architecture and Features}
\label{fig:architecture}
\end{center}
\end{figure}

\subsection{Architecture of coDoc}
The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
It contains a code manager (CM), a documentation manager (DM) and a relationship manager (RM).
There are three types of data here, 1) code, 2) documentation, and 3) relationships.
We handle only C/C++ code at this time, 
as most system code is written in C/C++.
CM reuses C/C++ Development Tool (CDT) editor from Elipse\footnote{\texttt{\url{http://www.eclipse.org}}} to handle C/C++ code.
The CDT editor reads and parses the code, 
and highlights syntax elements.
We use poppler to read the PDF file and render the PDF pages as images.
As poppler is developed in C++ and Eclipse Rich Client Program (RCP) is in Java,
we need an adaptor to bridge between C++ and Java,
for which we use Java Native Interface (JNI).
We implement this adaptor in PDF Editor, 
and uses it to get the PDF page from poppler and display the page.
RM reads the relationship data,
and highlights the code and document pieces that are related.

\begin{figure}
\begin{center}
\includegraphics[width=0.85\textwidth]{datamodel}
\caption{Data Model for coDoc}
\label{fig:datamodel}
\end{center}
\end{figure}

\subsection{Data Model}
The data model is shown in Figure \ref{fig:datamodel}.
We have four entities here: category, relationship, code piece and documentation piece.
Code piece and documentation piece represent the selected code and documentation respectively.
We represent the relationships between code and documentation as entities,
as we want to classify the relationships.
The relationships are classified by their functionality in our approach.
Category is used to maintain the classification information of the relationships.
To represent a relationship, 
we need to define the strategy to represent the code piece and documentation piece.

\begin{figure}
\begin{center}
\includegraphics[width=0.85\textwidth]{ast1}
\caption{Original code and its AST}
\label{fig:ast1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.85\textwidth]{ast2}
\caption{Evolved code and its AST}
\label{fig:ast2}
\end{center}
\end{figure}

\subsection{Representing Code Segments}
Code is always evolving during its lifetime.
We want the relationships created for one version of code keep working for other versions.
To achieve this goal, we need a robust strategy to represent the code pieces.
Our first method represents the code piece by the offset of the selected code from the beginning of the code file and the length of the selected code.
This method is straight forward and is easy to understand and implement.
However, this method is not robust,
as the change of the code file will change the offset of the selected code.
The left sides of Figure \ref{fig:ast1} and Figure \ref{fig:ast2} give the code before and after it evloves.
The highlighted code piece is what we want to select.
Unfortunitely, the offset of the select code increases after we add some code,
as shown in this example.
To achieve robustness, we need to find some properties of the code that are relatively stable when code evolves.
These properties can serve as keys to represent the code piece.
An intuitive thought is to use the semantic information,
that is the intrinsic meaning of the code.
However, we can't find a formal way of defining this information.
We use syntax information to form the main element of our code piece identifier.
The code can be parsed and represented by a syntax tree.
A change of the code in one branch will usually not affect the code in other branches.
Representing code segments based on the position in the syntax tree should be robust.
The right sides of Figure \ref{fig:ast1} and Figure \ref{fig:ast2} are the Abstract Syntax Trees (AST) for the code before and after it evolves.
In the ASTs, the highlighted nodes relate to the code piece we selected.
Through the two ASTs are different, 
the highlighted nodes can be represented by the same path from the roots of these two ASTs.
%To make the method more robust, % prof lost here
%we can introduce the information in the first method as the secondary key.
%When the syntax identifier fails to locate the code piece,
%we can use the offset information to assist the decision.
%We also include in the identifier the content of the code piece as an integrity check.
%The structure used to achieve this goal is shown bellow.
%\begin{Verbatim}[frame=single]
%class CodeSelection {
%  private String syntaxcodepath;
%  private String selcodepath;
%  private String syntaxcodetext;
%  private String selcodetext;
%}
%\end{Verbatim}

%\section{Methodology and Design Decisions}
%\label{sec:decision}
%\subsection{Embedded vs Seperate for PDF Reader}
%The tool should display both codes and documents at the same time.
%We can implement the code viewer and the PDF viewer in seperate process,
%and use inter process communication (IPC) techniques to communicate.
%The advantage of this method is that each process has its own window,
%can occupy the whole screen,
%and display more content which reduces the need to scroll the window horizontally.
%When the user uses a computer with two monitors,
%the tool implementing this method is an extremely good choice,
%as the user can choose to display the code and the document on seperate moniters.
%However, this implementation is heavy, % ?
%and has performance issues.
%When using the tool, 
%the user may need to launch the PDF reader,
%which is slow.
%Our earlest implementation uses this method,
%and encountered synchronization problems from the IPC communication.
%In coDoc, we choose to implement the code viewer and the PDF viewer in the same process.
%%The Eclipse framework even makes the whole system single thread.
%This way, all the commucation is internal to the same process,
%No IPC communication is needed,
%which is more efficient and makes the tool more responsive.
%With the new method, we can smoothly operate the tool without any uncomfortable feeling.
%The advantages of the first method become the disadvantage of the new method,
%as the code viwer and the document viwer must share the whole screen now.
%However, with a efficient and user-friendly method of assigning screen area,
%we can make the user feel less uncomfortable when viewing the content.
%Also, most programmer now not only are using two moniters, % prove
%but also the moniters they are using are larger and larger.
%Using a larger moniter with high definition will make this disadvantage nothing. % need revisement
%And even better, in this situation, this method will overcome the first method,
%as moving the eyes between two big moniter is energy consuming.

\section{Evaluation}
\label{sec:evaluation}
%We adopt poppler, a open-source PDF render, to render PDF content in coDoc.
%This PDF render is written in C++, 
%and is widely used in Linux systems.
%It uses Cairo and GTK to draw the rendered content.

\textbf{Effectiveness.} We evaluated coDoc by setting up relationships between the code for two virtual devices and their documentation.
The number of relationships created and the time used to created these relationships are listed in Table I.% \ref{table:evaluate}.

\begin{table}[th]
\tbl{Evaluate Result}{
\label{tab:evaluate}
\begin{tabular}{rcc}
\hline
Code & \# of Relationships & time(hr) \\
\hline
dio & 108 & 2 \\
e100  & 213 & 4
%\hline
\end{tabular}}
\end{table}

The identifying method with fine granularity makes the relationship created by coDoc very accurate, 
80\% of the code pieces are marked inside the statement.
This result is hard for comment-based method to achieve.
The same result happens for the document.
In the whole relationships, 
90\% of the document pieces are marked on cells in the tables.
The comments in the PDF file will be too crowd to be useful,
as it will affect the normal reading of the document.
Our approach can also make the development efficient,
as we don't need the developer to change either the code or the document while only relationship is created.
This makes the code and document neat and easily to read and understand.

\noindent \textbf{Usability.} We implemented coDoc as an Elipse Rich Client Program (RCP), 
which can make our tool share the appearence in Eclipse that is familiar by many programmer.
Figure \ref{fig:platformview} is the screenshot of the tool.
Three persons with no prior exprience with coDoc have successfully use this tool to create the relationships between their codes and documentation.
They didn't find any difficulties when using this tool.
All the feedbacks has been positive regarding the use of the tool.
%Now they can easily create their relationships by selecting the code and document piece using mouse, input the comment using keyboard.
%They can also manage the relationships by sorting by attributes, search certain relationships by keywords.
%They also find the feature that allow them to categorize the relationships helpful.
%This feature makes the relationships neater when the number of relationships is large.

In our own experience, we found that the ability to see the code, 
the documentation and the relationships on the same screen saves a lot of time,
as we don't need to switch between different tools.
%The visualized interface also saved us time to learn the detailed syntax about the identifier formats,
%and to write the identifier manually.
We believe this tool will lead to increased productivity.

% convert platformview.png platformview.eps
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{platformview}
\caption{coDoc Platform View}
\label{fig:platformview}
\end{center}
\end{figure}

\section{Related Work}
\label{sec:related}
Current tools can manage codes. 
These kinds of tools include revision control software like git, svn \cite{git} \cite{svn}. 
Revision control tools can give the evolving history of the software.
These tools usually adopt text comparison tools to figure out the differences between different versions of the software.
The comparation tools can easily give the result about the matching points and mismatching points in the codes,
which means they can manage the relationships between different versions of codes.
However, these tools are not designed to manage documents.
Though some people also use them to manage documents,
they only use it as a persistent data warehouse.
They can not take the advantages of the comparison tools, 
as these tool usually can only deal with text file.
People are using code comments to record the related document piece.
However, no consistent format exists,
which makes these information not managable,
especially when these comments are made by many different developers.

Full text indexing system is developed to processing documents \cite{lucene}.
However, they can only relate keywords to certain documents.
They do not deal with both codes and documents. 
Like full text indexing system,
search engines also work with documents in similar way.
Most of the documents that are handled by search engines are web pages.
Many PDF readers can support highlighting and commenting.
With these features, we can relate a document piece to a code piece.
However, these links created are not stable,
and PDF readers can not check the integrity of these information.

Generally speaking, these are tools can either do code management or do document management.
However, they are not designed to do both,
and managing the relationships between codes and documents is definitely a mission impossible task for them.

% Based on what you have so far, what can you conclude?  What cool ideas did you think up but not have time to implement so far?
\section{Conclusions and Future Work}
\label{sec:conclusion}
We have implemented coDoc, 
a tool for managing the relationships between the hardware related programs and their documentation.
The main contribution of this paper is the method to identify the code segment.
Our experiences of using coDoc to manage the code for two virtual devices and their documentation shows the tool is robust and efficent,
and is helpful when developing and maitaining the virtual devices.
The relationships remain stable even when the code changes.

There are still opportunities to improve coDoc.
\begin{enumerate}
\item Combine it with revision control tools to provide a more user-friendly tool suit for developing and maitaining the codes while managing the documents at the same time.
\item Design more robust method to identify the document pieces in the PDF documents to make the tool invariant to the change of the documents.
\item Use machine learning (use the data created as seed to train the model) to construct and check the relationships between hardware related codes and their documents.
\end{enumerate}

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{reference}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

\end{document}
% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2013-03-14 RPE/paper.tex
RPE paper, revised from project 5

--- 2013-03-14 P5-5-page-paper/paper.tex
@@
-% v2-acmsmall-sample.tex, dated March 6 2012
-% This is a sample file for ACM small trim journals
-%
-% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
-% (c) 2010 Association for Computing Machinery (ACM)
-%
-% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
-% Users can also go through the FAQs available on the journal's submission webpage.
-%
-% Steps to compile: latex, bibtex, latex latex
-%
-% For tracking purposes => this is v1.3 - March 2012
+\documentclass[runningheads,a4paper]{llncs}
 
-\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax
+\usepackage{amssymb}
+\setcounter{tocdepth}{3}
+\usepackage{graphicx}
 
-\usepackage{textcomp}
-\usepackage{fancyvrb}
-\usepackage{colortbl}
-\usepackage{graphicx}
 \usepackage{url}
+\urldef{\mailsa}\path|dejun@cs.pdx.edu|
+\newcommand{\keywords}[1]{\par\addvspace\baselineskip
+\noindent\keywordname\enspace\ignorespaces#1}
 
-% Package to generate and customize Algorithm as per ACM style
-\usepackage[ruled]{algorithm2e}
-\renewcommand{\algorithmcfname}{ALGORITHM}
-\SetAlFnt{\small}
-\SetAlCapFnt{\small}
-\SetAlCapNameFnt{\small}
-\SetAlCapHSkip{0pt}
-\IncMargin{-\parindent}
-
-% Metadata Information
-%\acmVolume{9}
-%\acmNumber{4}
-%\acmArticle{39}
-%\acmYear{2013}
-%\acmMonth{3}
-
-\renewcommand{\baselinestretch}{2}
-
-% Document starts
 \begin{document}
 
-% Page heads
-%\markboth{D. Qian et al.}{coDoc: A Tool for Managing Relationships between Code and Documentation}
+\mainmatter  % start of an individual contribution
 
-% Title portion
+% first the title is needed
 \title{coDoc: A Tool for Managing Relationships between Code and Documentation}
-\author{DEJUN QIAN
-\affil{Portland State University}
-}
-% NOTE! Affiliations placed here should be for the institution where the
-%       BULK of the research was done. If the author has gone to a new
-%       institution, before publication, the (above) affiliation should NOT be changed.
-%       The authors 'current' address may be given in the "Author's addresses:" block (below).
-%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
-%       currently affiliated with NASA.
+
+% a short form should be given in case it is too long for the running head
+\titlerunning{coDoc: Managing Relationships between Code and Documentation}
+
+% the name(s) of the author(s) follow(s) next
+%
+% NB: Chinese authors should write their first names(s) in front of
+% their surnames. This ensures that the names appear correctly in
+% the running heads and the author index.
+%
+\author{Dejun Qian}
+%
+\authorrunning{coDoc: Managing Relationships between Code and Documentation}
+% (feature abused for this document to repeat the title also on left hand pages)
+
+% the affiliations are given next; don't give your e-mail address
+% unless you accept that it will be published
+\institute{Computer Science Department,\\
+Portland State University,\\
+1900 SW 4th Avenue Portland, OR 97201, USA\\
+\mailsa\\
+\url{http://www.pdx.edu/computer-science/}}
+
+%
+% NB: a more complex sample for affiliations and the mapping to the
+% corresponding authors can be found in the file "llncs.dem"
+% (search for the string "\mainmatter" where a contribution starts).
+% "llncs.dem" accompanies the document class "llncs.cls".
+%
+
+\toctitle{Lecture Notes in Computer Science}
+\tocauthor{Authors' Instructions}
+\maketitle
 
@@
 We report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents by coDoc.
+\keywords{Software Engineering, Data Model}
 \end{abstract}
-
-%\category{C.2.2}{Software Engineering}{Tools}
-
-%\terms{Design, Algorithms, Performance}
-
-%\keywords{Wireless sensor networks, media access control, multi-channel, radio interference, time synchronization}
-
-%\acmformat{Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic,
-%and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially
-%designed for  wireless sensor network applications.}
-% At a minimum you need to supply the author names, year and a title.
-% IMPORTANT:
-% Full first names whenever they are known, surname last, followed by a period.
-% In the case of two authors, 'and' is placed between them.
-% In the case of three or more authors, the serial comma is used, that is, all author names
-% except the last one but including the penultimate author's name are followed by a comma,
-% and then 'and' is placed before the final author's name.
-% If only first and middle initials are known, then each initial
-% is followed by a period and they are separated by a space.
-% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.
-
-%\begin{bottomstuff}
-%This work is supported by the National Science Foundation, under
-%grant CNS-0435060, grant CCR-0325197 and grant EN-CS-0329609.
-%
-%Author's addresses: G. Zhou, Computer Science Department,
-%College of William and Mary; Y. Wu  {and} J. A. Stankovic,
-%Computer Science Department, University of Virginia; T. Yan,
-%Eaton Innovation Center; T. He, Computer Science Department,
-%University of Minnesota; C. Huang, Google; T. F. Abdelzaher,
-%(Current address) NASA Ames Research Center, Moffett Field, California 94035.
-%\end{bottomstuff}
-
-\maketitle
 
@@
 \textbf{Effectiveness.} We evaluated coDoc by setting up relationships between the code for two virtual devices and their documentation.
-The number of relationships created and the time used to created these relationships are listed in Table I.% \ref{table:evaluate}.
+The number of relationships created and the time used to created these relationships are listed in Table \ref{table:evaluate}.
 
 \begin{table}[th]
-\tbl{Evaluate Result}{
-\label{tab:evaluate}
+\caption{Evaluate Result}
+\centering
 \begin{tabular}{rcc}
@@
 dio & 108 & 2 \\
-e100  & 213 & 4
-%\hline
-\end{tabular}}
+e100  & 213 & 4\\
+\hline
+\end{tabular}
+\label{table:evaluate}
 \end{table}
@@
 % Bibliography
-\bibliographystyle{ACM-Reference-Format-Journals}
+\bibliographystyle{splncs03}
 \bibliography{reference}
-                             % Sample .bib file with references that match those in
-                             % the 'Specifications Document (V1.5)' as well containing
-                             % 'legacy' bibs and bibs with 'alternate codings'.
-                             % Gerry Murray - March 2012
 
 \end{document}
-% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2013-03-21 P6-15-min-talk/talk.tex
15 min talk with latex

\documentclass[]{beamer}
% Class options include: notes, notesonly, handout, trans,
%                        hidesubsections, shadesubsections,
%                        inrow, blue, red, grey, brown

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}

\usetheme{Madrid}
\usecolortheme{dolphin}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
\useoutertheme{infolines}
\useinnertheme{rectangles}
%\useoutertheme[footline=authortitle]{miniframes}

\setbeamercolor{block title}{bg=blue}
%\setbeamerfont*{title}{size=\huge}

% Theme for beamer presentation.
%\usepackage{beamerthemesplit} 
%\usepackage{beamerthemelined} 
% Other themes include: beamerthemebars, beamerthemelined, 
%                       beamerthemetree, beamerthemetreebars

\beamertemplatenavigationsymbolsempty

\makeatletter
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
    \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
    \insertframenumber{} / \inserttotalframenumber\hspace*{2ex} 
  \end{beamercolorbox}}%
  \vskip0pt%
}
\makeatother

%\setbeamercolor*{title}{bg=gray,fg=blue}
\title{Managing Relationships\\between Code and Documentation}    % Enter your title between curly braces
\author{Dejun Qian}                 % Enter your name between curly braces
\institute{Portland State University}      % Enter your institute name between curly braces
%\date{\today}                    % Enter the date or \today between curly braces
\date{}                    % Enter the date or \today between curly braces

\begin{document}

% Creates title page of slide show using above information
\begin{frame}
  \titlepage
\end{frame}
\note{Good afternoon, everyone. My name is Dejun Qian. Today I will talk about how to manage relationships between code and documentation.}

%\section[Outline]{}

% Creates table of contents slide incorporating
% all \section and \subsection commands
%\begin{frame}
%  \frametitle{Agenda}
%  \tableofcontents
%\end{frame}

\section{Background}
\subsection{Code vs Documentation}
\begin{frame}{\centerline{Background}}
  \includegraphics[width=\textwidth]{problem1}
\end{frame}
\note{To write and maintain code efficiently, we need documentation. Usually, code is composed of several code files, and each code file contains a string of ASCII charactors. Basically the string conforms to the syntax of certain languages like C, Java, and etc.. Compared to code, documentation is much more complicated. It may be in different file formats, like pdf, html, MS word, and etc.. Instead of raw ASCII string, the content in documentation could be text, table, picture, and etc..}

\subsection{Relationships}
\begin{frame}{\centerline{Background}}
  \includegraphics[width=\textwidth]{problem2}
\end{frame}
\note{Usually, just knowing which documentation file is needed for which code file does not help too much. We need more detailed information. As we read code word by word, and line by line, we need to know which code segment is related to which document segment.}

\section{Problem Statement}
\subsection{Problems}
\begin{frame}[b]{\centerline{Problem}}
  \ \\
  \fontsize{13.5}{11}\selectfont How to represent the code segments with
  \begin{itemize}
  \item code-evolving invariance,
  \item good granularity,
  \item and non-ambiguity? %\normalsize
  \end{itemize}
  \begin{center}
  \includegraphics[width=.9\textwidth]{problem3}
  \end{center}
\end{frame}
%\note[enumerate]       % Add notes to yourself that will be displayed when
%{                      % typeset with the notes or notesonly class options
%\item Note for Point 1   
%\item Note for Point 2   
%}

\section{Previous Solution}
\subsection{Previous Solutions}
\begin{frame}{\centerline{Previous Solutions}}
  \ \\
  \fontsize{13.5}{11}\selectfont Previous work addresses this problem by
  \begin{itemize}
  \item comment-based representation
  \item and offset-based representation.
  \end{itemize}
\end{frame}

\subsection{Comment-Representation}
\begin{frame}
  \frametitle{\centerline{Comment-Based Representation (CBR)}}
  \fontsize{13.5}{11}\selectfont
  \begin{columns}[c]
  \column{2.5in}  % slides are 3in high by 5in wide
  advantage: 
  \begin{itemize}
  \item code-evolving invariance
  \end{itemize}
  \vspace{2em}
  disadvantage: 
  \begin{itemize}
  \item bad granularity
  \item ambiguity
  \end{itemize}
  \column{1.5in}
  \includegraphics[height=.9\textheight]{comment}
  \end{columns}
\end{frame}

\subsection{Offset-Representation}
\begin{frame}
  \frametitle{\centerline{Offset-Based Representation (OBR)}}
  \fontsize{13.5}{11}\selectfont
  \begin{columns}[c]
  \column{2in}  % slides are 3in high by 5in wide
  advantage: 
  \begin{itemize}
  \item good granularity
  \item no ambiguity
  \end{itemize}
  \vspace{2em}
  disadvantage: 
  \begin{itemize}
  \item stop working when code evolves
  \end{itemize}
  \column{2in}
  \includegraphics[height=.9\textheight]{offset}
  \end{columns}
\end{frame}

\section{Solution}
\subsection{Abstract Syntax Tree}
\begin{frame}
  \frametitle{\centerline{Abstract Syntax Tree}}
  \begin{columns}[c]
  \column{1.8in}  % slides are 3in high by 5in wide
  \includegraphics[width=.9\textwidth]{code1}
  \column{2.5in}
  \includegraphics[height=.75\textheight]{ast1}
  \end{columns}
\end{frame}
\note{The end}

\subsection{Code-evolving Invariance}
\begin{frame}
  \frametitle{\centerline{AST-Based Representation (ABR)}}
  \begin{columns}[c]
  \column{1.8in}  % slides are 3in high by 5in wide
  \includegraphics[width=.9\textwidth]{code11}
  \column{2.5in}
  \includegraphics[height=.75\textheight]{ast11}
  \end{columns}
\end{frame}

%\subsection{Code-evolving Invariance}
%\begin{frame}[b]
%  \frametitle{\centerline{Code-evolving Invariance}}
  %\begin{center}
%  \begin{tikzpicture}
%    \node (img1) {\includegraphics[height=.75\textheight]{code21}};
    %\pause
%    \node (img2) at (img1.east)[xshift=.1\textheight] {\includegraphics[width=.95\textwidth]{ast21}};
%  \end{tikzpicture}
  %\end{center}
  %\includegraphics[width=.9\textwidth]{code21}
  %\includegraphics[height=.75\textheight]{ast21}
%\end{frame}

\subsection{Code-evolving Invariance}
\begin{frame}
  \frametitle{\centerline{Code-evolving Invariance}}
  \begin{columns}[c]
  \column{1.8in}  % slides are 3in high by 5in wide
  \includegraphics[width=.9\textwidth]{code21}
  \column{2.5in}
  \includegraphics[height=.75\textheight]{ast22}
  \end{columns}
\end{frame}

\subsection{Granularity}
\begin{frame}
  \frametitle{\centerline{Granularity and Non-ambiguity}}
  \begin{columns}[c]
  \column{1.8in}  % slides are 3in high by 5in wide
  \includegraphics[width=.9\textwidth]{code23}
  \column{2.5in}
  \includegraphics[height=.75\textheight]{ast23}
  \end{columns}
\end{frame}
\note{The end}

\section{Preliminary Result}
\subsection{Preliminary Result}
\begin{frame}{\centerline{Preliminary Result}}
  \ \\
  \begin{center}
  \includegraphics[width=\textwidth]{platformview}
  \end{center}
\end{frame}

\subsection{Preliminary Result}
\begin{frame}[b]{\centerline{Preliminary Result}}
  \fontsize{13.5}{11}\selectfont
  \begin{itemize}
  \item preserve all the relationships for this test case
  \item provide good granularity
  \end{itemize}
  \centerline{\includegraphics[width=.9\textwidth]{platformview}}
\end{frame}

\section{Conclusion}
\begin{frame}[t]{\centerline{Conclusion}}
  \ \\
  \fontsize{13.5}{11}\selectfont
  \centerline{
  \begin{tabular}{*{4}{c}}
    \toprule
    Strategy & Invariance & Granularity & Non-Ambiguity \\
    \midrule
    CBR   & Yes & No  & No \\
    OBR   & No  & Yes & Yes \\
    ABR   & Yes & Yes & Yes \\
    \bottomrule
  \end{tabular}
  }
\end{frame}

\section{Question}
\begin{frame}[t]{\centerline{Conclusion}}
  \ \\
  \fontsize{13.5}{11}\selectfont
  \centerline{
  \begin{tabular}{*{4}{c}}
    \toprule
    Strategy & Invariance & Granularity & Non-Ambiguity \\
    \midrule
    CBR   & Yes & No  & No \\
    OBR   & No  & Yes & Yes \\
    ABR   & Yes & Yes & Yes \\
    \bottomrule
  \end{tabular}
  }
  \begin{center}
  \begin{Huge}
  \ \\
  \ \\
  Question?
  \end{Huge}
  \end{center}
\end{frame}

\end{document}

### 2013-03-21 P6-15-min-talk/talk.tex
submited version

@@
   \item code-evolving invariance,
-  \item good granularity,
+  \item flexible granularity,
   \item and non-ambiguity? %\normalsize
@@
 \subsection{Previous Solutions}
-\begin{frame}{\centerline{Previous Solutions}}
+\begin{frame}{\centerline{Previous Work}}
   \ \\
-  \fontsize{13.5}{11}\selectfont Previous work addresses this problem by
+  \fontsize{13.5}{11}\selectfont
   \begin{itemize}
-  \item comment-based representation
-  \item and offset-based representation.
+  \item Comment-based representation
+    \begin{itemize}
+      \item Javadoc uses this to write documentation for code segments.
+    \end{itemize}
+  \ \\
+  \ \\
+  \item Offset-based representation
+    \begin{itemize}
+      \item Compiler uses this method to highlight error code.
+    \end{itemize}
   \end{itemize}
@@
 \begin{frame}
-  \frametitle{\centerline{Comment-Based Representation (CBR)}}
+  \frametitle{\centerline{Comment-Based Representation}}
   \fontsize{13.5}{11}\selectfont
@@
   \column{2.5in}  % slides are 3in high by 5in wide
-  advantage: 
+  Advantage
   \begin{itemize}
-  \item code-evolving invariance
+  \item Code-evolving invariance
   \end{itemize}
   \vspace{2em}
-  disadvantage: 
+  Disadvantage
   \begin{itemize}
-  \item bad granularity
-  \item ambiguity
+  \item Coarse granularity
+  \item Ambiguity
   \end{itemize}
@@
 \begin{frame}
-  \frametitle{\centerline{Offset-Based Representation (OBR)}}
+  \frametitle{\centerline{Offset-Based Representation}}
   \fontsize{13.5}{11}\selectfont
@@
   \column{2in}  % slides are 3in high by 5in wide
-  advantage: 
+  Advantage
   \begin{itemize}
-  \item good granularity
-  \item no ambiguity
+  \item Flexible granularity
+  \item No ambiguity
   \end{itemize}
   \vspace{2em}
-  disadvantage: 
+  Disadvantage
   \begin{itemize}
-  \item stop working when code evolves
+  \item No code-evolving invariance
   \end{itemize}
@@
 \begin{frame}
-  \frametitle{\centerline{AST-Based Representation (ABR)}}
+  \frametitle{\centerline{AST-Based Representation}}
   \begin{columns}[c]
@@
 \begin{frame}{\centerline{Preliminary Result}}
-  \ \\
   \begin{center}
-  \includegraphics[width=\textwidth]{platformview}
+  \includegraphics[width=.9\textwidth]{platformview}
   \end{center}
@@
   \begin{itemize}
-  \item preserve all the relationships for this test case
-  \item provide good granularity
+  \item Preserve all the relationships after code evolves.
+  \item Provide flexible granularity and non-ambiguity.
   \end{itemize}
-  \centerline{\includegraphics[width=.9\textwidth]{platformview}}
+  \centerline{\includegraphics[width=.7\textwidth]{platformview}}
 \end{frame}
@@
   \ \\
-  \fontsize{13.5}{11}\selectfont
+  \fontsize{10}{11}\selectfont
   \centerline{
-  \begin{tabular}{*{4}{c}}
+  \begin{tabular}{rccc}
     \toprule
-    Strategy & Invariance & Granularity & Non-Ambiguity \\
+    Representation & Code-evolving invariance & Flexible granularity & Non-ambiguity \\
     \midrule
-    CBR   & Yes & No  & No \\
-    OBR   & No  & Yes & Yes \\
-    ABR   & Yes & Yes & Yes \\
+    Comment based   & Yes & No  & No \\
+    Offset based   & No  & Yes & Yes \\
+    AST based   & Yes & Yes & Yes \\
     \bottomrule

### 2013-04-03 QSIC2013/paper.tex
QSIC2013

--- 2013-03-14 RPE/paper.tex
@@
-\documentclass[runningheads,a4paper]{llncs}
+% Note that the a4paper option is mainly intended so that authors in
+% countries using A4 can easily print to A4 and see how their papers will
+% look in print - the typesetting of the document will not typically be
+% affected with changes in paper size (but the bottom and side margins will).
+% Use the testflow package mentioned above to verify correct handling of
+% both paper sizes by the user's LaTeX system.
+%
+% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
+% should be used if it is desired that the figures are to be displayed in
+% draft mode.
+%
+\documentclass[conference]{IEEEtran}
+% Add the compsoc option for Computer Society conferences.
 
-\usepackage{amssymb}
-\setcounter{tocdepth}{3}
-\usepackage{graphicx}
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
 
+% *** CITATION PACKAGES ***
+%
+\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
+% not currently provide for hyperlinked citations.
+% The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+  \DeclareGraphicsExtensions{.pdf}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at: 
+% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
+% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+%\usepackage[cmex10]{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics. If using
+% it, be sure to load this package with the cmex10 option to ensure that
+% only type 1 fonts will utilized at all point sizes. Without this option,
+% it is possible that some math symbols, particularly those within
+% footnotes, will be rendered in bitmap form which will result in a
+% document that can not be IEEE Xplore compliant!
+%
+% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
+% There is also a support site at:
+% http://algorithms.berlios.de/index.html
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/tools/
+
+%\usepackage{mdwmath}
+%\usepackage{mdwtab}
+% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
+% especially mdwmath.sty and mdwtab.sty which are used to format equations
+% and tables, respectively. The MDWtools set is already installed on most
+% LaTeX systems. The lastest version and documentation is available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+%\usepackage{eqparbox}
+% Also of notable interest is Scott Pakin's eqparbox package for creating
+% (automatically sized) equal width boxes - aka "natural width parboxes".
+% Available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
+
+% *** SUBFIGURE PACKAGES ***
+%\usepackage[tight,footnotesize]{subfigure}
+% subfigure.sty was written by Steven Douglas Cochran. This package makes it
+% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
+% work, it is a good idea to load it with the tight package option to reduce
+% the amount of white space around the subfigures. subfigure.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at:
+% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
+% subfigure.sty has been superceeded by subfig.sty.
+
+%\usepackage[caption=false]{caption}
+%\usepackage[font=footnotesize]{subfig}
+% subfig.sty, also written by Steven Douglas Cochran, is the modern
+% replacement for subfigure.sty. However, subfig.sty requires and
+% automatically loads Axel Sommerfeldt's caption.sty which will override
+% IEEEtran.cls handling of captions and this will result in nonIEEE style
+% figure/table captions. To prevent this problem, be sure and preload
+% caption.sty with its "caption=false" package option. This is will preserve
+% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
+% (recommended due to many improvements over 1.2) of subfig.sty supports
+% the caption=false option directly:
+%\usepackage[caption=false,font=footnotesize]{subfig}
+%
+% The latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
+% The latest version and documentation of caption.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure. The latest version and documentation can be found at:
+% http://www.ctan.org/tex-archive/macros/latex/base/
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
+% Documentation is contained in the stfloats.sty comments as well as in the
+% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
+% does not allow \baselineskip to stretch. Authors submitting work to the
+% IEEE should note that IEEE rarely uses double column equations and
+% that authors should try to avoid such use. Do not be tempted to use the
+% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
+% not format its papers in such ways.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
 \usepackage{url}
-\urldef{\mailsa}\path|dejun@cs.pdx.edu|
-\newcommand{\keywords}[1]{\par\addvspace\baselineskip
-\noindent\keywordname\enspace\ignorespaces#1}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
+% Read the url.sty source comments for usage information. Basically,
+% \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
 \begin{document}
-
-\mainmatter  % start of an individual contribution
-
-% first the title is needed
+%
+% paper title
+% can use linebreaks \\ within to get better formatting as desired
 \title{coDoc: A Tool for Managing Relationships between Code and Documentation}
 
-% a short form should be given in case it is too long for the running head
-\titlerunning{coDoc: Managing Relationships between Code and Documentation}
+% author names and affiliations
+% use a multiple column layout for up to three different
+% affiliations
+\author{\IEEEauthorblockN{Xx Xxx}
+\IEEEauthorblockA{Computer Science\\
+Portland State University\\
+Portland, OR 97201\\
+Email: xx@cs.pdx.edu}
+\and
+\IEEEauthorblockN{Xx Xxx}
+\IEEEauthorblockA{Computer Science\\
+Portland State University\\
+Portland, OR 97201\\
+Email: xx@cs.pdx.edu}}
 
-% the name(s) of the author(s) follow(s) next
+% conference papers do not typically use \thanks and this command
+% is locked out in conference mode. If really needed, such as for
+% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
+% after \documentclass
+
+% for over three affiliations, or if they all won't fit within the width
+% of the page, use this alternative format:
 % 
-% NB: Chinese authors should write their first names(s) in front of
-% their surnames. This ensures that the names appear correctly in
-% the running heads and the author index.
-%
-\author{Dejun Qian}
-%
-\authorrunning{coDoc: Managing Relationships between Code and Documentation}
-% (feature abused for this document to repeat the title also on left hand pages)
+%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
+%Homer Simpson\IEEEauthorrefmark{2},
+%James Kirk\IEEEauthorrefmark{3}, 
+%Montgomery Scott\IEEEauthorrefmark{3} and
+%Eldon Tyrell\IEEEauthorrefmark{4}}
+%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
+%Georgia Institute of Technology,
+%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
+%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
+%Email: homer@thesimpsons.com}
+%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
+%Telephone: (800) 555--1212, Fax: (888) 555--1212}
+%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
 
-% the affiliations are given next; don't give your e-mail address
-% unless you accept that it will be published
-\institute{Computer Science Department,\\
-Portland State University,\\
-1900 SW 4th Avenue Portland, OR 97201, USA\\
-\mailsa\\
-\url{http://www.pdx.edu/computer-science/}}
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
 
-%
-% NB: a more complex sample for affiliations and the mapping to the
-% corresponding authors can be found in the file "llncs.dem"
-% (search for the string "\mainmatter" where a contribution starts).
-% "llncs.dem" accompanies the document class "llncs.cls".
-%
-
-\toctitle{Lecture Notes in Computer Science}
-\tocauthor{Authors' Instructions}
+% make the title area
 \maketitle
@@
 \begin{abstract}
-The reusing of either software or hardware components is an important way to build large systems.
+%\boldmath
+The reuse of either software or hardware components is an important way to build large systems.
 Documentation plays a critical role in the process of reusing,
@@
 such as device drivers and virtual device modules.
+Effectively relating the code and documentation reliablly can help improving the productivity of the developer and the quality of the software.
 This paper presents coDoc, 
@@
 We report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents by coDoc.
-\keywords{Software Engineering, Data Model}
 \end{abstract}
+% IEEEtran.cls defaults to using nonbold math in the Abstract.
+% This preserves the distinction between vectors and scalars. However,
+% if the conference you are submitting to favors bold math in the abstract,
+% then you can use LaTeX's standard command \boldmath at the very start
+% of the abstract to achieve this. Many IEEE journals/conferences frown on
+% math in the abstract anyway.
+
+\begin{IEEEkeywords}
+relationship, quality assurance, abstract syntax tree, tool.
+\end{IEEEkeywords}
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
 \section{Introduction}
+% no \IEEEPARstart
 \label{sec:introduction}
@@
 
-\section{Architecture and Features of coDoc}
+% An example of a floating figure using the graphicx package.
+% Note that \label must occur AFTER (or within) \caption.
+% For figures, \caption should occur after the \includegraphics.
+% Note that IEEEtran v1.7 and later has special internal code that
+% is designed to preserve the operation of \label within \caption
+% even when the captionsoff option is in effect. However, because
+% of issues like this, it may be the safest practice to put all your
+% \label just after \caption rather than within \caption{}.
+%
+% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+% option should be used if it is desired that the figures are to be
+% displayed while in draft mode.
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=2.5in]{myfigure}
+% where an .eps filename suffix will be assumed under latex, 
+% and a .pdf suffix will be assumed for pdflatex; or what has been declared
+% via \DeclareGraphicsExtensions.
+%\caption{Simulation Results}
+%\label{fig_sim}
+%\end{figure}
+
+% Note that IEEE typically puts floats only at the top, even when this
+% results in a large percentage of a column being occupied by floats.
+
+% An example of a double column floating figure using two subfigures.
+% (The subfig.sty package must be loaded for this to work.)
+% The subfigure \label commands are set within each subfloat command, the
+% \label for the overall figure must come after \caption.
+% \hfil must be used as a separator to get equal spacing.
+% The subfigure.sty package works much the same way, except \subfigure is
+% used instead of \subfloat.
+%
+%\begin{figure*}[!t]
+%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
+%\label{fig_first_case}}
+%\hfil
+%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
+%\label{fig_second_case}}}
+%\caption{Simulation results}
+%\label{fig_sim}
+%\end{figure*}
+%
+% Note that often IEEE papers with subfigures do not employ subfigure
+% captions (using the optional argument to \subfloat), but instead will
+% reference/describe all of them (a), (b), etc., within the main caption.
+
+\section{Motivation}
+\label{sec:motivation}
+In this section, we illustrate our motivation through a example.
+
+\section{Architecture of coDoc}
 \label{sec:arch}
@@
 \begin{figure}
-\begin{center}
-\includegraphics[width=0.55\textwidth]{architecture}
+\centering
+\includegraphics[width=2.5in]{architecture}
 \caption{coDoc Architecture and Features}
 \label{fig:architecture}
-\end{center}
 \end{figure}
 
-\subsection{Architecture of coDoc}
 The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
@@
 
+\subsection{CM}
+CM handles the code.
+
+\subsection{DM}
+DM handles the documentation.
+
+\subsection{RM}
+RM handles the relationships.
+
+\section{Data Model}
+
 \begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{datamodel}
+\centering
+\includegraphics[width=2.5in]{datamodel}
 \caption{Data Model for coDoc}
 \label{fig:datamodel}
-\end{center}
 \end{figure}
 
-\subsection{Data Model}
 The data model is shown in Figure \ref{fig:datamodel}.
@@
 \begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{ast1}
+\centering
+\includegraphics[width=2.5in]{ast1}
 \caption{Original code and its AST}
 \label{fig:ast1}
-\end{center}
 \end{figure}
@@
 \begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{ast2}
+\centering
+\includegraphics[width=2.5in]{ast2}
 \caption{Evolved code and its AST}
 \label{fig:ast2}
-\end{center}
 \end{figure}
 
-\subsection{Representing Code Segments}
+\section{Representing Code Segments}
 Code is always evolving during its lifetime.
@@
 
+% An example of a floating table. Note that, for IEEE style tables, the 
+% \caption command should come BEFORE the table. Table text will default to
+% \footnotesize as IEEE normally uses this smaller font for tables.
+% The \label must come after \caption as always.
+%
+%\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+%\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+%\caption{An Example of a Table}
+%\label{table_example}
+%\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+%\begin{tabular}{|c||c|}
+%\hline
+%One & Two\\
+%\hline
+%Three & Four\\
+%\hline
+%\end{tabular}
+%\end{table}
+
+% Note that IEEE does not put floats in the very first column - or typically
+% anywhere on the first page for that matter. Also, in-text middle ("here")
+% positioning is not used. Most IEEE journals/conferences use top floats
+% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
+% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
+% command of the stfloats package.
+
 \section{Evaluation}
@@
 \begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{platformview}
+\centering
+\includegraphics[width=2.5in]{platformview}
 \caption{coDoc Platform View}
 \label{fig:platformview}
-\end{center}
 \end{figure}
@@
 
-% Bibliography
-\bibliographystyle{splncs03}
+% conference papers do not normally have an appendix
+
+% use section* for acknowledgement
+\section*{Acknowledgment}
+
+The authors would like to thank...
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+\bibliographystyle{IEEEtran}
 \bibliography{reference}
 
+% that's all folks
 \end{document}

### 2013-04-18 RPE/paper.tex
backup
abstract

@@
 % first the title is needed
-\title{coDoc: A Tool for Managing Relationships between Code and Documentation}
+\title{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{coDoc: Managing Relationships between Code and Documentation}
+\titlerunning{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
 
@@
 %
-\authorrunning{coDoc: Managing Relationships between Code and Documentation}
+\authorrunning{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 Portland State University,\\
-1900 SW 4th Avenue Portland, OR 97201, USA\\
-\mailsa\\
-\url{http://www.pdx.edu/computer-science/}}
+1900 SW 4th Avenue Portland, OR 97201, USA}
+%\mailsa\\
+%\url{http://www.pdx.edu/computer-science/}}
 
@@
 \begin{abstract}
-The reusing of either software or hardware components is an important way to build large systems.
-Documentation plays a critical role in the process of reusing,
-as it describes how the components can be reused.
-When writing and testing software, 
-we need the documentation in hand.
-This is particularly true for software that is documentation-intensive, 
-such as device drivers and virtual device modules.
-This paper presents coDoc, 
-an integrated development environment for managing relationships between code and documentation.
-We describe the architecture and features of coDoc,
-and discuss several design decisions that we faced in developing coDoc and the trade-offs involved in making these decisions.
-We report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents by coDoc.
-\keywords{Software Engineering, Data Model}
+Traceability links between specifications and implementations play a crucial role in improving the quality of hardware/software (HW/SW) interfaces. 
+HW/SW interface specifications are typically stable while their hardware and software implementations are constantly evolving even after their releases. 
+Due to the low abstraction levels of HW/SW interfaces, 
+these specifications are often quite detailed, 
+thus demanding fine-grained traceability links. 
+In this paper, we present a framework for managing traceability links between specifications and implementations of HW/SW interfaces. 
+This framework supports fine-grained links between basic elements of specifications and semantic constructs of implementation languages. 
+It also supports automatic migration of links as implementations evolve. 
+We have implemented a prototype tool, namely coDoc, in support of this framework. 
+We have applied coDoc to ten versions of three virtual devices in the QEMU virtual machine.
+Experimental results show that our framework fully supports the types of traceability links between the virtual devices and their specifications,
+and it accurately migrates valid links from version to version.
+%\keywords{Software Engineering, Data Model}
 \end{abstract}
 
+%\newpage
 \section{Introduction}
@@
 Section \ref{sec:conclusion} concludes our work and gives our future research plan.
+
+introduction - give the problem (create and manage links)
+motivation and definition - example to illustrate the problem (further illustrate the problem)
+architechture and data model (a general framework to solve the problem) - key as a requirement
+handle some specific difficulties - our solution using ast tree
+evaluation - three vd with ten version
+related work
+conclusion
 

### 2013-05-04 RPE/abstract.tex
class review version

--- 2013-04-18 RPE/paper.tex
@@
-\documentclass[runningheads,a4paper]{llncs}
-
-\usepackage{amssymb}
-\setcounter{tocdepth}{3}
-\usepackage{graphicx}
-
-\usepackage{url}
-\urldef{\mailsa}\path|dejun@cs.pdx.edu|
-\newcommand{\keywords}[1]{\par\addvspace\baselineskip
-\noindent\keywordname\enspace\ignorespaces#1}
-
-\begin{document}
-
-\mainmatter  % start of an individual contribution
-
-% first the title is needed
-\title{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
-
-% a short form should be given in case it is too long for the running head
-\titlerunning{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
-
-% the name(s) of the author(s) follow(s) next
-%
-% NB: Chinese authors should write their first names(s) in front of
-% their surnames. This ensures that the names appear correctly in
-% the running heads and the author index.
-%
-\author{Dejun Qian}
-%
-\authorrunning{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
-% (feature abused for this document to repeat the title also on left hand pages)
-
-% the affiliations are given next; don't give your e-mail address
-% unless you accept that it will be published
-\institute{Computer Science Department,\\
-Portland State University,\\
-1900 SW 4th Avenue Portland, OR 97201, USA}
-%\mailsa\\
-%\url{http://www.pdx.edu/computer-science/}}
-
-%
-% NB: a more complex sample for affiliations and the mapping to the
-% corresponding authors can be found in the file "llncs.dem"
-% (search for the string "\mainmatter" where a contribution starts).
-% "llncs.dem" accompanies the document class "llncs.cls".
-%
-
-\toctitle{Lecture Notes in Computer Science}
-\tocauthor{Authors' Instructions}
-\maketitle
-
 \begin{abstract}
-Traceability links between specifications and implementations play a crucial role in improving the quality of hardware/software (HW/SW) interfaces. 
-HW/SW interface specifications are typically stable while their hardware and software implementations are constantly evolving even after their releases. 
-Due to the low abstraction levels of HW/SW interfaces, 
-these specifications are often quite detailed, 
+Traceability links between specifications and implementations of hardware/software (HW/SW) interfaces play a crucial role in improving the quality of computer systems.
+On one hand, HW/SW interfaces are often quite detailed, on low abstraction levels, 
 thus demanding fine-grained traceability links.
+On the other hand, HW/SW interface specifications are typically stable while their hardware and software implementations are constantly evolving even after their releases, which requires robust traceability links.
 In this paper, we present a framework for managing traceability links between specifications and implementations of HW/SW interfaces. 
-This framework supports fine-grained links between basic elements of specifications and semantic constructs of implementation languages. 
+This framework supports fine-grained traceability links between basic elements of specifications and constructs of implementation languages.
 It also supports automatic migration of links as implementations evolve. 
@@
 \end{abstract}
-
-%\newpage
-\section{Introduction}
-\label{sec:introduction}
-Documentation plays an important role in software engineering.
-%from requirement analysis to architecture design,
-%from coding to software testing,
-%from software debugging to software maintenance.
-Software that relates closely to hardware is extremely documentation intensive. % explain why
-Examples of such software include bootloaders, 
-Hardware Abstraction Layers (HAL) in Operating Systems (OS),
-and virtual device modules for virtual machines.
-Such software must follow the hardware documentation to operate correctly.
-A typical embedded CPU might have documentation consisting of thousands of pages.
-A computer system usually consists of more than ten hardware modules.
-Effectively maintaining the relationships between the code and the documentation is important for developing and verifying hardware-related software.
-
-To our knowledge, there are no tools to address this problem.
-Researchers have done a lot of work to handle the relationships between Application Programming Interface (API) documents and their client code \cite{Pandita_inferring_2012} \cite{wei_inferring_2011}.
-However, the approaches developed in the work do not consider the relationships between hardware-related code and its documentation.
-API documents are usually well indexed by the functions or the classes that they define.
-When we are interested in a piece of code in the client software
-we can easily find the related API documents by the names of the functions that the piece of code calls.
-% The relationships between the client codes and the API documents can be easily constructed by using the function names as the keywords.
-However, the code relating to hardware and its documentation usually relate in different ways.
-% the hardware docuemnts are not orgnized by functions or classes, which are the basic elements of code, but instead by hardware modules.
-People usually organize hardware documentation by hardware modules and the registers inside the hardware modules.
-These modules and registers do not relate to the code in an explicit way.
-Hardware documents include text, tables and diagrams, while API documents usually include text only.
-
-% These differences make the constructing of the relationships between the hardware related codes and their documents really challenging.
-A simple workaround is to include references to the positions of the related documentation as comments in the code.
-However, this can only handle simple situations.
-If there are thousands of such comments cluttered in the code,
-it will be very hard to manage them.
-
-This paper presents coDoc, a tool to create, maintain, and display relationships between code and documentation.
-% The initial version\footnote{\texttt{\url{git@github.com:derekqian/coDoc.git}}} has been released.
-The key features of coDoc include 
-the ability to display both code and documents, 
-the ability to write and edit code, 
-code-piece selection based on syntax tree of the code,
-%stable code selections regarding to the changes of unrelated codes;
-creation of relationships between codes and documents,
-and relationships management and display.
-Using coDoc, we have created relationships between two virtual NIC devices in QEMU and the related documents.
-These two devices are DIO \cite{dio} and E100 \cite{e100}.
-
-The main contributions of this paper are as follows.
-\begin{itemize}
-\item Design a framework to display and manage codes, documents and relationships.
-\item Design coDoc which implement the framework.
-\item Maintain integrity of the relationships when the code evolves.
-\item Design a standard format to represent the code piece.
-\item Design a standard format to represent the document piece.
-\item Design a data model for relationships between code and documentation.
-\end{itemize}
-
-The rest of the paper is organized as follows. 
-Section \ref{sec:arch} provides the overall architecture and key features of coDoc.
-%Section \ref{sec:decision} gives the design decisions of coDoc and the trade-offs of these decisions.
-Section \ref{sec:evaluation} summarizes our experiences of creating and maitaining the relationships for two virtual devices.
-Section \ref{sec:related} presents the related work.
-Section \ref{sec:conclusion} concludes our work and gives our future research plan.
-
-introduction - give the problem (create and manage links)
-motivation and definition - example to illustrate the problem (further illustrate the problem)
-architechture and data model (a general framework to solve the problem) - key as a requirement
-handle some specific difficulties - our solution using ast tree
-evaluation - three vd with ten version
-related work
-conclusion
-
-\section{Architecture and Features of coDoc}
-\label{sec:arch}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.55\textwidth]{architecture}
-\caption{coDoc Architecture and Features}
-\label{fig:architecture}
-\end{center}
-\end{figure}
-
-\subsection{Architecture of coDoc}
-The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
-It contains a code manager (CM), a documentation manager (DM) and a relationship manager (RM).
-There are three types of data here, 1) code, 2) documentation, and 3) relationships.
-We handle only C/C++ code at this time, 
-as most system code is written in C/C++.
-CM reuses C/C++ Development Tool (CDT) editor from Elipse\footnote{\texttt{\url{http://www.eclipse.org}}} to handle C/C++ code.
-The CDT editor reads and parses the code, 
-and highlights syntax elements.
-We use poppler to read the PDF file and render the PDF pages as images.
-As poppler is developed in C++ and Eclipse Rich Client Program (RCP) is in Java,
-we need an adaptor to bridge between C++ and Java,
-for which we use Java Native Interface (JNI).
-We implement this adaptor in PDF Editor, 
-and uses it to get the PDF page from poppler and display the page.
-RM reads the relationship data,
-and highlights the code and document pieces that are related.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{datamodel}
-\caption{Data Model for coDoc}
-\label{fig:datamodel}
-\end{center}
-\end{figure}
-
-\subsection{Data Model}
-The data model is shown in Figure \ref{fig:datamodel}.
-We have four entities here: category, relationship, code piece and documentation piece.
-Code piece and documentation piece represent the selected code and documentation respectively.
-We represent the relationships between code and documentation as entities,
-as we want to classify the relationships.
-The relationships are classified by their functionality in our approach.
-Category is used to maintain the classification information of the relationships.
-To represent a relationship, 
-we need to define the strategy to represent the code piece and documentation piece.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{ast1}
-\caption{Original code and its AST}
-\label{fig:ast1}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{ast2}
-\caption{Evolved code and its AST}
-\label{fig:ast2}
-\end{center}
-\end{figure}
-
-\subsection{Representing Code Segments}
-Code is always evolving during its lifetime.
-We want the relationships created for one version of code keep working for other versions.
-To achieve this goal, we need a robust strategy to represent the code pieces.
-Our first method represents the code piece by the offset of the selected code from the beginning of the code file and the length of the selected code.
-This method is straight forward and is easy to understand and implement.
-However, this method is not robust,
-as the change of the code file will change the offset of the selected code.
-The left sides of Figure \ref{fig:ast1} and Figure \ref{fig:ast2} give the code before and after it evloves.
-The highlighted code piece is what we want to select.
-Unfortunitely, the offset of the select code increases after we add some code,
-as shown in this example.
-To achieve robustness, we need to find some properties of the code that are relatively stable when code evolves.
-These properties can serve as keys to represent the code piece.
-An intuitive thought is to use the semantic information,
-that is the intrinsic meaning of the code.
-However, we can't find a formal way of defining this information.
-We use syntax information to form the main element of our code piece identifier.
-The code can be parsed and represented by a syntax tree.
-A change of the code in one branch will usually not affect the code in other branches.
-Representing code segments based on the position in the syntax tree should be robust.
-The right sides of Figure \ref{fig:ast1} and Figure \ref{fig:ast2} are the Abstract Syntax Trees (AST) for the code before and after it evolves.
-In the ASTs, the highlighted nodes relate to the code piece we selected.
-Through the two ASTs are different, 
-the highlighted nodes can be represented by the same path from the roots of these two ASTs.
-%To make the method more robust, % prof lost here
-%we can introduce the information in the first method as the secondary key.
-%When the syntax identifier fails to locate the code piece,
-%we can use the offset information to assist the decision.
-%We also include in the identifier the content of the code piece as an integrity check.
-%The structure used to achieve this goal is shown bellow.
-%\begin{Verbatim}[frame=single]
-%class CodeSelection {
-%  private String syntaxcodepath;
-%  private String selcodepath;
-%  private String syntaxcodetext;
-%  private String selcodetext;
-%}
-%\end{Verbatim}
-
-%\section{Methodology and Design Decisions}
-%\label{sec:decision}
-%\subsection{Embedded vs Seperate for PDF Reader}
-%The tool should display both codes and documents at the same time.
-%We can implement the code viewer and the PDF viewer in seperate process,
-%and use inter process communication (IPC) techniques to communicate.
-%The advantage of this method is that each process has its own window,
-%can occupy the whole screen,
-%and display more content which reduces the need to scroll the window horizontally.
-%When the user uses a computer with two monitors,
-%the tool implementing this method is an extremely good choice,
-%as the user can choose to display the code and the document on seperate moniters.
-%However, this implementation is heavy, % ?
-%and has performance issues.
-%When using the tool, 
-%the user may need to launch the PDF reader,
-%which is slow.
-%Our earlest implementation uses this method,
-%and encountered synchronization problems from the IPC communication.
-%In coDoc, we choose to implement the code viewer and the PDF viewer in the same process.
-%%The Eclipse framework even makes the whole system single thread.
-%This way, all the commucation is internal to the same process,
-%No IPC communication is needed,
-%which is more efficient and makes the tool more responsive.
-%With the new method, we can smoothly operate the tool without any uncomfortable feeling.
-%The advantages of the first method become the disadvantage of the new method,
-%as the code viwer and the document viwer must share the whole screen now.
-%However, with a efficient and user-friendly method of assigning screen area,
-%we can make the user feel less uncomfortable when viewing the content.
-%Also, most programmer now not only are using two moniters, % prove
-%but also the moniters they are using are larger and larger.
-%Using a larger moniter with high definition will make this disadvantage nothing. % need revisement
-%And even better, in this situation, this method will overcome the first method,
-%as moving the eyes between two big moniter is energy consuming.
-
-\section{Evaluation}
-\label{sec:evaluation}
-%We adopt poppler, a open-source PDF render, to render PDF content in coDoc.
-%This PDF render is written in C++, 
-%and is widely used in Linux systems.
-%It uses Cairo and GTK to draw the rendered content.
-
-\textbf{Effectiveness.} We evaluated coDoc by setting up relationships between the code for two virtual devices and their documentation.
-The number of relationships created and the time used to created these relationships are listed in Table \ref{table:evaluate}.
-
-\begin{table}[th]
-\caption{Evaluate Result}
-\centering
-\begin{tabular}{rcc}
-\hline
-Code & \# of Relationships & time(hr) \\
-\hline
-dio & 108 & 2 \\
-e100  & 213 & 4\\
-\hline
-\end{tabular}
-\label{table:evaluate}
-\end{table}
-
-The identifying method with fine granularity makes the relationship created by coDoc very accurate, 
-80\% of the code pieces are marked inside the statement.
-This result is hard for comment-based method to achieve.
-The same result happens for the document.
-In the whole relationships, 
-90\% of the document pieces are marked on cells in the tables.
-The comments in the PDF file will be too crowd to be useful,
-as it will affect the normal reading of the document.
-Our approach can also make the development efficient,
-as we don't need the developer to change either the code or the document while only relationship is created.
-This makes the code and document neat and easily to read and understand.
-
-\noindent \textbf{Usability.} We implemented coDoc as an Elipse Rich Client Program (RCP), 
-which can make our tool share the appearence in Eclipse that is familiar by many programmer.
-Figure \ref{fig:platformview} is the screenshot of the tool.
-Three persons with no prior exprience with coDoc have successfully use this tool to create the relationships between their codes and documentation.
-They didn't find any difficulties when using this tool.
-All the feedbacks has been positive regarding the use of the tool.
-%Now they can easily create their relationships by selecting the code and document piece using mouse, input the comment using keyboard.
-%They can also manage the relationships by sorting by attributes, search certain relationships by keywords.
-%They also find the feature that allow them to categorize the relationships helpful.
-%This feature makes the relationships neater when the number of relationships is large.
-
-In our own experience, we found that the ability to see the code, 
-the documentation and the relationships on the same screen saves a lot of time,
-as we don't need to switch between different tools.
-%The visualized interface also saved us time to learn the detailed syntax about the identifier formats,
-%and to write the identifier manually.
-We believe this tool will lead to increased productivity.
-
-% convert platformview.png platformview.eps
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{platformview}
-\caption{coDoc Platform View}
-\label{fig:platformview}
-\end{center}
-\end{figure}
-
-\section{Related Work}
-\label{sec:related}
-Current tools can manage codes. 
-These kinds of tools include revision control software like git, svn \cite{git} \cite{svn}. 
-Revision control tools can give the evolving history of the software.
-These tools usually adopt text comparison tools to figure out the differences between different versions of the software.
-The comparation tools can easily give the result about the matching points and mismatching points in the codes,
-which means they can manage the relationships between different versions of codes.
-However, these tools are not designed to manage documents.
-Though some people also use them to manage documents,
-they only use it as a persistent data warehouse.
-They can not take the advantages of the comparison tools, 
-as these tool usually can only deal with text file.
-People are using code comments to record the related document piece.
-However, no consistent format exists,
-which makes these information not managable,
-especially when these comments are made by many different developers.
-
-Full text indexing system is developed to processing documents \cite{lucene}.
-However, they can only relate keywords to certain documents.
-They do not deal with both codes and documents. 
-Like full text indexing system,
-search engines also work with documents in similar way.
-Most of the documents that are handled by search engines are web pages.
-Many PDF readers can support highlighting and commenting.
-With these features, we can relate a document piece to a code piece.
-However, these links created are not stable,
-and PDF readers can not check the integrity of these information.
-
-Generally speaking, these are tools can either do code management or do document management.
-However, they are not designed to do both,
-and managing the relationships between codes and documents is definitely a mission impossible task for them.
-
-% Based on what you have so far, what can you conclude?  What cool ideas did you think up but not have time to implement so far?
-\section{Conclusions and Future Work}
-\label{sec:conclusion}
-We have implemented coDoc, 
-a tool for managing the relationships between the hardware related programs and their documentation.
-The main contribution of this paper is the method to identify the code segment.
-Our experiences of using coDoc to manage the code for two virtual devices and their documentation shows the tool is robust and efficent,
-and is helpful when developing and maitaining the virtual devices.
-The relationships remain stable even when the code changes.
-
-There are still opportunities to improve coDoc.
-\begin{enumerate}
-\item Combine it with revision control tools to provide a more user-friendly tool suit for developing and maitaining the codes while managing the documents at the same time.
-\item Design more robust method to identify the document pieces in the PDF documents to make the tool invariant to the change of the documents.
-\item Use machine learning (use the data created as seed to train the model) to construct and check the relationships between hardware related codes and their documents.
-\end{enumerate}
-
-% Bibliography
-\bibliographystyle{splncs03}
-\bibliography{reference}
-
-\end{document}

### 2013-05-04 RPE/approach.tex
class review version

\section{Our Approach}
\label{sec:approach}

We first present an overview of our approach. Then, we propose the underlying data model. The data model introduces the requirement \hlc{of the} techniques to represent the POIs and the POSes. We illustrate how our approach address this problem at last.

\subsection{Overview}
\todo{this section need rewriting. focus on data.}
\begin{figure}
\begin{center}
\includegraphics[width=0.55\textwidth]{framework}
\caption{Framework of Our Approach.}
\label{fig:framework}
\end{center}
\end{figure}

As shown in Fig.~\ref{fig:framework}, the framework of our approach consists three components: database, control logic, and user interface. The structure of the traceability link data in the database is defined by the data model. Control logic lays in the middle of user interface and datamodel. It receives and processes command from the user interface. Depending on the command, it either updates the database, or queries the data in the database and report the result to the user interface. User interface is responsible of communicating with the end user, processs and passes the input from user to the control logic, get the result from the control logic and present the result to the user.

\begin{figure}
\begin{center}
\includegraphics[width=0.85\textwidth]{datamodel}
\caption{Data Model. Entity-Relation Model is used. Rectangles represent entity sets. Ovals represent attributes. Diamonds represent relationships.}
\label{fig:datamodel}
\end{center}
\end{figure}

\subsection{Data Model}
The data model is the key to support fine-grained links between basic elements of specifications and semantic constructs of implementation languages and automatic migration of links as implementations evolve. We introduce the data model of our approach in this section.

The data model describes the data objects being handled in the framework, their attributes, and the relationships between these data objects.
Fig.~\ref{fig:datamodel} presents the data model of our design.
Entiry-relationship model is used.
Rectangles represent entiry sets.
Ovals represent attributes.
Diamonds represent relationships.
We have four entity sets in our design: code file mark, spec file mark, code piece anchor and specification piece anchor.
Code piece anchor and specification piece anchor represent the selected code and specification piece respectively.
Both code file mark and spec file mark entities have attributes id and path:
id is a 128-bit number, and serves as the key of the entity;
path is the file path pointing to a file in the local machine. % not a key, it may change
Code piece anchor and spec piece anchor have id and path as attributes:
id is a 128-bit number, and serves as the key;
path points to the code or spec piece.
Traceability links are represented by the relationships between code piece anchor and spec piece anchor.

Special attention should be paid to four attributes: path for code file, path for spec file, path for code piece anchor and path for spec piece anchor.
\todo{explain}\hlc{These four attributes are foreign keys used to refer to data that do not exist in database.}
As foreign keys, these attributes should be able to uniquely identify the entities they refer to.
The path provided by the file system is a solution to the path for code files and spec files, as we can easily identify both code files and spec files by these pathes.
The pathes for anchors are challenging, little work has been done to address this problem.

%Based on the model above, we can conclude the schema as following.
%Examples?

\subsection{Anchor Design}

Anchors includes specification anchor and implementation anchor. The three basic requirements for traceability links are the constraints for the design. We present how our approach make these requirements fulfilled. Specification anchor design is addressed first, then we present the implementation anchor design.

\subsubsection{Spec Anchor}

Specifications are relatively stable, which make the specification anchor design easier than implementation anchor. Using the absolute coordinate is enough to meet the requirements. Most of the HW/SW interface specification are in PDF format. We use this format to present our approach. Basically, the coordinate for specification piece is denoted by two points -- the point representing the beginnings of the selection and the point representing the end of the selection. Each point is denoted by a vector $<$page, x-coord, y-coord$>$, where page is the page number the point located, x-coord and y-coord are the horizontal and vertical coordinate respectively.

The method is accurate as each point is uniquely represented by the coordinate. This method is also fine-grained, because this method could represent each word, sentence or evan arbitrary size of POS. The method is not robust as it uses the absolute coordinate as the basic element of the anchor. However, specifications are relatively stable, which makes this approach work most of the time.

\subsubsection{Offset-Based Anchor}

Similar to specification anchor,
absolute coordinates also fit the situation of implementation anchor.
Basically, implementation code is just a string of ASCII charactors. 
Each piece of code is a substring of this string.
We can use the offset of the substring in the string and the length of the piece of code to represent this piece of code.
The pair (offset, length) is called Offset-Based Anchor.
Fig.~\ref{fig:code}(a) illustrate this technique.
The parenthesized number in front of each line represent the offset of the first charactor of that line.
Using this approach, we can get the Offset-Based Anchors for the three code pieces labeled 1, 2 and 3 as (590, 4), (614, 4) and (635, 4) respectively.

The advantage of this technique is obvious, it is simple and provides fine-grained traceability. The disadvantage of this technique is that these anchors fail after the code evolves. Fig.~\ref{fig:code}(b) is the code after the code in Fig.~\ref{fig:code}(a) evolves. We can see the anchors we get above do not point to the previous pieces of code anymore. The reason is that this approach is context sensitive. By saying context sensitive, we mean it depends on its context. In this approach, the anchor depends on the number of charactors preceeding the piece of code.

One way to overcome this disadvantage is to get the knowledge of change to keep the links valid. However, this information is not always available. Most of the time, code is changed by other people. We can only get the changed result without how the change is made.

% a figure example
\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{c}
\begin{minipage}[b]{\linewidth}
  \centering
  \includegraphics[width=0.8\linewidth]{ast1}
\end{minipage}\\
(a) AST for the Code in Fig.~\ref{fig:code}(a)\\
\\
\begin{minipage}[b]{\linewidth}
  \centering
  \includegraphics[width=0.8\linewidth]{ast2}
\end{minipage}\\
(b) AST for the Code in Fig.~\ref{fig:code}(b)\\
\\
\begin{minipage}[b]{\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{ast_legend}
\end{minipage}
\end{tabular}
\caption{The AST for the implementation code in Fig.~\ref{fig:code}.}
\label{fig:ast}
\end{center}
\end{figure}

% syntax tree, a string of syntax tree leaf nodes.
% content-free (make immune from change of the content) vs content-sensitive (make unique)
% evaluate on unique
\subsubsection{Syntax Tree Based Anchor}
To make the traceability links created for one version of code work for other versions,
we need a robust strategy to represent the code pieces.
More specifically, we need to find some properties of the code that are relatively stable when code evolves.
These properties can serve as keys to identify the code piece.
We use syntax information to form the main element of our code piece identifier.
The code can be parsed and represented by a parse tree or an abstract syntax tree (AST).
We use AST in our approach, as it faithfully retains the structure of the original source code, and is concise and efficient to compute compared to parse tree.
AST usually has fewer nodes than parse tree, and takes less time to traverse.
Each node in AST tree represents a syntax unit of the grammer,
a parent of a node represent a bigger grammer unit that includes the grammer unit represented by the child node.
The nodes are labeled by the type of the grammer unit.
For each leaf node, we also include the value, which is the code this node represents, in the label.
For some of the inner nodes that have a name, we also include the name in their labels. For example, a inner node that represents a function will be labeled with the grammer unit type and the name of the function.
A change of the code in one branch of AST usually does not affect the structure in other branches.
Representing code pieces based on the structure in the syntax tree is robust.
Fig.~\ref{fig:ast}(a) and Fig.~\ref{fig:ast}(b) are the Abstract Syntax Trees (AST) for the code in Fig.~\ref{fig:code}(a) and Fig.~\ref{fig:code}(b).
Dot lines represent branches not shown.
Fig.~\ref{fig:ast}(a) shows two subtrees of the root.
The left subtree represents line 13 - line 25 of Fig.~\ref{fig:code}(a), which defines the structure max7310\_s.
The right subtree represent line 27 - line 35 of Fig.~\ref{fig:code}(a), which defines the function max7310\_reset.
Similarly, the left subtree of the AST in Fig.~\ref{fig:ast}(b) represent line 12 - line 24 in Fig.~\ref{fig:code}(b), and the right subtree represents line 26 - line 34.
From the AST shown in Fig.~\ref{fig:ast}(a) and fig.~\ref{fig:ast}(b), we can see that the left tree has changed as the code for structure definition changed.
However, the structure of the right subtree remain the same, unaffected by the change of the left subtree.

Based on the AST of the code, we define our identifier to a piece of code as a sequence of leaf nodes in the AST. Each leaf node is represented by the path from the leaf node to the root of the AST. For example, line 31 in Fig.~\ref{fig:code}(a) is represented by the highlighted three leaf nodes in Fig.~\ref{fig:ast}(a). The leaf nodes are in the same order as they are visited by depth-first search of the AST. For this example, the closest common parent node for these three leaf nodes also represents the same piece of code, and thes representation is even simpler. We avoid using this representation for two reasons: First, this representation contains less information; Second, this representation is sensitive to formatting and style convention. For example, some programmer may prefer no spaces adjacent to the equal sign, or they may insert some spaces besides the equal sign to make it aligned with other lines of assignment statements. Either case will change the string represented by this common parent, and make the traceability link invalid. We will address how we determine if a traceability link is valid or not in the next section.

Using this approach, let's consider the pieces of code label by 1, 2 and 3 in fig.~\ref{fig:code} again. The identifier for these code pieces in AST are shown in fig.~\ref{fig:ast} labeled with the same number.
Through the two ASTs are different, 
the highlighted nodes can be represented by the same path from the roots of these two ASTs.
As a result, we can use this method to identify the piece of code, and the change of the unrelated code does not invalidate the identifier.

This method is relatively stable.
However, it may not uniquely identify a piece of code,
which means one identifier may refer to two or more pieces of code.
The pieces of code label by 1 and 3 in fig.~\ref{fig:ast}(a) showes two pathes that are encoded as the same identifier -- $<$\texttt{LE:0xff/BE/ES/CS/FD:max7310\_reset/TU}$>$.
As a result, this identifier can not distinguish these two pieces of code, 
and can not serve as a key to these pieces of code.

\subsubsection{Hybrid Anchor}

Offset-based anchor can uniquely identify a piece of code, but it is not immune to code evolusion.
Syntax tree based anchor is immune to code evolusion, but it can not uniquely identify some pieces of code.
We combine these two methods and form hybrid anchor.
For each leaf node that has an ambiguous path representation,
we can always find at least one of its ancesters that has an unique path.
In the worst case, we will get to the root node.
Our approach is composed of two steps.
First, we compute the syntax tree based anchor,
then, we go over the path from leaf to root, find the first node that is a unique identifier.
Second, we compute offset based anchor based on this unique identifier instead of the begining of the whole implementation code.
Consider the AST in fig.~\ref{fig:ast}(a), to identify the piece of code labeled by 1,
we go through the path towards the root,
and get to the first unique identifier at the inner node CS.
The node CS represent line 28 - line 35 of the code in fig.~\ref{fig:code}(a).
It is the body of the function \texttt{max7310\_reset}, and there is only one body for this function by the C language grammer.
The offset based identifier based on this node is (103,4), as the first charactor of the node CS is located at offset 487 and the offset based anchor is (590,4).
We combine the information of the inner node CS and the calculated coordinate to represent the piece of code with no ambiguity.
Same as offset based anchor, if the code does not change, it can uniquely identify the piece of code.
If the code changes, this method still works if the code for the unique identifier remain the same.
Actually, this is a general approach for the previous two.
If we get to the root node while finding the first unique ancestor, then this approach will become the same as offset based anchor.
However, if the lead node itself is the firtst node with unique identifier, then this approach is the same as syntax based anchor.
The lower the node with the unique identifier in AST, the better our approach works.
%However, this method provide redundent information, which can be used to check the validity.

% example?

### 2013-05-04 RPE/conclusion.tex
class review version

\section{Conclusions and Future Work}
\label{sec:conclusion}
We present an approach to manage the traceability links between HW/SW interface specifications and implementations, considering the unique properties of these traceability links. We also implemented our approach in a prototype, namely, coDoc, and used this tool to evaluate our approach. We did the experiments on three virtual device prototypes in QEMU. The results show that our approach can effectively manage traceability links for HW/SW interface implementations and their specifications. 70\% of the traceability links are fine-grained, 80\% of them remains valid after source code evolves to a new version.

In the future, we will continue our research in the following directions. First, we will consider the specification change, and develop strategy to manage traceability links in this circumstance. Second, we will develop automatic traceability link recovering technique for device drivers and their specifications.

### 2013-05-04 RPE/evaluation.tex
class review version

\section{Evaluation}
\label{sec:evaluation}

\subsection{Experimental Setup}
\todo{The data in the section are fake.}
We evaluate our approach on four virtual device prototypes in QEMU. QEMU is a generic and open source machine emulator, which can host unmodified guest operating systems \cite{bellard_qemuwiki_2013} \cite{bellard_qemu_2005}. QEMU includes virtual implementations for a large number of hardware devices. We do our evaluation on four of them: MAX7310, RTL8139, EEPro100 and E1000. MAX7310 is a 8-bit I/O expander developed by Maxim. This device is used when a system need more I/O ports. EEPro100, E1000 and RTL8139 are three popular network adapters. Both EEPro100 and E1000 are developed by Intel, and RTL8139 is developed by Realtek. All these four devices have specifications in PDF (Portable Document Format) format. We examined the release history of the virtual implementations and specifications of these four hardware device, and found that almost no change has been made to specifications after the corresponding implementations have begun to release.

Based on the QEMU repository, the virtual device prototypes for MAX7310, RTL8139, EEPro100 and E1000 have 22, 143, 163 and 168 versions since they are first created. We check out ten stable versions of all these virtual device drivers from the repository. 
The ten versions we used are stable-0.10, stable-0.11, stable-0.12, stable-0.13, stable-0.14, stable-0.15, stable-1.0, stable-1.1, stable-1.2 and stable-1.3, we represent them as 1 - 10 repectively.
We present the average lines of code (LOC) and the average number of functions of the virtual device prototypes, as well as the number of pages of the specifications in Table \ref{table:vdd}.
The LOC metrics are measured by the tool named locmetrics.
The lines of code (LOC) range from 181 to 2771. The sizes of specification range from 15 pages to 410 pages.

The changes from version to version for all the four virtual device prototypes are shown in Table \ref{table:version}. The changes are measured by the lines of code different from version to version using an open source tool cloc.

\begin{table}[th]
\caption{Three Virtual Device Drivers Used for Evaluation}
\centering
\begin{tabular*}{0.6\textwidth}{@{\extracolsep{\fill}}rccc}
\hline
 & \multicolumn{2}{c}{implementation} & specification \\
\cline{2-4}
 & LOC & Functions & pages \\
\hline
MAX7310 & 181 & 9 & 15\\
RTL8139  & 2771 & 101 & 67\\
EEPro100  & 1870 & 64 & 175\\
E1000  & 1905 & 52 & 410\\
\hline
\end{tabular*}
\label{table:vdd}
\end{table}

\begin{table}[th]
\caption{The Changes in Ten Versions}
\centering
\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}rccccccccc}
\hline
 & 1-2 & 2-3 & 3-4 & 4-5 & 5-6 & 6-7 & 7-8 & 8-9 & 9-10 \\
\hline
MAX7310 & 32 & 28 & 0 & 0 & 18 & 0 & 24 & 0 & 0\\
RTL8139 & 50 & 349 & 120 & 41 & 432 & 116 & 123 & 9 & 88\\
EEPro100 & 81 & 765 & 903 & 22 & 304 & 231 & 135 & 21 & 2\\
E1000 & 64 & 199 & 39 & 42 & 80 & 120 & 198 & 25 & 27\\
\hline
\end{tabular*}
\label{table:version}
\end{table}

% accuracy
\subsection{Accuracy}
We measure the accurary by the number of uniquely identifiable POC over number of traceability links recovered for all the virtual prototypes. The result is shown in Table \ref{table:accuracy}

\begin{table}[th]
\caption{Accuracy}
\centering
\begin{tabular*}{0.3\textwidth}{@{\extracolsep{\fill}}rc}
\hline
 & accuracy \\
\hline
MAX7310 & 80\%\\
RTL8139  & 87\%\\
EEPro100  & 78\%\\
E1000  & 91\%\\
\hline
\end{tabular*}
\label{table:accuracy}
\end{table}

% granularity
\subsection{Granularity}

The identifying method with fine granularity makes the relationship created by coDoc very accurate, 
80\% of the code pieces are marked inside the statement and expressions.
The same result happens for the document.
In the whole relationships, 
90\% of the document pieces are marked on cells in the tables.
The granulariy results are listed in Table \ref{table:granularity}.

\begin{table}[th]
\caption{Granularity Result}
\centering
\begin{tabular*}{0.6\textwidth}{@{\extracolsep{\fill}}rccc}
\hline
 & \# functions & statements & expressions \\
\hline
MAX7310 & 108 & 2 & 3\\
RTL8139  & 213 & 4 & 5\\
EEPro100  & 213 & 4 & 5\\
E1000  & 213 & 4 & 5\\
\hline
\end{tabular*}
\label{table:granularity}
\end{table}

%In our own experience, we found that the ability to see the code, 
%the documentation and the relationships on the same screen saves a lot of time,
%as we don't need to switch between different tools.

\subsection{Adapting to Evolving Code}

To evaluate how our approach adapt to evolving code, we recover the traceability links for the first version of all the four virtual device driver code.
We then check the number of valid traceability links left in the later versions. The result is shown in table \ref{table:robust}.
% traceability link lifetiem (versions)

\begin{table}[th]
\caption{Robustness}
\centering
\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}rccccccccc}
\hline
 & 1-2 & 2-3 & 3-4 & 4-5 & 5-6 & 6-7 & 7-8 & 8-9 & 9-10 \\
\hline
MAX7310 & 108 & 2 & 10 & 108 & 2 & 10 & 108 & 2 & 10\\
RTL8139  & 213 & 4 & 210 & 108 & 2 & 10 & 108 & 2 & 10\\
EEPro100  & 213 & 4 & 20 & 108 & 2 & 10 & 108 & 2 & 10\\
E1000  & 213 & 4 & 290 & 108 & 2 & 10 & 108 & 2 & 10\\
\hline
\end{tabular*}
\label{table:robust}
\end{table}

\subsection{Performance}

We test the performance of our algorithm to complete code selection and to verify traceability links. The result is shown in table \ref{table:performance}.

\begin{table}[th]
\caption{Performance}
\centering
\begin{tabular*}{0.6\textwidth}{@{\extracolsep{\fill}}rccc}
\hline
 & verification & completion\\
\hline
MAX7310 & 108 & 2 \\
RTL8139  & 213 & 4\\
EEPro100  & 213 & 4\\
E1000  & 213 & 4\\
\hline
\end{tabular*}
\label{table:performance}
\end{table}

\subsection{Summary}

In summary, our approach can meet the three requirements for the traceability links between device drivers and device specifications.
We believe this tool will lead to increased productivity.

### 2013-05-04 RPE/implementation.tex
class review version

\section{Implementation}
\label{sec:implementation}

This section presents the architecture of the implementation of our approach first. After that, we introduce the algorithm for validating the traceability links, and for code selection completion which helps the user to complete the code piece selection when part of a syntax element is selected.

\subsection{Architecture}

\begin{figure}
\begin{center}
\includegraphics[width=0.55\textwidth]{architecture}
\caption{coDoc Architecture and Features}
\label{fig:architecture}
\end{center}
\end{figure}

The architecture of our approach is shown in Figure \ref{fig:architecture}. 
There are three types of data here, 1) code, 2) spec, and 3) traceability links.
These data are consumed by three components: code manager (CM), spec manager (SM) and link manager (LM).
\begin{enumerate}
\item \textit{Link Manager.} Traceability link manager get the highlighted code piece from code manager and the highlighted spec piece from spec manager, and create traceability link for these two piece of information. It also reads the traceability link data, verify the validity of the link,
and highlights the code and document pieces that are related.
\item \textit{Code Manager.} Code manager reuses C/C++ Development Tool (CDT) editor from Elipse\footnote{\texttt{\url{http://www.eclipse.org}}} to parses the code, 
and highlights syntax elements. It can highlight the piece of code based on the information provided by the user or the link manager.
\item \textit{Spec Manager.} Spec manager renders the pdf content, can support select and highlight spec content, and communicate with the link manager.
\end{enumerate}

We implemented coDoc as an Elipse Rich Client Program (RCP), 
which can make our tool share the appearence in Eclipse that is familiar by many programmer.
Figure \ref{fig:platformview} is the screenshot of the tool.
The bottom is the UI for link manager, while the top left part and top right side are the UI for code manager and spec manager repectively.

% convert platformview.png platformview.eps
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{platformview}
\caption{coDoc Platform View}
\label{fig:platformview}
\end{center}
\end{figure}

\subsection{Link Validation}

\begin{algorithm}[!h]
\DontPrintSemicolon
\SetKwComment{tcp}{\hfill$\triangleright$ }{}
\SetCommentSty{emph}
$AST \leftarrow \textsc{Gen-AST}(code)$\;
$\langle RES, CONTENT_C \rangle \leftarrow \textsc{Get-Code-Content}(AST, link.code.path)$\;
\If{$RES = FAIL$} {
\Return $FAIL$\;
}
$RES \leftarrow \textsc{Compare-Content}(CONTENT_C, link.code.content)$\;
\If{$RES = FAIL$} {
\Return $FAIL$\;
}
$CONTENT_S \leftarrow \textsc{Get-Spec-Content}(spec, link.spec.path)$\;
$RES \leftarrow \textsc{Compare-Content}(CONTENT_S, link.spec.content)$\;
\If{$RES = FAIL$} {
\Return $FAIL$\;
}
\Return $SUCCESS$\;
\caption{$\textsc{Traceability-Link-Validation}(link)$}
\label{alg:validate}
\end{algorithm}

%\begin{figure}[h!]
%  \begin{center}
%    \begin{minipage}[b]{0.6\linewidth}
%      \centering
%      \renewcommand{\ttdefault}{pcr}
%      \begin{lstlisting}
%for each leaf node in syntax tree
%  for each node in anchor
%    node string compare
%\end{lstlisting}
%\end{minipage}
%\caption{Pseudocode for Link Validation}
%\label{fig:validate}
%\end{center}
%\end{figure}

When code evolves, we need to validate the existing traceability links.
Once an invalid traceability links is found, we should report it to let user correct it manually.
To check the validity of the traceability links, we record the content of the code piece and the spec piece when generating the links.
The content is used later to compare with the content to which the path points to when code changes.
The validation process basically go through each traceability link in the database, 
and check whether the link is valid or not.
Algorithm~\ref{alg:validate} presents the pseudo-code for check the validation of one single traceability link.
Line 1 - line 7 check the validity of the code piece part of the traceability link.
Line 1 generates the AST for the current code first.
Line 2 then invokes the function \textsc{Get-Code-Content} with the path of the code piece as input, identify the code piece in the new AST, and return the content of the code piece if the code piece is identified successfully.
If the path of the code piece cannot identify any code piece or can identify more than one code piece, the function \textsc{Get-Code-Content} reports failure.
Line 5 compare the the new content extracted from the new code with the recorded old content, and fail if the two contents do not match.
After finishing check the code piece part, line 8 - line 11 of the algorithm check the spec piece part in a similar flow.
If no failure happens, the algorithm return successfully at line 12.

\subsection{Code Selection Completion}

\begin{algorithm}[!h]
\DontPrintSemicolon
\SetKwComment{tcp}{\hfill$\triangleright$ }{}
\SetCommentSty{emph}
$AST \leftarrow \textsc{Gen-AST}(code)$\;
$SEQUENCE_{LEAF} \leftarrow \textsc{Gen-Leaf-Sequence}(AST)$\;
$POC_{AST} \leftarrow \textsc{To-AST-Based}(SEQUENCE_{LEAF}, selection_{org})$\;
$selection_{new} \leftarrow \textsc{To-Offset-Based}(POC_{AST})$\;
\Return $selection_{new}$\;
\caption{$\textsc{Complete-Code-Selection}(selection_{org})$}
\label{alg:completion}
\end{algorithm}

To improve the user experience of coDoc, we help users to select the code pieces when creating traceability links.
Our approach is based on the fact that it is usually meaningless to have part of the basic code elements as the code piece of the traceability links.
For example, we do not create a link between half of the variable and the spec piece.
We assume that every selected piece of code is composed of valid syntax elements.
Based on this assumption, we can help the user to automatically complete their selection when they only select part of the syntax element, like a variable, a constant, and etc. 
Algorithm \ref{alg:completion} outlines our approach.
This algorithm takes a code selection in offset based format,
and returns a new code selection in offset based format.
We choose offset based format because Eclipse use this format to highlight the code piece.
The algorithm basically includes two parts: (1) line 1 - line 3 force the input selection to be aligned by transforming it from offset based code piece to AST based code piece. (2) line 4 generates the required format by transforming AST based code piece back to offset based code piece.
As we discussed before, AST based representatioin is a sequence of AST leaf nodes in DFS visit order, which is the same order as in the source code.
The AST based code piece covers all the meaningful part of the original offset based code piece.
To transform the offset based code piece to AST based code piece, 
we get the sequence of leaf nodes of AST in line 1 and line 2,
and then match the leaf node sequence with the code piece to get the AST based representation.
The leaf node in the AST based representation is determined this way: if the leaf node contains any part of the selected code, then the leaf node is in the representation.
After we get the AST based representation,
we transform it back to offset based reprensentation, and return it.
This way, each time the user make a selection,
our engine adjust the selection to valid syntax boundary.

### 2013-05-04 RPE/introduction.tex
class review version

% maintenace is important, takes time. 
% reason: code size, spec size, relationship

% the lowest level HW/SW interface primitive is found in the form of SW programmable registers. 
% There are other vital aspects of the HW/SW interface, such as interrupts but these are not covered within the scope of this paper.
% the software interface of an IP block as an address-mapped bus (from processor) being mapped into registers that provide the configuration, control and status interface of the hardware logic.
\section{Introduction}
\label{sec:introduction}

The majority of software engineering work is devoted to maintaining legacy software systems other than developing new ones \cite{abran_maintenance_1991}.
It is estimated that up to 60\% of software maintenance time is spent on program comprehension \cite{lawrence_software_2006}.
Software developers often find it difficult to extract the knowledge about a software system,
because the knowledge is often implicitly expressed,
and distributed in a variety of software artifacts.
Examples of software artifacts include source code, design documents, application programming interface specifications, bug reports, etc.

To make the knowledge about a software system explicit,
reserachers have built various techniques to recover the semantic connections among software artifacts,
especially between documentation and source code \cite{antoniol_recoveringtraceability_2002} \cite{deLucia_incremental_2006} \cite{marcus_recovering_2003}.
These semantic connections are often called \textit{traceability links}. 
Effectively maintaining the traceability links can help improving the productivity of the developer and the quality of the software \cite{neumuller_case_2006}.

Unfortunately, these techniques are not ready to be applied to implementations and specifications of HW/SW interfaces,
even though these implementations are an important category of software that caused most of the system failures in both Windows and Linux operating systems \cite{swift_os_2003} \cite{chou_os_2001},
HW/SW interface forms the interaction point of hardware and software,
and defines the protocol for the hardware and software to communicate.
The implementation of HW/SW interfaces refers to hardware design, device drivers and virtual device prototypes, who implement the communication logic on both sides of the interfaces.
%The implements are designed for a variety of computer components, and form a large part of operating systems and virtual machines.
HW/SW interface specifications describe the HW/SW interfaces in natuaral lagnguage,
and guide the implementation of the interfaces.
HW/SW interface specifications play a crucial role in the comprehension and maintenance of the implementations of the interfaces.
The reason why existing traceability link recovering techniques do not work for HW/SW interfaces is that these traceability links need to be fine-grained,
which is not supported by the existing techniques.
HW/SW interfaces are mainly composed of software-programmable hardware registers mapped to the processor's address space.
The low-level abstraction of the software/hardware interface makes the traceability links fine-grained.
Traceability links between the specifications and implementations usually connect statements, which operate the registers, or expressions, which represent certain bits of registers, to the register bit descriptions in the specifications. 
However, previous tools usually maintain tracebility links between the classes or functions of the source code and sections or paragraphes of the documentation, which is more coarse-grained.

% Second, the evolution nature of software artifacts makes the situation even worse.
% No matter how the traceability links are created -- automatically or manually, these links are probably only valid for a certain version of the software.
% As software evolves during the development and maintenance process, software artifacts changes as well.
% These changes might invalidate the existing traceability links.
% For automatically recovered links, we can re-run the traceability recovery tool to reestablish them.
% However, this solution is computationally costly for interactive use during software development stage.
% For manually recovered links, we must reestablish these links manually again, which is arduous.
% This intimidate people from using these tools in their daily work.

% Second, previous traceability link recovering approaches use information retrieval techniques which have the assumption that all software artifacts are plain texts, and the key words in the texts can express the semantic information of the software artifacts precisely.
% These key words form the digital fingerprint of the software artifacts, and the digital fingerprints for the related software artifacts are highly similar, while the digital fingerprints for unrelated software artifacts are highly different.
% The assumption for IR techniques does not hold for device drivers and device specifications.
% People usually organize device specification by hardware modules and the registers inside the hardware modules.
% The semantic information is often encoded into binary numbers, and presented in tables.
% These modules and registers do not relate to the code in an explicit way.

We present a framework for managing traceability links between specifications and implementations of HW/SW interfaces. 
This framework supports fine-grained links between basic elements of specifications and constructs of implementation languages.
We design a data model to support the framework, and organize the data for the traceability links.
Our framework also supports automatic migration of links as implementations evolve.

We have implemented a prototype tool, namely coDoc, in support of this framework. 
With this tool, the developer can import and manage implementation source code and interface specifications, select a certain piece of implementation (POI) and a certain piece of specification (POS) of interest, create a traceability link connecting the seleted POI and POS, check out a different version of source code, review and verify the existing traceability links. 
We applied coDoc to three virtual device prototypes and their specifications, recovered traceability links, and verified the traceability links on other versions of the driver code.
Experimental results show that our framework fully supports the types of traceability links between the virtual devices and their specifications,
maintain traceability links with required granularity, 
and it accurately migrates valid links from version to version.
\todo{the data need to be updated}\hlc{It preserves 70\% of the existing traceability links when code evolves to a new version.}

This paper makes the following key contributions:
\begin{itemize}
\item Presented a framework for managing traceability links between specifications and implementations of HW/SW interfaces with accuracy, robustness and fine-granularity.
\item Developed coDoc, a tool implementing the approach.
\item Evaluated our approach with realistic examples.
\end{itemize}

The rest of the paper is organized as follows. 
Section \ref{sec:problem} examplifies and defines the problem that we address in this paper.
Section \ref{sec:approach} and section \ref{sec:implementation} illustrate the design and implementation details of our approach.
Section \ref{sec:evaluation} provides some preliminary evaluation results.
Section \ref{sec:related} reviews the related work.
We conclude our approach and discuss the future work in Section \ref{sec:conclusion}.

### 2013-05-04 RPE/paper.tex
class review version

--- 2013-03-14 RPE/paper.tex
@@
+% lucidchart: online chart drawing
+
 \documentclass[runningheads,a4paper]{llncs}
@@
 \setcounter{tocdepth}{3}
-\usepackage{graphicx}
+\usepackage[pdftex]{graphicx}
+\DeclareGraphicsExtensions{.pdf}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{float}
+\usepackage{url}
 
-\usepackage{url}
+\usepackage{llncsdoc}
+%\usepackage{makeidx}  % allows for indexgeneration
+%\usepackage{mathbbold}
+\usepackage{wrapfig}
+
+\usepackage{times}
+\usepackage{amsmath, amsfonts}
+\usepackage{latexsym, amssymb}
+\usepackage{setspace}
+\usepackage{longtable}
+\usepackage{grffile}
+%\usepackage{subfigure}
+%\usepackage{algorithm}
+%\usepackage{algorithmic}
+\usepackage{multirow}
+\usepackage{supertabular}
+\usepackage{listings}
+\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
+\usepackage{todonotes}
+%\usepackage{color}
+%\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
+\usepackage{soul}
+\newcommand{\hlc}[2][yellow]{{\sethlcolor{#1}\hl{#2}}}
+
 \urldef{\mailsa}\path|dejun@cs.pdx.edu|
@@
 
+%\tableofcontents
+
 \mainmatter  % start of an individual contribution
@@
 % first the title is needed
-\title{coDoc: A Tool for Managing Relationships between Code and Documentation}
+\title{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
+% a short form should be given in case it is too long for the running head
+\titlerunning{Traceability Links between Specifications and Implementations}
+\authorrunning{Dejun Qian}
 
-% a short form should be given in case it is too long for the running head
-\titlerunning{coDoc: Managing Relationships between Code and Documentation}
-
-% the name(s) of the author(s) follow(s) next
-%
-% NB: Chinese authors should write their first names(s) in front of
-% their surnames. This ensures that the names appear correctly in
-% the running heads and the author index.
-%
-\author{Dejun Qian}
-%
-\authorrunning{coDoc: Managing Relationships between Code and Documentation}
-% (feature abused for this document to repeat the title also on left hand pages)
-
-% the affiliations are given next; don't give your e-mail address
-% unless you accept that it will be published
-\institute{Computer Science Department,\\
-Portland State University,\\
-1900 SW 4th Avenue Portland, OR 97201, USA\\
-\mailsa\\
-\url{http://www.pdx.edu/computer-science/}}
-
-%
-% NB: a more complex sample for affiliations and the mapping to the
-% corresponding authors can be found in the file "llncs.dem"
-% (search for the string "\mainmatter" where a contribution starts).
-% "llncs.dem" accompanies the document class "llncs.cls".
-%
+\author{Dejun Qian\\dejun@cs.pdx.edu}
+\institute{Computer Science Department, Portland State University}
 
@@
 
-\begin{abstract}
-The reusing of either software or hardware components is an important way to build large systems.
-Documentation plays a critical role in the process of reusing,
-as it describes how the components can be reused.
-When writing and testing software, 
-we need the documentation in hand.
-This is particularly true for software that is documentation-intensive, 
-such as device drivers and virtual device modules.
-This paper presents coDoc, 
-an integrated development environment for managing relationships between code and documentation.
-We describe the architecture and features of coDoc,
-and discuss several design decisions that we faced in developing coDoc and the trade-offs involved in making these decisions.
-We report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents by coDoc.
-\keywords{Software Engineering, Data Model}
-\end{abstract}
+%\lstset{frame=trBL,language=C,columns=fullflexible,
+%  numbers=left,framexleftmargin=6mm,xleftmargin=7mm,framexrightmargin=5mm,
+%  basicstyle=\footnotesize\ttfamily, commentstyle=\rmfamily\itshape}
+\lstset{frame=trbl,language=C,columns=fullflexible,
+  numbers=left,framexleftmargin=6mm,xleftmargin=7mm,framexrightmargin=5mm,
+  basicstyle=\footnotesize\ttfamily, commentstyle=\rmfamily\itshape}
 
-\section{Introduction}
-\label{sec:introduction}
-Documentation plays an important role in software engineering.
-%from requirement analysis to architecture design,
-%from coding to software testing,
-%from software debugging to software maintenance.
-Software that relates closely to hardware is extremely documentation intensive. % explain why
-Examples of such software include bootloaders, 
-Hardware Abstraction Layers (HAL) in Operating Systems (OS),
-and virtual device modules for virtual machines.
-Such software must follow the hardware documentation to operate correctly.
-A typical embedded CPU might have documentation consisting of thousands of pages.
-A computer system usually consists of more than ten hardware modules.
-Effectively maintaining the relationships between the code and the documentation is important for developing and verifying hardware-related software.
+\input{abstract}
 
-To our knowledge, there are no tools to address this problem.
-Researchers have done a lot of work to handle the relationships between Application Programming Interface (API) documents and their client code \cite{Pandita_inferring_2012} \cite{wei_inferring_2011}.
-However, the approaches developed in the work do not consider the relationships between hardware-related code and its documentation.
-API documents are usually well indexed by the functions or the classes that they define.
-When we are interested in a piece of code in the client software
-we can easily find the related API documents by the names of the functions that the piece of code calls.
-% The relationships between the client codes and the API documents can be easily constructed by using the function names as the keywords.
-However, the code relating to hardware and its documentation usually relate in different ways.
-% the hardware docuemnts are not orgnized by functions or classes, which are the basic elements of code, but instead by hardware modules.
-People usually organize hardware documentation by hardware modules and the registers inside the hardware modules.
-These modules and registers do not relate to the code in an explicit way.
-Hardware documents include text, tables and diagrams, while API documents usually include text only.
+% introduction - give the problem (create and manage links)
+\input{introduction}
 
-% These differences make the constructing of the relationships between the hardware related codes and their documents really challenging.
-A simple workaround is to include references to the positions of the related documentation as comments in the code.
-However, this can only handle simple situations.
-If there are thousands of such comments cluttered in the code,
-it will be very hard to manage them.
+% problem and definition - example to illustrate the problem (further illustrate the problem)
+\input{problem}
 
-This paper presents coDoc, a tool to create, maintain, and display relationships between code and documentation.
-% The initial version\footnote{\texttt{\url{git@github.com:derekqian/coDoc.git}}} has been released.
-The key features of coDoc include 
-the ability to display both code and documents, 
-the ability to write and edit code, 
-code-piece selection based on syntax tree of the code,
-%stable code selections regarding to the changes of unrelated codes;
-creation of relationships between codes and documents,
-and relationships management and display.
-Using coDoc, we have created relationships between two virtual NIC devices in QEMU and the related documents.
-These two devices are DIO \cite{dio} and E100 \cite{e100}.
+% the design and data model (a general framework to solve the problem) - key as a requirement
+\input{approach}
 
-The main contributions of this paper are as follows.
-\begin{itemize}
-\item Design a framework to display and manage codes, documents and relationships.
-\item Design coDoc which implement the framework.
-\item Maintain integrity of the relationships when the code evolves.
-\item Design a standard format to represent the code piece.
-\item Design a standard format to represent the document piece.
-\item Design a data model for relationships between code and documentation.
-\end{itemize}
+% handle some specific difficulties - our solution using ast tree
+\input{implementation}
 
-The rest of the paper is organized as follows. 
-Section \ref{sec:arch} provides the overall architecture and key features of coDoc.
-%Section \ref{sec:decision} gives the design decisions of coDoc and the trade-offs of these decisions.
-Section \ref{sec:evaluation} summarizes our experiences of creating and maitaining the relationships for two virtual devices.
-Section \ref{sec:related} presents the related work.
-Section \ref{sec:conclusion} concludes our work and gives our future research plan.
+%evaluation - three vd with ten version
+\input{evaluation}
 
-\section{Architecture and Features of coDoc}
-\label{sec:arch}
+% related work
+\input{related}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.55\textwidth]{architecture}
-\caption{coDoc Architecture and Features}
-\label{fig:architecture}
-\end{center}
-\end{figure}
-
-\subsection{Architecture of coDoc}
-The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
-It contains a code manager (CM), a documentation manager (DM) and a relationship manager (RM).
-There are three types of data here, 1) code, 2) documentation, and 3) relationships.
-We handle only C/C++ code at this time, 
-as most system code is written in C/C++.
-CM reuses C/C++ Development Tool (CDT) editor from Elipse\footnote{\texttt{\url{http://www.eclipse.org}}} to handle C/C++ code.
-The CDT editor reads and parses the code, 
-and highlights syntax elements.
-We use poppler to read the PDF file and render the PDF pages as images.
-As poppler is developed in C++ and Eclipse Rich Client Program (RCP) is in Java,
-we need an adaptor to bridge between C++ and Java,
-for which we use Java Native Interface (JNI).
-We implement this adaptor in PDF Editor, 
-and uses it to get the PDF page from poppler and display the page.
-RM reads the relationship data,
-and highlights the code and document pieces that are related.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{datamodel}
-\caption{Data Model for coDoc}
-\label{fig:datamodel}
-\end{center}
-\end{figure}
-
-\subsection{Data Model}
-The data model is shown in Figure \ref{fig:datamodel}.
-We have four entities here: category, relationship, code piece and documentation piece.
-Code piece and documentation piece represent the selected code and documentation respectively.
-We represent the relationships between code and documentation as entities,
-as we want to classify the relationships.
-The relationships are classified by their functionality in our approach.
-Category is used to maintain the classification information of the relationships.
-To represent a relationship, 
-we need to define the strategy to represent the code piece and documentation piece.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{ast1}
-\caption{Original code and its AST}
-\label{fig:ast1}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.85\textwidth]{ast2}
-\caption{Evolved code and its AST}
-\label{fig:ast2}
-\end{center}
-\end{figure}
-
-\subsection{Representing Code Segments}
-Code is always evolving during its lifetime.
-We want the relationships created for one version of code keep working for other versions.
-To achieve this goal, we need a robust strategy to represent the code pieces.
-Our first method represents the code piece by the offset of the selected code from the beginning of the code file and the length of the selected code.
-This method is straight forward and is easy to understand and implement.
-However, this method is not robust,
-as the change of the code file will change the offset of the selected code.
-The left sides of Figure \ref{fig:ast1} and Figure \ref{fig:ast2} give the code before and after it evloves.
-The highlighted code piece is what we want to select.
-Unfortunitely, the offset of the select code increases after we add some code,
-as shown in this example.
-To achieve robustness, we need to find some properties of the code that are relatively stable when code evolves.
-These properties can serve as keys to represent the code piece.
-An intuitive thought is to use the semantic information,
-that is the intrinsic meaning of the code.
-However, we can't find a formal way of defining this information.
-We use syntax information to form the main element of our code piece identifier.
-The code can be parsed and represented by a syntax tree.
-A change of the code in one branch will usually not affect the code in other branches.
-Representing code segments based on the position in the syntax tree should be robust.
-The right sides of Figure \ref{fig:ast1} and Figure \ref{fig:ast2} are the Abstract Syntax Trees (AST) for the code before and after it evolves.
-In the ASTs, the highlighted nodes relate to the code piece we selected.
-Through the two ASTs are different, 
-the highlighted nodes can be represented by the same path from the roots of these two ASTs.
-%To make the method more robust, % prof lost here
-%we can introduce the information in the first method as the secondary key.
-%When the syntax identifier fails to locate the code piece,
-%we can use the offset information to assist the decision.
-%We also include in the identifier the content of the code piece as an integrity check.
-%The structure used to achieve this goal is shown bellow.
-%\begin{Verbatim}[frame=single]
-%class CodeSelection {
-%  private String syntaxcodepath;
-%  private String selcodepath;
-%  private String syntaxcodetext;
-%  private String selcodetext;
-%}
-%\end{Verbatim}
-
-%\section{Methodology and Design Decisions}
-%\label{sec:decision}
-%\subsection{Embedded vs Seperate for PDF Reader}
-%The tool should display both codes and documents at the same time.
-%We can implement the code viewer and the PDF viewer in seperate process,
-%and use inter process communication (IPC) techniques to communicate.
-%The advantage of this method is that each process has its own window,
-%can occupy the whole screen,
-%and display more content which reduces the need to scroll the window horizontally.
-%When the user uses a computer with two monitors,
-%the tool implementing this method is an extremely good choice,
-%as the user can choose to display the code and the document on seperate moniters.
-%However, this implementation is heavy, % ?
-%and has performance issues.
-%When using the tool, 
-%the user may need to launch the PDF reader,
-%which is slow.
-%Our earlest implementation uses this method,
-%and encountered synchronization problems from the IPC communication.
-%In coDoc, we choose to implement the code viewer and the PDF viewer in the same process.
-%%The Eclipse framework even makes the whole system single thread.
-%This way, all the commucation is internal to the same process,
-%No IPC communication is needed,
-%which is more efficient and makes the tool more responsive.
-%With the new method, we can smoothly operate the tool without any uncomfortable feeling.
-%The advantages of the first method become the disadvantage of the new method,
-%as the code viwer and the document viwer must share the whole screen now.
-%However, with a efficient and user-friendly method of assigning screen area,
-%we can make the user feel less uncomfortable when viewing the content.
-%Also, most programmer now not only are using two moniters, % prove
-%but also the moniters they are using are larger and larger.
-%Using a larger moniter with high definition will make this disadvantage nothing. % need revisement
-%And even better, in this situation, this method will overcome the first method,
-%as moving the eyes between two big moniter is energy consuming.
-
-\section{Evaluation}
-\label{sec:evaluation}
-%We adopt poppler, a open-source PDF render, to render PDF content in coDoc.
-%This PDF render is written in C++, 
-%and is widely used in Linux systems.
-%It uses Cairo and GTK to draw the rendered content.
-
-\textbf{Effectiveness.} We evaluated coDoc by setting up relationships between the code for two virtual devices and their documentation.
-The number of relationships created and the time used to created these relationships are listed in Table \ref{table:evaluate}.
-
-\begin{table}[th]
-\caption{Evaluate Result}
-\centering
-\begin{tabular}{rcc}
-\hline
-Code & \# of Relationships & time(hr) \\
-\hline
-dio & 108 & 2 \\
-e100  & 213 & 4\\
-\hline
-\end{tabular}
-\label{table:evaluate}
-\end{table}
-
-The identifying method with fine granularity makes the relationship created by coDoc very accurate, 
-80\% of the code pieces are marked inside the statement.
-This result is hard for comment-based method to achieve.
-The same result happens for the document.
-In the whole relationships, 
-90\% of the document pieces are marked on cells in the tables.
-The comments in the PDF file will be too crowd to be useful,
-as it will affect the normal reading of the document.
-Our approach can also make the development efficient,
-as we don't need the developer to change either the code or the document while only relationship is created.
-This makes the code and document neat and easily to read and understand.
-
-\noindent \textbf{Usability.} We implemented coDoc as an Elipse Rich Client Program (RCP), 
-which can make our tool share the appearence in Eclipse that is familiar by many programmer.
-Figure \ref{fig:platformview} is the screenshot of the tool.
-Three persons with no prior exprience with coDoc have successfully use this tool to create the relationships between their codes and documentation.
-They didn't find any difficulties when using this tool.
-All the feedbacks has been positive regarding the use of the tool.
-%Now they can easily create their relationships by selecting the code and document piece using mouse, input the comment using keyboard.
-%They can also manage the relationships by sorting by attributes, search certain relationships by keywords.
-%They also find the feature that allow them to categorize the relationships helpful.
-%This feature makes the relationships neater when the number of relationships is large.
-
-In our own experience, we found that the ability to see the code, 
-the documentation and the relationships on the same screen saves a lot of time,
-as we don't need to switch between different tools.
-%The visualized interface also saved us time to learn the detailed syntax about the identifier formats,
-%and to write the identifier manually.
-We believe this tool will lead to increased productivity.
-
-% convert platformview.png platformview.eps
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{platformview}
-\caption{coDoc Platform View}
-\label{fig:platformview}
-\end{center}
-\end{figure}
-
-\section{Related Work}
-\label{sec:related}
-Current tools can manage codes. 
-These kinds of tools include revision control software like git, svn \cite{git} \cite{svn}. 
-Revision control tools can give the evolving history of the software.
-These tools usually adopt text comparison tools to figure out the differences between different versions of the software.
-The comparation tools can easily give the result about the matching points and mismatching points in the codes,
-which means they can manage the relationships between different versions of codes.
-However, these tools are not designed to manage documents.
-Though some people also use them to manage documents,
-they only use it as a persistent data warehouse.
-They can not take the advantages of the comparison tools, 
-as these tool usually can only deal with text file.
-People are using code comments to record the related document piece.
-However, no consistent format exists,
-which makes these information not managable,
-especially when these comments are made by many different developers.
-
-Full text indexing system is developed to processing documents \cite{lucene}.
-However, they can only relate keywords to certain documents.
-They do not deal with both codes and documents. 
-Like full text indexing system,
-search engines also work with documents in similar way.
-Most of the documents that are handled by search engines are web pages.
-Many PDF readers can support highlighting and commenting.
-With these features, we can relate a document piece to a code piece.
-However, these links created are not stable,
-and PDF readers can not check the integrity of these information.
-
-Generally speaking, these are tools can either do code management or do document management.
-However, they are not designed to do both,
-and managing the relationships between codes and documents is definitely a mission impossible task for them.
-
-% Based on what you have so far, what can you conclude?  What cool ideas did you think up but not have time to implement so far?
-\section{Conclusions and Future Work}
-\label{sec:conclusion}
-We have implemented coDoc, 
-a tool for managing the relationships between the hardware related programs and their documentation.
-The main contribution of this paper is the method to identify the code segment.
-Our experiences of using coDoc to manage the code for two virtual devices and their documentation shows the tool is robust and efficent,
-and is helpful when developing and maitaining the virtual devices.
-The relationships remain stable even when the code changes.
-
-There are still opportunities to improve coDoc.
-\begin{enumerate}
-\item Combine it with revision control tools to provide a more user-friendly tool suit for developing and maitaining the codes while managing the documents at the same time.
-\item Design more robust method to identify the document pieces in the PDF documents to make the tool invariant to the change of the documents.
-\item Use machine learning (use the data created as seed to train the model) to construct and check the relationships between hardware related codes and their documents.
-\end{enumerate}
+% conclusion and future work
+\input{conclusion}
 

### 2013-05-04 RPE/problem.tex
class review version

% emphasize the special characteristic of hardware-related software
\section{Problem Statement}
\label{sec:problem}

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{c}
\begin{minipage}[b]{\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{code1}
\end{minipage}\\
(a) The Old Version\\
\\
\begin{minipage}[b]{\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{code2}
\end{minipage}\\
(b) The Newer Version
\end{tabular}
  \caption{Two Versions of a Virtual Devices Written in C. This piece of code is extracted from MAX7310 virtual device in QEMU virtual machine. This code defines a function to reset the registers. However, we do not know why they are resetted to the values labeled 1, 2 and 3. To know the answer, we need to refer to the specification.}
\label{fig:code}
\end{center}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{spec}
  \caption{Specification Example. This is part of MAX7310 specification. It includes three tables, which define the default values for three registers.}
  \label{fig:spec}
\end{figure}

The interfaces between software and hardware are composed of registers exposed by hardware devices and accessible by software. The implementation of the interfaces should conform to the specification in order to function correctly. Suppose we have to maintain and understand this implementation, we need to establish relationships between the implementation and the specification. Fig.~\ref{fig:code}(a) presents part of code extracted from a virtual device prototype for MAX7310 in QEMU. A virtual device prototype is a software implementation emulating a hardware device. MAX7310 is a 8-bit I/O port expander. QEMU (Quick EMUlator)\footnote{\texttt{\url{http://www.qemu.org}}} is virtual machine used widely in industry to assist hardware related software development. The source code for this implementation is written in C language. From the name of the function, we can guess the function shown is trying to reset the device to its initial state. However, we can not figure out what the values in the right sides of the assignment statements mean only by reading the code here. Fig.~\ref{fig:spec} includes the information extracted from the specification of MAX7310. In this figure, we can see three tables for three registers: polarity register, direction register and status register. These tables present the bit arrangement and the default value for each register. By looking at this specification, now we can see that the values used in the code are defined in the specification. The code uses the hex format, and the specification use binary format. The piece of code and the piece of specification labeled with the same number are related, which means the piece of specification explains the piece of code with the same label.

% in the directory including max7310.c: git log --follow --all -p max7310.c > a.txt
Code evolves all the time in its lifecycle. By checking the QEMU repository, we can find that the first version of the code in Fig~\ref{fig:code} was created on May 23, 2007, and the last change is on May 1, 2013. This code has changed 21 times till now, and it still keeps changing. 
Fig.~\ref{fig:code}(b) shows an example of a new version of the code in Fig.~\ref{fig:code}(a). Line 13, 25 and 29 of the code in Fig.~\ref{fig:code}(a) has changed to the line 12, 24 and 28 in Fig.~\ref{fig:code}(b).

Compared to code, specification is relatively stable. The specification in Fig~\ref{fig:spec} only has three versions, and the last change happened in 2005. The specification remains unchanged since the code was created.

This example is simple, but reveals three basic requirements for the management of traceability links between specification and implementations as follows.

\textbf{Requirement 1:} Traciability links should be able to uniquely refer to and accurately locate the relevant pieces of code in the source file and the piece of specification in the specification file. As in the example, there should be a way to locate the code pieces and specification pieces surrounded by the boxes labeled by 1, 2 and 3.

\textbf{Requirement 2:} Traceability links should be able to provide referrence at statement level or expression level for source code and at sentence level or word level for specification. As in this example, the code pieces and specification pieces surrounded by the boxes labeled by 1, 2 and 3 are all on this level.

\textbf{Requirement 3:} Traceability links should be immune from the evolusion of unrelated code. We should grarantee that the identifier created for the old version of code works for the new version of code if the code piece refered by the identifier does not change.

### 2013-05-04 RPE/related.tex
class review version

\section{Related Work}
\label{sec:related}
Researchers have done much work to build automatic tools for traceability link recovery (TLR) from software systems \cite{antoniol_recoveringtraceability_2002} \cite{deLucia_incremental_2006} \cite{marcus_recovering_2003}.
TLR technology scans the software artifacts including source code and documentation and recovers the semantic connections by information retrieval (IR) methods.
\todo{improve}This technology has shown to be advanced and successful \cite{spanoudakis_software_2004}.
However, IR techniques are not good enough to substitute the human decision-maker in the linking process.
Hayes et al. suggests these IR techniques should only be used to generate an appropriate list of candidate links evaluated by software analyst \cite{hayes_advancing_2006}.
The recall of these techniques is not as good as to be pratical, a significant part of traceability links need to be recovered manually.
Trace acquisition remains human-intensive and with high initial cost as reported in case studies on industrial processes and traceability experiences \cite{lindvall_practical_1996} \cite{ramesh_implementing_1995} \cite{asuncion_an_2007} \cite{gotel_extended_1997} \cite{neumuller_case_2006}.

The evolution nature of software artifacts makes the situation even worse.
No matter how the traceability links are created -- automatically or manually,
these links are probably only valid for a certain version of the software.
As software evolves during the development and maintenance process, software artifacts changes as well.
These changes might invalidate the existing traceability links.
For automatically recovered links, we can re-run the TLR tool to reestablish them.
However, this solution is computationally costly for interactive use during software development stage.
For manually recovered links, we must reestablish these links manually again, which is arduous.
This intimidate people from using TLR tools in their daily work.
Some work has been done to address this problem by improving exisiting IR based methods \cite{jiang_incremental_2008}.
However, these work didn't consider the situations specific to hardware related software.

%An intuitive thought is to use the semantic information,
%that is the intrinsic meaning of the code.
%However, we can't find a formal way of defining this information.

### 2013-05-05 RPE/abstract.tex
revise

@@
 \begin{abstract}
-Traceability links between specifications and implementations of hardware/software (HW/SW) interfaces play a crucial role in improving the quality of computer systems.
-On one hand, HW/SW interfaces are often quite detailed, on low abstraction levels, 
-thus demanding fine-grained traceability links.
-On the other hand, HW/SW interface specifications are typically stable while their hardware and software implementations are constantly evolving even after their releases, which requires robust traceability links.
-In this paper, we present a framework for managing traceability links between specifications and implementations of HW/SW interfaces. 
+Traceability links between specification and implementation are crucial to improving the quality of hardware/software (HW/SW) interfaces.
+HW/SW interface implementation is often quite detailed and on low abstraction levels, thus demanding fine-grained traceability links.
+HW/SW interface specification is typically stable while its hardware and software implementations are constantly evolving even after 
+their releases, which requires robust traceability links.
+In this paper, we present a framework for managing traceability links between specification and implementation of HW/SW interfaces.
 This framework supports fine-grained traceability links between basic elements of specifications and constructs of implementation languages.
-It also supports automatic migration of links as implementations evolve. 
-We have implemented a prototype tool, namely coDoc, in support of this framework. 
-We have applied coDoc to ten versions of three virtual devices in the QEMU virtual machine.
+It supports automatic migration of links as implementation evolves.
+We have developed a prototype tool, namely coDoc, in support of this framework.
+We have applied coDoc to ten versions of three virtual devices from the QEMU virtual machine.
 Experimental results show that our framework fully supports the types of traceability links between the virtual devices and their specifications,
-and it accurately migrates valid links from version to version.
+and accurately migrates valid links from version to version.
 %\keywords{Software Engineering, Data Model}

### 2013-05-05 RPE/approach.tex
revise

@@
-\section{Our Approach}
+\section{Approach to Managing HW/SW Interface Traceability Links}
 \label{sec:approach}
 
-We first present an overview of our approach.
-Then, we propose the underlying data model.
-The data model introduces the requirement \hlc{of the} techniques to represent the POIs and the POSes.
-We illustrate how our approach address this problem at last.
-
-\subsection{Overview}
-\todo{this section need rewriting. focus on data.}
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.55\textwidth]{framework}
-\caption{Framework of Our Approach.}
-\label{fig:framework}
-\end{center}
-\end{figure}
-
-As shown in Fig.~\ref{fig:framework}, the framework of our approach consists three components: database, control logic, and user interface.
+%In this section, we first present an overview of our framework.
+We then propose the underlying data model.
+After that, we focus on how we design the anchors in the code and specification, which are utilized in the data model to capture traceability links.
+%
+%\subsection{Overview}
+%\todo{this section need rewriting. focus on data.}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.55\textwidth]{framework}
+%\caption{Framework of Our Approach.}
+%\label{fig:framework}
+%\end{center}
+%\end{figure}
+%
+%As shown in Figure~\ref{fig:framework}, the framework of our approach consists three components: database, control logic, and user interface.
 The structure of the traceability link data in the database is defined by the data model.
@@
 
+We have developed a framework for managing traceability links between specification and implementation of HW/SW interfaces.
+This framework supports fine-grained links between basic elements of specifications and constructs of implementation languages 
+and automatic migration of valid traceability links as implementation evolves. Central to this framework is a simple, but 
+effective data model for organizing the data of the traceability links. In support of this data model, we have identified 
+anchors in implementation and specification, which identify the pieces of specification and code involved in traceability 
+links. The data model with these anchors fulfills the three requirements for HW/SW interface traceability links identified above.
+In this section, we first introduce the data model and then discuss the design of anchors in code and spec.
+
+\subsection{Data Model}
+The data model is central to support fine-grained links between basic elements of specifications and constructs of implementation languages and automatic migration of links as implementations evolve.
+We introduce the data model of our approach in this section.
+
 \begin{figure}
@@
 \includegraphics[width=0.85\textwidth]{datamodel}
-\caption{Data Model. Entity-Relation Model is used. Rectangles represent entity sets. Ovals represent attributes. Diamonds represent relationships.}
+\caption{Data Model. Entity-Relation Model is used: rectangles represent entity sets; ovals represent attributes; diamonds represent relationships.}
 \label{fig:datamodel}
@@
 
-\subsection{Data Model}
-The data model is the key to support fine-grained links between basic elements of specifications and semantic constructs of implementation languages and automatic migration of links as implementations evolve.
-We introduce the data model of our approach in this section.
-
 The data model describes the data objects being handled in the framework, their attributes, and the relationships between these data objects.
-Fig.~\ref{fig:datamodel} presents the data model of our design.
-Entiry-relationship model is used.
-Rectangles represent entiry sets.
+Figure~\ref{fig:datamodel} presents the data model of our design.
+Entity-relationship model is used.
+Rectangles represent entity sets.
 Ovals represent attributes.
@@
 We have four entity sets in our design: code file mark, spec file mark, code piece anchor and specification piece anchor.
-Code piece anchor and specification piece anchor represent the selected code and specification piece respectively.
+Code piece anchor and specification piece anchor represent the selected code and specification pieces respectively.
 Both code file mark and spec file mark entities have attributes id and path:
@@
 Special attention should be paid to four attributes: path for code file, path for spec file, path for code piece anchor and path for spec piece anchor.
-\todo{explain}\hlc{These four attributes are foreign keys used to refer to data that do not exist in database.}
+These four attributes are foreign keys used to refer to data that is not in the database.
 As foreign keys, these attributes should be able to uniquely identify the entities they refer to.
 The path provided by the file system is a solution to the path for code files and spec files, as we can easily identify both code files and spec files by these pathes.
-The pathes for anchors are challenging, little work has been done to address this problem.
+The design of the anchors in the code and spec files is key to fine-granularity and link migration. We discuss it next.
+%The pathes for anchors are challenging, little work has been done to address this problem.
 
@@
 
-\subsection{Anchor Design}
-
-Anchors includes specification anchor and implementation anchor.
+%\subsection{Anchor Design}
+%
+%Anchors include specification anchor and implementation anchor.
 The three basic requirements for traceability links are the constraints for the design.
-We present how our approach make these requirements fulfilled.
+We present how our approach fulfilled these requirements.
 Specification anchor design is addressed first, then we present the implementation anchor design.
 
-\subsubsection{Spec Anchor}
+\subsection{Design of Spec Anchor}
 
@@
 Basically, the coordinate for specification piece is denoted by two points -- the point representing the beginnings of the selection and the point representing the end of the selection.
-Each point is denoted by a vector $<$page, x-coord, y-coord$>$, where page is the page number the point located, x-coord and y-coord are the horizontal and vertical coordinate respectively.
+Each point is denoted by a vector $<$page, x-coord, y-coord$>$, where page is the page number the point located, x-coord and y-coord are the horizontal and vertical coordinates respectively.
 
 The method is accurate as each point is uniquely represented by the coordinate.
-This method is also fine-grained, because this method could represent each word, sentence or evan arbitrary size of POS.
+This method is also fine-grained, because this method could represent each word, sentence or even arbitrary size of POS.
 The method is not robust as it uses the absolute coordinate as the basic element of the anchor.
-However, specifications are relatively stable, which makes this approach work most of the time.
+However, specifications are relatively stable, which makes this approach acceptable.
 
-\subsubsection{Offset-Based Anchor}
+\subsection{Design of Code Anchor}
+
+In designing code anchors, we first experimented with offset-based anchors and syntax-tree-based anchors.
+We then designed hybrid anchors that integrate the above two types of anchors and address their respective limitations.
+
+\subsubsection{Offset-Based Anchor.}
 
 Similar to specification anchor,
-absolute coordinates also fit the situation of implementation anchor.
-Basically, implementation code is just a string of ASCII charactors. 
+absolute coordinates can also be used as implementation anchors.
+Basically, implementation code is just a string of ASCII characters.
 Each piece of code is a substring of this string.
@@
 The pair (offset, length) is called Offset-Based Anchor.
-Fig.~\ref{fig:code}(a) illustrate this technique.
-The parenthesized number in front of each line represent the offset of the first charactor of that line.
+Figure~\ref{fig:code}(a) illustrate this technique.
+The parenthesized number in front of each line represent the offset of the first character of that line.
 Using this approach, we can get the Offset-Based Anchors for the three code pieces labeled 1, 2 and 3 as (590, 4), (614, 4) and (635, 4) respectively.
@@
 The disadvantage of this technique is that these anchors fail after the code evolves.
-Fig.~\ref{fig:code}(b) is the code after the code in Fig.~\ref{fig:code}(a) evolves.
+Figure~\ref{fig:code}(b) is the code after the code in Figure~\ref{fig:code}(a) evolves.
 We can see the anchors we get above do not point to the previous pieces of code anymore.
-The reason is that this approach is context sensitive.
-By saying context sensitive, we mean it depends on its context.
-In this approach, the anchor depends on the number of charactors preceeding the piece of code.
-
-One way to overcome this disadvantage is to get the knowledge of change to keep the links valid.
-However, this information is not always available.
+The reason is that such anchor depends on the number of characters preceding the piece of code.
+One way to overcome this limitation is to use the code information to update these links.
+However, such information is not always available.
 Most of the time, code is changed by other people.
-We can only get the changed result without how the change is made.
+We can only get the changed code without knowing how the change was made, without fully comprehending the code.
 
@@
 \end{minipage}\\
-(a) AST for the Code in Fig.~\ref{fig:code}(a)\\
+(a) AST for the Code in Figure~\ref{fig:code}(a)\\
 \\
@@
 \end{minipage}\\
-(b) AST for the Code in Fig.~\ref{fig:code}(b)\\
+(b) AST for the Code in Figure~\ref{fig:code}(b)\\
 \\
@@
 \end{tabular}
-\caption{The AST for the implementation code in Fig.~\ref{fig:code}.}
+\caption{The AST for the implementation code in Figure~\ref{fig:code}.}
 \label{fig:ast}
@@
 % evaluate on unique
-\subsubsection{Syntax Tree Based Anchor}
+\subsubsection{Syntax Tree Based Anchor.}
 To make the traceability links created for one version of code work for other versions,
@@
 AST usually has fewer nodes than parse tree, and takes less time to traverse.
-Each node in AST tree represents a syntax unit of the grammer,
-a parent of a node represent a bigger grammer unit that includes the grammer unit represented by the child node.
-The nodes are labeled by the type of the grammer unit.
-For each leaf node, we also include the value, which is the code this node represents, in the label.
+Each node in AST tree represents a syntax unit of the grammar,
+a parent of a node represent a bigger grammar unit that includes the grammar unit represented by the child node.
+The nodes are labeled by the type of the grammar unit.
+Each leaf node includes the code this node represents in its label.
 For some of the inner nodes that have a name, we also include the name in their labels.
-For example, a inner node that represents a function will be labeled with the grammer unit type and the name of the function.
+For example, an inner node that represents a function will be labeled with the grammar unit type and the name of the function.
 A change of the code in one branch of AST usually does not affect the structure in other branches.
 Representing code pieces based on the structure in the syntax tree is robust.
-Fig.~\ref{fig:ast}(a) and Fig.~\ref{fig:ast}(b) are the Abstract Syntax Trees (AST) for the code in Fig.~\ref{fig:code}(a) and Fig.~\ref{fig:code}(b).
+Figure~\ref{fig:ast}(a) and Figure~\ref{fig:ast}(b) are the Abstract Syntax Trees (AST) for the code in Figure~\ref{fig:code}(a) and Figure~\ref{fig:code}(b).
 Dot lines represent branches not shown.
-Fig.~\ref{fig:ast}(a) shows two subtrees of the root.
-The left subtree represents line 13 - line 25 of Fig.~\ref{fig:code}(a), which defines the structure max7310\_s.
-The right subtree represent line 27 - line 35 of Fig.~\ref{fig:code}(a), which defines the function max7310\_reset.
-Similarly, the left subtree of the AST in Fig.~\ref{fig:ast}(b) represent line 12 - line 24 in Fig.~\ref{fig:code}(b), and the right subtree represents line 26 - line 34.
-From the AST shown in Fig.~\ref{fig:ast}(a) and fig.~\ref{fig:ast}(b), we can see that the left tree has changed as the code for structure definition changed.
+Figure~\ref{fig:ast}(a) shows two subtrees of the root.
+The left subtree represents line 13 - line 25 of Figure~\ref{fig:code}(a), which defines the structure max7310\_s.
+The right subtree represent line 27 - line 35 of Figure~\ref{fig:code}(a), which defines the function max7310\_reset.
+Similarly, the left subtree of the AST in Figure~\ref{fig:ast}(b) represent line 12 - line 24 in Figure~\ref{fig:code}(b), and the right subtree represents line 26 - line 34.
+From the AST shown in Figure~\ref{fig:ast}(a) and Figure~\ref{fig:ast}(b), we can see that the left tree has changed as the code for structure definition changed.
 However, the structure of the right subtree remain the same, unaffected by the change of the left subtree.
@@
 Each leaf node is represented by the path from the leaf node to the root of the AST.
-For example, line 31 in Fig.~\ref{fig:code}(a) is represented by the highlighted three leaf nodes in Fig.~\ref{fig:ast}(a).
+For example, line 31 in Figure~\ref{fig:code}(a) is represented by the highlighted three leaf nodes in Figure~\ref{fig:ast}(a).
 The leaf nodes are in the same order as they are visited by depth-first search of the AST.
-For this example, the closest common parent node for these three leaf nodes also represents the same piece of code, and thes representation is even simpler.
+For this example, the closest common parent node for these three leaf nodes also represents the same piece of code, and this representation is even simpler.
 We avoid using this representation for two reasons: First, this representation contains less information; Second, this representation is sensitive to formatting and style convention.
@@
 
-Using this approach, let's consider the pieces of code label by 1, 2 and 3 in fig.~\ref{fig:code} again.
-The identifier for these code pieces in AST are shown in fig.~\ref{fig:ast} labeled with the same number.
-Through the two ASTs are different, 
-the highlighted nodes can be represented by the same path from the roots of these two ASTs.
-As a result, we can use this method to identify the piece of code, and the change of the unrelated code does not invalidate the identifier.
+Using this approach, consider the pieces of code labeled by 1, 2 and 3 in Figure~\ref{fig:code} again.
+The identifiers for these code pieces in AST are shown in Figure~\ref{fig:ast} labeled with the same numbers.
+Though the two ASTs are different,
+the highlighted nodes can be represented by the same paths from the roots in both ASTs.
+This method can identify the piece of code and the change of the unrelated code does not invalidate the identifier.
 
-This method is relatively stable.
-However, it may not uniquely identify a piece of code,
-which means one identifier may refer to two or more pieces of code.
-The pieces of code label by 1 and 3 in fig.~\ref{fig:ast}(a) showes two pathes that are encoded as the same identifier -- $<$\texttt{LE:0xff/BE/ES/CS/FD:max7310\_reset/TU}$>$.
-As a result, this identifier can not distinguish these two pieces of code, 
-and can not serve as a key to these pieces of code.
+This method is robust. However, it may not uniquely identify a piece of code, i.e., one identifier may refer to two or more pieces of code.
+The pieces of code labeled 1 and 3 in Figure~\ref{fig:ast}(a) have different paths from the root of the syntax, however that have the same 
+identifier -- $<$\texttt{LE:0xff/BE/ES/CS/FD:max7310\_reset/TU}$>$. As a result, such identifier cannot distinguish these two pieces of code.
 
-\subsubsection{Hybrid Anchor}
+\subsubsection{Hybrid Anchor.}
 
-Offset-based anchor can uniquely identify a piece of code, but it is not immune to code evolusion.
-Syntax tree based anchor is immune to code evolusion, but it can not uniquely identify some pieces of code.
+Offset-based anchor can uniquely identify a piece of code, but it is not immune to code evolution.
+Syntax tree based anchor is immune to code evolution, but it cannot uniquely identify pieces of code.
 We combine these two methods and form hybrid anchor.
 For each leaf node that has an ambiguous path representation,
-we can always find at least one of its ancesters that has an unique path.
+we can always find at least one of its ancestors that has an unique path.
 In the worst case, we will get to the root node.
 Our approach is composed of two steps.
-First, we compute the syntax tree based anchor,
-then, we go over the path from leaf to root, find the first node that is a unique identifier.
-Second, we compute offset based anchor based on this unique identifier instead of the begining of the whole implementation code.
-Consider the AST in fig.~\ref{fig:ast}(a), to identify the piece of code labeled by 1,
+First, we compute the syntax tree based anchor, go over the path from leaf to root, and find the first node that is a unique identifier.
+Second, we compute offset based anchor using this unique identifier instead of the beginning of the whole implementation code.
+Consider the AST in Figure~\ref{fig:ast}(a), to identify the piece of code labeled by 1,
 we go through the path towards the root,
 and get to the first unique identifier at the inner node CS.
-The node CS represent line 28 - line 35 of the code in fig.~\ref{fig:code}(a).
-It is the body of the function \texttt{max7310\_reset}, and there is only one body for this function by the C language grammer.
-The offset based identifier based on this node is (103,4), as the first charactor of the node CS is located at offset 487 and the offset based anchor is (590,4).
+The node CS represents line 28 - line 35 of the code in Figure~\ref{fig:code}(a).
+It is the body of the function \texttt{max7310\_reset}, and there is only one body for this function by the C language grammar.
+The offset based identifier based on this node is (103,4), as the first character of the node CS is located at offset 487 and the offset based anchor is (590,4).
 We combine the information of the inner node CS and the calculated coordinate to represent the piece of code with no ambiguity.
 Same as offset based anchor, if the code does not change, it can uniquely identify the piece of code.
-If the code changes, this method still works if the code for the unique identifier remain the same.
-Actually, this is a general approach for the previous two.
+If the code changes, this method still works if the code identified by the unique identifier remains the same.
+Actually, this is a generalization of the previous two approaches.
 If we get to the root node while finding the first unique ancestor, then this approach will become the same as offset based anchor.
-However, if the lead node itself is the firtst node with unique identifier, then this approach is the same as syntax based anchor.
+However, if the lead node itself is the first node with unique identifier, then this approach is the same as syntax based anchor.
 The lower the node with the unique identifier in AST, the better our approach works.
-%However, this method provide redundent information, which can be used to check the validity.
+%However, this method provide redundant information, which can be used to check the validity.
 

### 2013-05-05 RPE/conclusion.tex
revise

@@
 \label{sec:conclusion}
-We present an approach to manage the traceability links between HW/SW interface specifications and implementations, considering the unique properties of these traceability links.
-We also implemented our approach in a prototype, namely, coDoc, and used this tool to evaluate our approach.
-We did the experiments on three virtual device prototypes in QEMU.
-The results show that our approach can effectively manage traceability links for HW/SW interface implementations and their specifications.
-70\% of the traceability links are fine-grained, 80\% of them remains valid after source code evolves to a new version.
+We present an approach to manage the traceability links between HW/SW interface specification and implementation.
+This approach considers the unique properties of such traceability links.
+We have implemented our approach in a prototype tool, namely, coDoc, and used it in evaluating our approach.
+We conducted experiments on three QEMU virtual devices.
+The results show that our approach can effectively manage traceability links between HW/SW interface implementation and their specification.
+70\% of the traceability links are fine-grained.
+80\% of them remains valid after source code evolves to a new version.
 
-In the future, we will continue our research in the following directions.
-First, we will consider the specification change, and develop strategy to manage traceability links in this circumstance.
-Second, we will develop automatic traceability link recovering technique for device drivers and their specifications.
+For future work, we plan to continue our research in the following directions.
+First, we will improve our specification anchors to tolerate possible, but infrequent specification changes, and develop strategies to manage traceability links when both code and spec are evolving.
+Second, we will utilize machine-learning techniques to recover additional traceability links based on manually established links.

### 2013-05-05 RPE/evaluation.tex
revise

@@
 MAX7310 is a 8-bit I/O expander developed by Maxim.
-This device is used when a system need more I/O ports.
+This device is used when a system needs additional I/O ports.
 EEPro100, E1000 and RTL8139 are three popular network adapters.
@@
 All these four devices have specifications in PDF (Portable Document Format) format.
-We examined the release history of the virtual implementations and specifications of these four hardware device, and found that almost no change has been made to specifications after the corresponding implementations have begun to release.
+We examined the release history of the virtual implementations and specifications of these four hardware device, and found that almost no change has been made to specifications after the corresponding implementations were released.
 
@@
 We check out ten stable versions of all these virtual device drivers from the repository.
-The ten versions we used are stable-0.10, stable-0.11, stable-0.12, stable-0.13, stable-0.14, stable-0.15, stable-1.0, stable-1.1, stable-1.2 and stable-1.3, we represent them as 1 - 10 repectively.
+The ten versions we used are stable-0.10, stable-0.11, stable-0.12, stable-0.13, stable-0.14, stable-0.15, stable-1.0, stable-1.1, stable-1.2 and stable-1.3. We represent them as 1 - 10 respectively.
 We present the average lines of code (LOC) and the average number of functions of the virtual device prototypes, as well as the number of pages of the specifications in Table \ref{table:vdd}.
-The LOC metrics are measured by the tool named locmetrics.
+The LOC metrics are measured by a tool named locmetrics.
 The lines of code (LOC) range from 181 to 2771. The sizes of specification range from 15 pages to 410 pages.

### 2013-05-05 RPE/implementation.tex
revise

@@
 
-This section presents the architecture of the implementation of our approach first.
-After that, we introduce the algorithm for validating the traceability links, and for code selection completion which helps the user to complete the code piece selection when part of a syntax element is selected.
+This section first presents the architecture of the coDoc prototype tool, which implements our traceability link management framework.
+After that, we introduce the algorithms for validating the traceability links and for code selection completion which helps users to complete code piece selection when part of a syntax element is selected.
 
@@
 
+The architecture of our approach is shown in Figure \ref{fig:architecture}.
+There are three types of data here, 1) code, 2) spec, and 3) traceability links.
+These data are consumed by three components: code manager (CM), spec manager (SM) and link manager (LM).
 \begin{figure}
@@
 \end{figure}
-
-The architecture of our approach is shown in Figure \ref{fig:architecture}. 
-There are three types of data here, 1) code, 2) spec, and 3) traceability links.
-These data are consumed by three components: code manager (CM), spec manager (SM) and link manager (LM).
 \begin{enumerate}
-\item \textit{Link Manager.} Traceability link manager get the highlighted code piece from code manager and the highlighted spec piece from spec manager, and create traceability link for these two piece of information.
-It also reads the traceability link data, verify the validity of the link,
+\item \textit{Link Manager.} Traceability link manager gets the highlighted code piece from code manager and the highlighted spec piece from spec manager, and creates traceability link for these two piece of information.
+It also reads the traceability link data, verifies the validity of the link,
 and highlights the code and document pieces that are related.
-\item \textit{Code Manager.} Code manager reuses C/C++ Development Tool (CDT) editor from Elipse\footnote{\texttt{\url{http://www.eclipse.org}}} to parses the code, 
+\item \textit{Code Manager.} Code manager reuses C/C++ Development Tool (CDT) editor from Eclipse~\cite{Eclipse} to parses the code,
 and highlights syntax elements. It can highlight the piece of code based on the information provided by the user or the link manager.
@@
 We implemented coDoc as an Elipse Rich Client Program (RCP),
-which can make our tool share the appearence in Eclipse that is familiar by many programmer.
+which can make our tool share the appearance in Eclipse that is familiar by many programmer.
 Figure \ref{fig:platformview} is the screenshot of the tool.
-The bottom is the UI for link manager, while the top left part and top right side are the UI for code manager and spec manager repectively.
+The bottom is the UI for link manager, while the top middle part and top right side are the UI for code manager and spec manager respectively.
+To traverse a traceability link, users can select a link from the list in the link manager or click on a code construct in the code manager. 
+As a result, the link, the relevant code, and the relevant spec piece are highlighted in the link, code, and the spec mangers.
 
@@
 \includegraphics[width=\textwidth]{platformview}
-\caption{coDoc Platform View}
+\caption{coDoc User Interface Screenshot}
 \label{fig:platformview}
@@
 \subsection{Link Validation}
-
-\begin{algorithm}[!h]
-\DontPrintSemicolon
-\SetKwComment{tcp}{\hfill$\triangleright$ }{}
-\SetCommentSty{emph}
-$AST \leftarrow \textsc{Gen-AST}(code)$\;
-$\langle RES, CONTENT_C \rangle \leftarrow \textsc{Get-Code-Content}(AST, link.code.path)$\;
-\If{$RES = FAIL$} {
-\Return $FAIL$\;
-}
-$RES \leftarrow \textsc{Compare-Content}(CONTENT_C, link.code.content)$\;
-\If{$RES = FAIL$} {
-\Return $FAIL$\;
-}
-$CONTENT_S \leftarrow \textsc{Get-Spec-Content}(spec, link.spec.path)$\;
-$RES \leftarrow \textsc{Compare-Content}(CONTENT_S, link.spec.content)$\;
-\If{$RES = FAIL$} {
-\Return $FAIL$\;
-}
-\Return $SUCCESS$\;
-\caption{$\textsc{Traceability-Link-Validation}(link)$}
-\label{alg:validate}
-\end{algorithm}
 
@@
 When code evolves, we need to validate the existing traceability links.
-Once an invalid traceability links is found, we should report it to let user correct it manually.
+Once an invalid traceability link is found, we report it and ask the user to correct it manually.
 To check the validity of the traceability links, we record the content of the code piece and the spec piece when generating the links.
 The content is used later to compare with the content to which the path points to when code changes.
-The validation process basically go through each traceability link in the database, 
-and check whether the link is valid or not.
+The validation process basically goes through each traceability link in the database,
+and checks whether the link is valid or not.
+\begin{algorithm}[!h]
+\DontPrintSemicolon
+\SetKwComment{tcp}{\hfill$\triangleright$ }{}
+\SetCommentSty{emph}
+$AST \leftarrow \textsc{Gen-AST}(code)$\;
+$\langle RES, CONTENT_C \rangle \leftarrow \textsc{Get-Code-Content}(AST, link.code.path)$\;
+\If{$RES = FALSE$} {
+\Return $FAILURE$\;
+}
+$RES \leftarrow \textsc{Compare-Content}(CONTENT_C, link.code.content)$\;
+\If{$RES = FAIL$} {
+\Return $FAILURE$\;
+}
+$CONTENT_S \leftarrow \textsc{Get-Spec-Content}(spec, link.spec.path)$\;
+$RES \leftarrow \textsc{Compare-Content}(CONTENT_S, link.spec.content)$\;
+\If{$RES = FAIL$} {
+\Return $FAILURE$\;
+}
+\Return $SUCCESS$\;
+\caption{$\textsc{Traceability-Link-Validation}(link)$}
+\label{alg:validate}
+\end{algorithm}
 Algorithm~\ref{alg:validate} presents the pseudo-code for check the validation of one single traceability link.
@@
 If the path of the code piece cannot identify any code piece or can identify more than one code piece, the function \textsc{Get-Code-Content} reports failure.
-Line 5 compare the the new content extracted from the new code with the recorded old content, and fail if the two contents do not match.
-After finishing check the code piece part, line 8 - line 11 of the algorithm check the spec piece part in a similar flow.
-If no failure happens, the algorithm return successfully at line 12.
+Line 5 compares the the content extracted from the new code with the recorded content, and reports failure if they do not match.
+After finishing checking the code piece, line 8 - line 11 of the algorithm check the spec piece in a similar flow.
+If no failure happens, the algorithm returns successfully at line 12.
 
@@
 
+%To improve the user experience of coDoc, we help users to select the code pieces when creating traceability links.
+The coDoc tool assists user to select the code pieces that can be used in traceability links. Each code piece selected is required to be a complete language construct.
+%Our approach is based on the fact that it is usually meaningless to have part of the basic code elements as the code piece of the traceability links.
+For example, we do not create a link between part of a variable name in the code and part of a word in the spec.
+We assume that every selected piece of code is composed of valid syntax elements.
+Based on this assumption, we can help users to automatically complete their selection when they only select part of a syntax element such as a variable. 
+Algorithm \ref{alg:completion} outlines our approach.
 \begin{algorithm}[!h]
@@
 $AST \leftarrow \textsc{Gen-AST}(code)$\;
-$SEQUENCE_{LEAF} \leftarrow \textsc{Gen-Leaf-Sequence}(AST)$\;
-$POC_{AST} \leftarrow \textsc{To-AST-Based}(SEQUENCE_{LEAF}, selection_{org})$\;
-$selection_{new} \leftarrow \textsc{To-Offset-Based}(POC_{AST})$\;
-\Return $selection_{new}$\;
-\caption{$\textsc{Complete-Code-Selection}(selection_{org})$}
+$LEAF\_SEQ \leftarrow \textsc{Gen-Leaf-Sequence}(AST)$\;
+$AST\_selection \leftarrow \textsc{To-AST-Based}(LEAF\_SEQ, original\_offset)$\;
+$new\_offset \leftarrow \textsc{To-Offset-Based}(AST\_selection)$\;
+\Return $new\_offset$\;
+\caption{$\textsc{Complete-Code-Selection}(orginal\_offset)$}
 \label{alg:completion}
 \end{algorithm}
-
-To improve the user experience of coDoc, we help users to select the code pieces when creating traceability links.
-Our approach is based on the fact that it is usually meaningless to have part of the basic code elements as the code piece of the traceability links.
-For example, we do not create a link between half of the variable and the spec piece.
-We assume that every selected piece of code is composed of valid syntax elements.
-Based on this assumption, we can help the user to automatically complete their selection when they only select part of the syntax element, like a variable, a constant, and etc. 
-Algorithm \ref{alg:completion} outlines our approach.
-This algorithm takes a code selection in offset based format,
-and returns a new code selection in offset based format.
-We choose offset based format because Eclipse use this format to highlight the code piece.
-The algorithm basically includes two parts: (1) line 1 - line 3 force the input selection to be aligned by transforming it from offset based code piece to AST based code piece.
-(2) line 4 generates the required format by transforming AST based code piece back to offset based code piece.
-As we discussed before, AST based representatioin is a sequence of AST leaf nodes in DFS visit order, which is the same order as in the source code.
+This algorithm takes a code selection in the offset based format,
+and returns a new, appropriately enlarged code selection in the offset based format.
+We choose offset based format because Eclipse use this format to highlight code pieces.
+The algorithm basically works as follows: (1) lines 1 - 3 align the input offset-based selection to its smallest enclosing language construct by analyzing the AST.
+(2) line 4 maps the enlarged code selection to the offset based format and returns it.  
+As we discussed above, the AST based selection is a sequence of AST leaf nodes in the depth-first-search order, which is the same order as the code in the source code.
 The AST based code piece covers all the meaningful part of the original offset based code piece.
-To transform the offset based code piece to AST based code piece, 
-we get the sequence of leaf nodes of AST in line 1 and line 2,
-and then match the leaf node sequence with the code piece to get the AST based representation.
-The leaf node in the AST based representation is determined this way: if the leaf node contains any part of the selected code, then the leaf node is in the representation.
-After we get the AST based representation,
-we transform it back to offset based reprensentation, and return it.
-This way, each time the user make a selection,
-our engine adjust the selection to valid syntax boundary.
+To transform the offset based selection to the AST based selection,
+we obtain the sequence of leaf nodes of the AST in line 1 and line 2,
+and then match the leaf node sequence with the offset-based selection to get the enlarged AST based selection.
+The leaf nodes in the AST based selection is determined as follows: if a leaf node contains any part of the offset selected code, then the leaf node is in the AST based selection.
+After we obtain the AST based selection, we transform it back to a new, enlarged offset based selection, and display it to users.
+Each time users make a selection, coDoc adjusts the selection to valid syntax boundary.

### 2013-05-05 RPE/introduction.tex
revise

@@
 
-The majority of software engineering work is devoted to maintaining legacy software systems other than developing new ones \cite{abran_maintenance_1991}.
-It is estimated that up to 60\% of software maintenance time is spent on program comprehension \cite{lawrence_software_2006}.
+Significant portion of software engineering efforts is devoted to maintaining legacy software systems~\cite{abran_maintenance_1991}.
+It is estimated that up to 60\% of software maintenance efforts is spent on program comprehension~\cite{lawrence_software_2006}.
 Software developers often find it difficult to extract the knowledge about a software system,
-because the knowledge is often implicitly expressed,
-and distributed in a variety of software artifacts.
+because such knowledge is often implicitly expressed and distributed in a variety of software artifacts.
 Examples of software artifacts include source code, design documents, application programming interface specifications, bug reports, etc.
 
-To make the knowledge about a software system explicit,
-reserachers have built various techniques to recover the semantic connections among software artifacts,
+To capture such knowledge explicitly, various techniques have been developed to recover the semantic connections among software artifacts,
 especially between documentation and source code \cite{antoniol_recoveringtraceability_2002} \cite{deLucia_incremental_2006} \cite{marcus_recovering_2003}.
-These semantic connections are often called \textit{traceability links}. 
-Effectively maintaining the traceability links can help improving the productivity of the developer and the quality of the software \cite{neumuller_case_2006}.
+Such semantic connections are often called \textit{traceability links}.
+Effectively maintaining the traceability links helps improving developer productivity and software quality \cite{neumuller_case_2006}.
 
-Unfortunately, these techniques are not ready to be applied to implementations and specifications of HW/SW interfaces,
-even though these implementations are an important category of software that caused most of the system failures in both Windows and Linux operating systems \cite{swift_os_2003} \cite{chou_os_2001},
-HW/SW interface forms the interaction point of hardware and software,
-and defines the protocol for the hardware and software to communicate.
-The implementation of HW/SW interfaces refers to hardware design, device drivers and virtual device prototypes, who implement the communication logic on both sides of the interfaces.
+Unfortunately, these techniques are not readily applicable to specification and implementation of hardware/software (HW/SW) interfaces,
+even though such implementation causes most system failures in both Windows and Linux operating systems \cite{swift_os_2003} \cite{chou_os_2001},
+HW/SW interface inter-connects hardware and software and defines the protocol for hardware and software to communicate.
+The implementation of HW/SW interfaces typically include hardware designs and device drivers.
+There is also software implementation of hardware design, e.g., virtual devices in virtual machines such as QEMU~\cite{Bellard05}
+%and virtual device prototypes, who implement the communication logic on both sides of the interfaces.
 %The implements are designed for a variety of computer components, and form a large part of operating systems and virtual machines.
-HW/SW interface specifications describe the HW/SW interfaces in natuaral lagnguage,
-and guide the implementation of the interfaces.
-HW/SW interface specifications play a crucial role in the comprehension and maintenance of the implementations of the interfaces.
-The reason why existing traceability link recovering techniques do not work for HW/SW interfaces is that these traceability links need to be fine-grained,
-which is not supported by the existing techniques.
-HW/SW interfaces are mainly composed of software-programmable hardware registers mapped to the processor's address space.
-The low-level abstraction of the software/hardware interface makes the traceability links fine-grained.
-Traceability links between the specifications and implementations usually connect statements, which operate the registers, or expressions, which represent certain bits of registers, to the register bit descriptions in the specifications.
-However, previous tools usually maintain tracebility links between the classes or functions of the source code and sections or paragraphes of the documentation, which is more coarse-grained.
+
+A HW/SW interface specification describes a HW/SW interface in natural language and guides its implementation.
+The specification plays a crucial role in the comprehension and maintenance of the implementation.
+The key reason why existing traceability link recovering techniques do not work for HW/SW interfaces is that these traceability links need to be fine-grained,
+which are not supported by the existing techniques.
+HW/SW interfaces are mainly composed of software-programmable hardware registers mapped to the processor address space.
+The low-level abstraction of the HW/SW interface demands the fine-grained traceability links.
+These traceability links need to connect statements which operate the registers or expressions which represent certain bits of registers to the register bit descriptions in the specification.
+However, previous techniques maintain traceability links between classes or functions of the source code and sections or paragraphes of the specification, which is to coarse-grained.
 
@@
 
-We present a framework for managing traceability links between specifications and implementations of HW/SW interfaces. 
+We present a framework for managing traceability links between specification and implementation of HW/SW interfaces.
 This framework supports fine-grained links between basic elements of specifications and constructs of implementation languages.
-We design a data model to support the framework, and organize the data for the traceability links.
-Our framework also supports automatic migration of links as implementations evolve.
+A simple, but effective data model is developed to support the framework and organize the data of the traceability links.
+Our framework also supports automatic migration of valid traceability links as implementation evolves.
 
 We have implemented a prototype tool, namely coDoc, in support of this framework.
-With this tool, the developer can import and manage implementation source code and interface specifications, select a certain piece of implementation (POI) and a certain piece of specification (POS) of interest, create a traceability link connecting the seleted POI and POS, check out a different version of source code, review and verify the existing traceability links.
-We applied coDoc to three virtual device prototypes and their specifications, recovered traceability links, and verified the traceability links on other versions of the driver code.
+With coDoc, developers can (1) import and manage implementation source code and interface specifications, (2) select a piece of implementation (POI) and a piece of specification (POS) of interest, (3) create a traceability link connecting the selected POI and POS, (4) check out a different version of source code, and (5) migrate, review, and verify existing traceability links.
+We applied coDoc to source code of three virtual devices from QEMU and their specifications, recovered traceability links, and migrated these links to newer versions of source code .
 Experimental results show that our framework fully supports the types of traceability links between the virtual devices and their specifications,
-maintain traceability links with required granularity, 
-and it accurately migrates valid links from version to version.
-\todo{the data need to be updated}\hlc{It preserves 70\% of the existing traceability links when code evolves to a new version.}
+maintain traceability links with required granularity, and accurately migrates valid links from version to version.
+\todo{the data need to be updated}\hlc{It preserves 70\% of valid traceability links when source code evolves to a new version.}
 
@@
 \begin{itemize}
-\item Presented a framework for managing traceability links between specifications and implementations of HW/SW interfaces with accuracy, robustness and fine-granularity.
-\item Developed coDoc, a tool implementing the approach.
-\item Evaluated our approach with realistic examples.
+\item Presented a framework for managing traceability links between specification and implementation of HW/SW interfaces;  
+\item Developed a simple, but effective data model for capturing and recording links; 
+\item Identified appropriate anchors in implementation and specification that support fine-granularity and migration of valid links as implementation evolves; 
+\item Developed coDoc, a prototype tool implementing the approach and evaluated our approach on realistic examples.
 \end{itemize}
@@
 The rest of the paper is organized as follows.
-Section \ref{sec:problem} examplifies and defines the problem that we address in this paper.
-Section \ref{sec:approach} and section \ref{sec:implementation} illustrate the design and implementation details of our approach.
-Section \ref{sec:evaluation} provides some preliminary evaluation results.
-Section \ref{sec:related} reviews the related work.
-We conclude our approach and discuss the future work in Section \ref{sec:conclusion}.
+Section \ref{sec:problem} elaborates on the problem addressed in this paper.
+Section \ref{sec:approach} and Section \ref{sec:implementation} illustrate the design and implementation details of our approach.
+Section \ref{sec:evaluation} provides preliminary evaluation results.
+Section \ref{sec:related} reviews related work.
+We conclude this paper and discuss future work in Section \ref{sec:conclusion}.

### 2013-05-05 RPE/paper.tex
revise

@@
 
-\documentclass[runningheads,a4paper]{llncs}
+\documentclass[letter]{llncs}
 
@@
 \usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \usepackage{float}
@@
 % first the title is needed
-\title{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
+\title{Managing Traceability Links between Specification and Implementation of Hardware/Software Interfaces}
 % a short form should be given in case it is too long for the running head
-\titlerunning{Traceability Links between Specifications and Implementations}
-\authorrunning{Dejun Qian}
+%\titlerunning{Traceability Links between Specifications and Implementations}
+%\authorrunning{Dejun Qian}
 
-\author{Dejun Qian\\dejun@cs.pdx.edu}
-\institute{Computer Science Department, Portland State University}
+\author{Dejun Qian}
+\institute{Department of Computer Science  \\
+Portland State University \\
+Portland, OR 97207 \\
+dejun@cs.pdx.edu}
 

### 2013-05-05 RPE/problem.tex
revise

@@
 % emphasize the special characteristic of hardware-related software
-\section{Problem Statement}
+\section{Problem in Managing HW/SW Interface Traceability Links}
 \label{sec:problem}
 
+An interface between hardware and software is typically composed of registers exposed by hardware devices and accessible by software.
+The implementation of the interface should conform to the specification in order to function correctly.
+Suppose we have to maintain and understand this implementation, we need to establish the relationships between the implementation and the specification.
 \begin{figure}[h!]
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{code1}
+  \includegraphics[width=0.8\linewidth]{code1}
 \end{minipage}\\
-(a) The Old Version\\
+(a) Older Version\\
 \\
@@
   \centering
-  \includegraphics[width=0.95\linewidth]{code2}
+  \includegraphics[width=0.8\linewidth]{code2}
 \end{minipage}\\
-(b) The Newer Version
+(b) Newer Version
 \end{tabular}
-  \caption{Two Versions of a Virtual Devices Written in C.
-This piece of code is extracted from MAX7310 virtual device in QEMU virtual machine.
-This code defines a function to reset the registers.
-However, we do not know why they are resetted to the values labeled 1, 2 and 3.
-To know the answer, we need to refer to the specification.}
+  \caption{ Corresponding code snippets from two versions of the MAX7310 virtual device from the QEMU virtual machine. This code defines a function to reset the device.}
+  %However, it is unclear why the registers are reset to the values labeled 1, 2 and 3. To know the answer, one has to refer to the specification.}
 \label{fig:code}
@@
 \end{figure}
+Figure~\ref{fig:code}(a) presents part of code extracted from the MAX7310 virtual device from QEMU.
+A virtual device is a software implementation emulating a hardware device.
+MAX7310 is a 8-bit I/O port expander.
+QEMU (Quick EMUlator)~\cite{Bellard05} is a virtual machine widely used in industry to assist hardware-related software development.
+The source code for this implementation is written in the C language.
+From the name of the function, we can guess it is trying to reset the device to its initial state.
+However, we cannot figure out what the values in the right sides of the assignment statements mean only by reading the code here.
+Figure~\ref{fig:spec} includes the information extracted from the specification of MAX7310.
+In this figure, we can see three tables for three registers: polarity register, direction register, and status register.
+These tables present the bit arrangement and the default value for each register.
+We can see that the values used in the code are defined in the specification.
+The code uses the hex format, and the specification uses the binary format.
+The piece of code and the piece of specification labeled with the same number are related, which means the piece of specification explains the piece of code with the same label.
 
@@
   \includegraphics[width=0.7\textwidth]{spec}
-  \caption{Specification Example. This is part of MAX7310 specification. It includes three tables, which define the default values for three registers.}
+  \caption{Specification Example. This is part of the MAX7310 specification, including three tables which define default values for three registers.}
   \label{fig:spec}
@@
 
-The interfaces between software and hardware are composed of registers exposed by hardware devices and accessible by software.
-The implementation of the interfaces should conform to the specification in order to function correctly.
-Suppose we have to maintain and understand this implementation, we need to establish relationships between the implementation and the specification.
-Fig.~\ref{fig:code}(a) presents part of code extracted from a virtual device prototype for MAX7310 in QEMU.
-A virtual device prototype is a software implementation emulating a hardware device.
-MAX7310 is a 8-bit I/O port expander.
-QEMU (Quick EMUlator)\footnote{\texttt{\url{http://www.qemu.org}}} is virtual machine used widely in industry to assist hardware related software development.
-The source code for this implementation is written in C language.
-From the name of the function, we can guess the function shown is trying to reset the device to its initial state.
-However, we can not figure out what the values in the right sides of the assignment statements mean only by reading the code here.
-Fig.~\ref{fig:spec} includes the information extracted from the specification of MAX7310.
-In this figure, we can see three tables for three registers: polarity register, direction register and status register.
-These tables present the bit arrangement and the default value for each register.
-By looking at this specification, now we can see that the values used in the code are defined in the specification.
-The code uses the hex format, and the specification use binary format.
-The piece of code and the piece of specification labeled with the same number are related, which means the piece of specification explains the piece of code with the same label.
-
 % in the directory including max7310.c: git log --follow --all -p max7310.c > a.txt
-Code evolves all the time in its lifecycle.
-By checking the QEMU repository, we can find that the first version of the code in Fig~\ref{fig:code} was created on May 23, 2007, and the last change is on May 1, 2013.
+Implementation code evolves all the time in its lifecycle.
+By checking the QEMU repository, we found that the first version of the code in Figure~\ref{fig:code} was created on May 23, 2007, and the last change was on May 1, 2013.
 This code has changed 21 times till now, and it still keeps changing.
-Fig.~\ref{fig:code}(b) shows an example of a new version of the code in Fig.~\ref{fig:code}(a).
-Line 13, 25 and 29 of the code in Fig.~\ref{fig:code}(a) has changed to the line 12, 24 and 28 in Fig.~\ref{fig:code}(b).
-
-Compared to code, specification is relatively stable.
-The specification in Fig~\ref{fig:spec} only has three versions, and the last change happened in 2005.
+Figure~\ref{fig:code}(b) shows a newer version of the code in Figure~\ref{fig:code}(a).
+Line 13, 25 and 29 of the code in Figure~\ref{fig:code}(a) has changed to the line 12, 24 and 28 in Figure~\ref{fig:code}(b).
+Compared to code, specification is often relatively stable.
+The specification in Figure~\ref{fig:spec} only has three versions, and the last change happened in 2005.
 The specification remains unchanged since the code was created.
 
-This example is simple, but reveals three basic requirements for the management of traceability links between specification and implementations as follows.
+This example, although simple, reveals three basic requirements for managing traceability links between specification and implementations as follows.
 
-\textbf{Requirement 1:} Traciability links should be able to uniquely refer to and accurately locate the relevant pieces of code in the source file and the piece of specification in the specification file.
-As in the example, there should be a way to locate the code pieces and specification pieces surrounded by the boxes labeled by 1, 2 and 3.
+\smallskip
+\noindent 
+\textbf{Requirement 1:} Traceability links should be able to uniquely identify and accurately locate relevant pieces of code in the source file and pieces of specification in the specification file.
+As in the example, there should be a simple and unique way to locate the code pieces and specification pieces surrounded by the boxes labeled by 1, 2 and 3.
 
-\textbf{Requirement 2:} Traceability links should be able to provide referrence at statement level or expression level for source code and at sentence level or word level for specification.
-As in this example, the code pieces and specification pieces surrounded by the boxes labeled by 1, 2 and 3 are all on this level.
+\smallskip
+\noindent
+\textbf{Requirement 2:} Traceability links should be able to provide references on the statement level or expression level for source code and at the sentence level or word level for specification.
+As in this example, the code pieces and specification pieces surrounded by the boxes labeled by 1, 2 and 3 are all on the expression level and the word level.
 
-\textbf{Requirement 3:} Traceability links should be immune from the evolusion of unrelated code.
-We should grarantee that the identifier created for the old version of code works for the new version of code if the code piece refered by the identifier does not change.
+\smallskip
+\noindent
+\textbf{Requirement 3:} Traceability links should be immune from the evolution of unrelated code.
+We need to ensure that an identifier created for the old version of code works for the new version if the code piece referred to by the identifier does not change.

### 2013-05-05 RPE/related.tex
revise

@@
 \label{sec:related}
-Researchers have done much work to build automatic tools for traceability link recovery (TLR) from software systems \cite{antoniol_recoveringtraceability_2002} \cite{deLucia_incremental_2006} \cite{marcus_recovering_2003}.
+There has been much research on building automatic tools for traceability link recovery (TLR) from software artifacts \cite{antoniol_recoveringtraceability_2002} \cite{deLucia_incremental_2006} \cite{marcus_recovering_2003}.
 TLR technology scans the software artifacts including source code and documentation and recovers the semantic connections by information retrieval (IR) methods.
-\todo{improve}This technology has shown to be advanced and successful \cite{spanoudakis_software_2004}.
-However, IR techniques are not good enough to substitute the human decision-maker in the linking process.
-Hayes et al. suggests these IR techniques should only be used to generate an appropriate list of candidate links evaluated by software analyst \cite{hayes_advancing_2006}.
-The recall of these techniques is not as good as to be pratical, a significant part of traceability links need to be recovered manually.
-Trace acquisition remains human-intensive and with high initial cost as reported in case studies on industrial processes and traceability experiences \cite{lindvall_practical_1996} \cite{ramesh_implementing_1995} \cite{asuncion_an_2007} \cite{gotel_extended_1997} \cite{neumuller_case_2006}.
+%\todo{improve}This technology has shown to be advanced and successful \cite{spanoudakis_software_2004}.
+However, IR techniques cannot completely substitute the human decision-maker in the linking process.
+Hayes et al. suggests such IR techniques should only be used to generate an appropriate list of candidate links which are then evaluated by software analysts \cite{hayes_advancing_2006}.
+For this reason, these automatic techniques have not been widely adopted and most traceability links still need to be recovered manually.
+Link acquisition remains human-intensive and with high initial cost as reported in case studies on industrial processes and traceability experiences \cite{lindvall_practical_1996} \cite{ramesh_implementing_1995} \cite{asuncion_an_2007} \cite{gotel_extended_1997} \cite{neumuller_case_2006}.
 
@@
 these links are probably only valid for a certain version of the software.
-As software evolves during the development and maintenance process, software artifacts changes as well.
+As software evolves during the development and maintenance process, software artifacts changes constantly.
 These changes might invalidate the existing traceability links.
+For manually recovered links, we must reestablish these links manually again, which is arduous.
 For automatically recovered links, we can re-run the TLR tool to reestablish them.
-However, this solution is computationally costly for interactive use during software development stage.
-For manually recovered links, we must reestablish these links manually again, which is arduous.
-This intimidate people from using TLR tools in their daily work.
-Some work has been done to address this problem by improving exisiting IR based methods \cite{jiang_incremental_2008}.
-However, these work didn't consider the situations specific to hardware related software.
+However, this solution is computationally costly for interactive use during the software development stage.
+This intimidates people from using TLR tools in their daily work.
+There has been research addressing this problem by improving existing IR based methods \cite{jiang_incremental_2008}.
+Our approach differs in that we try to migrate valid links instead of re-establishing these links.
+%However, these work didn't consider the situations specific to hardware related software.
 

### 2013-05-05 RPE/evaluation.tex
evaluation part

@@
+% the granularity of valid links:
+% 0 135 100
+% the number of valid links:
+% 233 232 195 188 188 170 170 169 169 169
+
 \section{Evaluation}
@@
 
+In this section, we evaluate our approach with four real world implementations and their specifications.
+With coDoc, we first manually create the traceability links between these implementations and specifications.
+We then analyze these traceability links and show how they meet the three requirements we propose in previous sections.
+
 \subsection{Experimental Setup}
-\todo{The data in the section are fake.}
-We evaluate our approach on four virtual device prototypes in QEMU.
+We evaluate our approach on four virtual devices in QEMU.
+Virtual devices form a category of implementations of HW/SW interfaces.
+They emulate the hardware devices for virtual machines, and conform to the same specifications as the real hardware devices.
 QEMU is a generic and open source machine emulator, which can host unmodified guest operating systems \cite{bellard_qemuwiki_2013} \cite{bellard_qemu_2005}.
-QEMU includes virtual implementations for a large number of hardware devices.
+QEMU includes virtual devices for a large number of hardware devices.
 We do our evaluation on four of them: MAX7310, RTL8139, EEPro100 and E1000.
@@
 Both EEPro100 and E1000 are developed by Intel, and RTL8139 is developed by Realtek.
-All these four devices have specifications in PDF (Portable Document Format) format.
-We examined the release history of the virtual implementations and specifications of these four hardware device, and found that almost no change has been made to specifications after the corresponding implementations were released.
+The specifications of all these four devices are in PDF (Portable Document Format) format.
 
-Based on the QEMU repository, the virtual device prototypes for MAX7310, RTL8139, EEPro100 and E1000 have 22, 143, 163 and 168 versions since they are first created.
-We check out ten stable versions of all these virtual device drivers from the repository.
-The ten versions we used are stable-0.10, stable-0.11, stable-0.12, stable-0.13, stable-0.14, stable-0.15, stable-1.0, stable-1.1, stable-1.2 and stable-1.3. We represent them as 1 - 10 respectively.
-We present the average lines of code (LOC) and the average number of functions of the virtual device prototypes, as well as the number of pages of the specifications in Table \ref{table:vdd}.
-The LOC metrics are measured by a tool named locmetrics.
-The lines of code (LOC) range from 181 to 2771. The sizes of specification range from 15 pages to 410 pages.
+The release history of these four virtual devices and their specifications shows that almost no change has been made to specifications after the virtual devices were first released.
+The virtual devices for MAX7310, RTL8139, EEPro100 and E1000 have 22, 143, 163 and 168 versions respectively since their first release.
+QEMU published ten stable versions: stable-0.10, stable-0.11, stable-0.12, stable-0.13, stable-0.14, stable-0.15, stable-1.0, stable-1.1, stable-1.2 and stable-1.3.
+We will going to illustrate our evaluation results on these then versions.
+In the rest of the paper, we refer to these ten versions as 1 - 10 respectively.
 
-The changes from version to version for all the four virtual device prototypes are shown in Table \ref{table:version}.
-The changes are measured by the lines of code different from version to version using an open source tool cloc.
+Table \ref{table:vdd} shows the size of these four virtual devices and their specifications.
+We use the lines of code (LOC) and number of functions to measure the size of the virtual devices, and the number of pages to measure the size of the specifications.
+As shown in the table, the LOCs of the virtual devices range from 181 to 2771, and the number of functions range from 9 to 101.
+The sizes of the specifications range from 15 to 410 pages.
 
 \begin{table}[th]
-\caption{Three Virtual Device Drivers Used for Evaluation}
+\caption{Four Virtual Devices and Their Specifications Used for Evaluation}
 \centering
@@
 \hline
- & \multicolumn{2}{c}{implementation} & specification \\
-\cline{2-4}
- & LOC & Functions & pages \\
+ & \multicolumn{2}{c}{Virtual Devices} & Specifications \\
+\cline{2-3} \cline{4-4}
+ & LOC & Functions & Pages \\
 \hline
@@
 
+\subsection{Evaluation Results for Our Approach}
+The results show how our approach meets the three requirements respectively.
+We manually create the traceability links between the four virtual devices of version VER1 and their specification.
+We then analyze the traceability links and compute the correspondence and granularity.
+The created traceability links are also checked with the other versions of virtual devices, and show the orthogonality of our approach.
+
+% accuracy
+\subsubsection{The Correspondence of Our Approach}
+We measure the correspondence by the percentage of the number of traceability links that can uniquely identify a certain POI and a certain POS over the number of all the traceability links created.
+We go through each traceability link, and check if the traceability links can identify a different POI and POS.
+If not, we count this traceability links as the one with correspondence.
+We do the experiments on all created traceability links for the four virtual devices and their specifications.
+The results show that our approach can grantee that the traceability links conform to the requirement of correspondence.
+
+% granularity
+\subsubsection{The Granularity of Our Approach}
+To measure the granularity of the traceability links created by our approach, we count the traceability links that connect to functions, statements and expressions respectively.
+We check each traceability link.
+If it connects to a POI including a function declarator, we count it as a function level traceability.
+If a traceability link is not at function level, we check if the POI includes semicolon.
+If so, we classify it as statement level traceability link, otherwise, we classify it as expression level traceability link.
+The results are listed in Table \ref{table:granularity}.
+From the results, we can see most of the traceability links connect to statements and expressions, and our approach can handle this situation very well.
+The same result happens for the specifications.
+All the traceability links connect to the POSes smaller than a paragraph, and most of them connect to the cells in the tables describing registers.
+
 \begin{table}[th]
-\caption{The Changes in Ten Versions}
+\caption{The Granularity Result of Our Approach}
+\centering
+\begin{tabular*}{0.6\textwidth}{@{\extracolsep{\fill}}rccc}
+\hline
+ & \# functions & statements & expressions \\
+\hline
+MAX7310 & 0 & 3 & 18\\
+RTL8139  & 0 & 135 & 100\\
+EEPro100  & 5 & 81 & 127\\
+E1000  & 2 & 102 & 127\\
+\hline
+\end{tabular*}
+\label{table:granularity}
+\end{table}
+
+%In our own experience, we found that the ability to see the code,
+%the documentation and the relationships on the same screen saves a lot of time,
+%as we don't need to switch between different tools.
+
+\subsubsection{The Orthogonality of Our Approach}
+
+To evaluate the orthogonality of our approach, we apply the traceability links created on the virtual devices of version 1 to the other versions.
+We count the number of traceability links that are still valid when the virtual devices evolve to another version.
+Table \ref{table:version} shows the changes of all the four virtual devices from version to version.
+The changes are measured by the lines of code using an open source tool cloc.
+From the table, we can see that some virtual device do not change for some versions.
+For example, the virtual device MAX7310 did not change when the version moves from 3 to 4.
+We also can see some virtual device change dramatically for some version.
+For example, the virtual device EEPro100 has 1870 lines of code, and has 903 lines of code change from version 3 to 4.
+
+\begin{table}[th]
+\caption{The Differences Between The Virtual Device Versions}
 \centering
@@
 
-% accuracy
-\subsection{Accuracy}
-We measure the accurary by the number of uniquely identifiable POC over number of traceability links recovered for all the virtual prototypes. The result is shown in Table \ref{table:accuracy}
-
-\begin{table}[th]
-\caption{Accuracy}
-\centering
-\begin{tabular*}{0.3\textwidth}{@{\extracolsep{\fill}}rc}
-\hline
- & accuracy \\
-\hline
-MAX7310 & 80\%\\
-RTL8139  & 87\%\\
-EEPro100  & 78\%\\
-E1000  & 91\%\\
-\hline
-\end{tabular*}
-\label{table:accuracy}
-\end{table}
-
-% granularity
-\subsection{Granularity}
-
-The identifying method with fine granularity makes the relationship created by coDoc very accurate,
-80\% of the code pieces are marked inside the statement and expressions.
-The same result happens for the document.
-In the whole relationships,
-90\% of the document pieces are marked on cells in the tables.
-The granulariy results are listed in Table \ref{table:granularity}.
-
-\begin{table}[th]
-\caption{Granularity Result}
-\centering
-\begin{tabular*}{0.6\textwidth}{@{\extracolsep{\fill}}rccc}
-\hline
- & \# functions & statements & expressions \\
-\hline
-MAX7310 & 108 & 2 & 3\\
-RTL8139  & 213 & 4 & 5\\
-EEPro100  & 213 & 4 & 5\\
-E1000  & 213 & 4 & 5\\
-\hline
-\end{tabular*}
-\label{table:granularity}
-\end{table}
-
-%In our own experience, we found that the ability to see the code,
-%the documentation and the relationships on the same screen saves a lot of time,
-%as we don't need to switch between different tools.
-
-\subsection{Adapting to Evolving Code}
-
-To evaluate how our approach adapt to evolving code, we recover the traceability links for the first version of all the four virtual device driver code.
-We then check the number of valid traceability links left in the later versions. The result is shown in table \ref{table:robust}.
+The number of valid traceability links remaining valid at each version is shown in table \ref{table:robust}.
+As expected, the number of valid traceability links falls while the versions move away.
+However, more than half of the traceability links still remain valid even after ten stable versions of code change.
+We can also see from the table that the more the code changes, the less the traceability links remain valid.
 % traceability link lifetiem (versions)
@@
 \begin{table}[th]
-\caption{Robustness}
+\caption{The Orthogonality Result of Our Approach}
 \centering
-\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}rccccccccc}
+\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}rcccccccccc}
 \hline
- & 1-2 & 2-3 & 3-4 & 4-5 & 5-6 & 6-7 & 7-8 & 8-9 & 9-10 \\
+ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
 \hline
-MAX7310 & 108 & 2 & 10 & 108 & 2 & 10 & 108 & 2 & 10\\
-RTL8139  & 213 & 4 & 210 & 108 & 2 & 10 & 108 & 2 & 10\\
-EEPro100  & 213 & 4 & 20 & 108 & 2 & 10 & 108 & 2 & 10\\
-E1000  & 213 & 4 & 290 & 108 & 2 & 10 & 108 & 2 & 10\\
+MAX7310 & 21 & 12 & 12 & 12 & 12 & 12 & 12 & 12 & 12 & 12\\
+RTL8139  & 233 & 232 & 195 & 188 & 188 & 170 & 170 & 169 & 169 & 169\\
+EEPro100  & 233 & 232 & 195 & 188 & 188 & 170 & 170 & 169 & 169 & 169\\
+E1000  & 233 & 232 & 195 & 188 & 188 & 170 & 170 & 169 & 169 & 169\\
 \hline
@@
 
-\subsection{Performance}
+\subsubsection{Summary}
+Our approach can meet the three requirements for the traceability links between virtual devices and specifications.
+The traceability links created using our approach are fine grained and robust.
+They can connect to statement and expression level POIs, as well as sentence and word level POSes.
+More than half of them remain valid after the code evolves for ten stable versions.
 
-We test the performance of our algorithm to complete code selection and to verify traceability links. The result is shown in table \ref{table:performance}.
-
-\begin{table}[th]
-\caption{Performance}
-\centering
-\begin{tabular*}{0.6\textwidth}{@{\extracolsep{\fill}}rccc}
-\hline
- & verification & completion\\
-\hline
-MAX7310 & 108 & 2 \\
-RTL8139  & 213 & 4\\
-EEPro100  & 213 & 4\\
-E1000  & 213 & 4\\
-\hline
-\end{tabular*}
-\label{table:performance}
-\end{table}
-
-\subsection{Summary}
-
-In summary, our approach can meet the three requirements for the traceability links between device drivers and device specifications.
-We believe this tool will lead to increased productivity.
+% LocalWords:  coDoc rccc RTL cloc rccccccccc EEPro
